### 2015-02-04 proposal.tex
proposal

% This is "bach-ref-2009.tex" Updated january 29th 2010.
% This file should be compiled with "sig-alternate-fixed.cls" January 2010.
% It is based on the ACM style "sig-alternate.cls"
% -------------------------------------------------------------------------
% This example file demonstrates the use of the 'sig-alternate-fixed.cls'
% V2.5 LaTeX2e document class file. It is for those submitting
% articles to the Twente Student Conference on IT. Both this file as the 
% document class file are based upon ACM documents.
%
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls) produces:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line TSConIT
%       4) NO page numbers
%       5) NO headers and/or footers
%
%
% Using 'sig-alternate.cls' you have control, however, from within
% the source .tex file, over both the CopyrightYear
% (defaulted to 200X) and the ACM Copyright Data
% (defaulted to X-XXXXX-XX-X/XX/XX).
% e.g.
% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
%
% ---------------------------------------------------------------------------------------------------------------
% This .tex source is an example which *does* use
% the .bib file (from which the .bbl file % is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission, you *NEED* to 'insert'
% your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%

% refers to the cls file being used
\documentclass{sig-alternate-br}

\begin{document}
%
% --- Author Metadata here --- DO NOT REMOVE OR CHANGE 
\conferenceinfo{13$^{th}$ Twente Student Conference on IT}{June 21$^{st}$, 2010, Enschede, The Netherlands.}
\CopyrightYear{2010} % Allows default copyright year (200X) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{Bachelor's Student Conference Proceedings Paper in LaTeX Template}
% In Bachelor Referaat at University of Twente the use of a subtitle is discouraged.
% \subtitle{[Instructions]}

%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{1} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
1st Author\\
       \affaddr{University of Twente}\\
       \affaddr{P.O. Box 217, 7500AE Enschede}\\
       \affaddr{The Netherlands}\\
       \email{1st author's email address}
% 2nd. author
\alignauthor 2nd Author\\
       \affaddr{2nd author's affiliation}\\
       \affaddr{1st line of address}\\
       \affaddr{2nd line of address}\\
       \email{2nd author's email address}
% 3rd. author
\alignauthor 3rd Author\\
       \affaddr{3rd author's affiliation}\\
       \affaddr{1st line of address}\\
       \affaddr{2nd line of address}\\
       \email{3rd author's email address}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
\additionalauthors{Additional authors: John Smith (The
Th{\o}rv{\"a}ld Group, email: {\texttt{jsmith@affiliation.org}})
and Julius P.~Kumquat (The Kumquat Consortium, email:
{\texttt{jpkumquat@consortium.net}}).}
\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
In this paper, we describe the formatting guidelines for ACM SIG Proceedings.  
\end{abstract}

% A category with the (minimum) three required fields (NOT USED in Bachelor Referaat)
% \category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
% \category{D.2.8}{Software Engineering}{Metrics}[complexity
% measures, performance measures]

\keywords{Keywords are your own designated keywords.}

\section{Introduction}
The \textit{proceedings} are the records of the conference. ACM 
hopes to give these conference by-products a single, high-quality
appearance. To do this, we ask that authors follow some simple 
guidelines. In essence, we ask you to make your paper look exactly 
like this document. The easiest way to do this is simply to down-load 
a template and replace the content with your own material.

\section{Page size}
All material on each page should fit within a rectangle centered on 
the page, beginning 2.54 cm (1") from the top of the page and ending 
with 2.54 cm (1") from the bottom.  The right and left margins should be 
1.9 cm (.75").  The text should be in two 8.18 cm columns with a .83 cm 
(.33") gutter. Page format is International A4.

\section{Typeset text}
\subsection{Normal or body text}
Please use a 9-point Times Roman font, or other Roman font with 
serifs, as close as possible in appearance to Times Roman in which 
these guidelines have been set. The goal is to have a 9-point text, 
as you see here. Please use sans-serif or non-proportional fonts 
only for special purposes, such as distinguishing source code text. 
If Times Roman is not available, try the font named Computer Modern
Roman. On a Macintosh, use the font named Times. Right margins 
should be justified, not ragged.

\subsection{Title and authors}
The title (Helvetica 18-point bold), authors' names (Helvetica 
12-point) and affiliations (Helvetica 10-point) run across the full 
width of the page - one column wide. We also recommend an  e-mail 
address (Helvetica 12-point). See the top of this page for three 
addresses. If only one address is needed, center all address text. 
For two addresses, use two centered tabs, and so on.

\subsection{First Page Copyright Notice}
Please leave the Copyright Notice on the first page as it is but 
change the date and the number of the conference, if necessary.

\subsection{Subsequent Pages}
For pages other than the first page, start at the top of the page, and 
continue in double-column format.  The two columns on the last page 
should be as close to equal length as possible.

\begin{table}
\centering \caption{Table captions should be placed above the table}
\begin{tabular}{|c|c|c|c|} \hline
\textbf{Graphics} & \textbf{Top} & \textbf{In-between} & \textbf{Bottom}\\ \hline 
Tables&End&Last&First\\ \hline 
Figures&Good&Similar&Very well\\
\hline\end{tabular}
\end{table}

\subsection{References and Citations}
Footnotes should be Times New Roman 9-point, and justified to the 
full width of the column.\footnote{A footnote in 9-point Times New Roman.}

Use the "ACM Reference format" for references - that is, a numbered 
list at the end of the article, ordered alphabetically and formatted 
accordingly. See examples of some typical reference types, in the new 
"ACM Reference format", at the end of this document. Within this 
template, use the style named references for the text. Acceptable 
abbreviations, for journal names, can be found here: 
http://library.caltech.edu/reference/abbreviations/

The references are also in 9 pt., but that section (see Section 7) is 
ragged right. References should be published materials accessible to 
the public. Internal technical reports may be cited only if they are 
easily accessible (i.e. you can give the address to obtain the report 
within your citation) and may be obtained by any reader. Proprietary
information may not be cited. Private communications should be 
acknowledged, not referenced  (e.g., "[Robertson, personal communication]")

\subsection{Page Numbering, Headers and Footers}
Do not include headers, footers or page numbers in your submission. 
These will be added when the publications are assembled.

\section{Figures / Captions}
Place Tables/Figures/Images in text as close to the reference as possible 
(See Figure \ref{fig:abc}).  It may extend across both columns.

\begin{figure}
\centering 
\epsfig{file=fly2.eps} 
\caption{Insert caption to place below figure.}
\label{fig:abc} %always place your label after your caption!
\end{figure}

Captions should be Times New Roman 9-point bold.  They should be numbered (e.g., "Table 1" or "Figure 2"), please note that the word for Table and Figure are spelled out. Figure's captions should be centered beneath the image or picture, and Table captions should be centered above the table body.

\section{Sections}
The heading of a section should be in Times New Roman 12-point bold in all-capitals flush left with an additional 6-points of white space above the section head.  Sections and subsequent sub- sections should be numbered and flush left. For a section head and a subsection head together (such as Section 3 and subsection 3.1), use no additional space above the subsection head.

\subsection{Subsections}
The heading of subsections should be in Times New Roman 12-point bold with only the initial letters capitalized. (Note: For subsections and subsubsections, a word like the or a is not capitalized unless it is the first word of the header.)

\subsubsection{Subsubsections}
The heading for subsubsections should be in Times New Roman 11-point italic with initial letters capitalized and 6-points of white space above the subsubsection head.

\section{Acknowledgments}
Our thanks to ACM SIGCHI for allowing us to modify templates they had developed.

\section{Introduction to Latex}
Typically, the body of a paper is organized into a hierarchical
structure, with numbered or unnumbered headings for sections,
subsections, sub-subsections, and even smaller sections.  The
command \texttt{{\char'134}section} that precedes this paragraph
is part of such a hierarchy. \LaTeX\ handles the numbering and placement of these
headings for you, when you use the appropriate heading commands
around the titles of the headings.  If you want a sub-subsection
or smaller part to be unnumbered in your output, simply append an
asterisk to the command name.  Examples of both numbered and
unnumbered headings will appear throughout the balance of this
sample document.

Because the entire article is contained in the \textbf{document}
environment, you can indicate the start of a new paragraph with a
blank line in your input file; that is why this sentence forms a
separate paragraph.

\subsection{Type Changes and {\subsecit Special} Characters}
We have already seen several typeface changes in this sample.  You
can indicate italicized words or phrases in your text with the
command \texttt{{\char'134}textit}; emboldening with the command
\texttt{{\char'134}textbf} and typewriter-style (for instance, for
computer code) with \texttt{{\char'134}texttt}.  But remember, you
do not have to indicate typestyle changes when such changes are
part of the \textit{structural} elements of your article; for
instance, the heading of this subsection will be in a sans
serif\footnote{A third footnote, here. Let's make this a rather
short one to see how it looks.} typeface, but that is handled by
the document class file. Take care with the use of\footnote{A
fourth, and last, footnote.} the curly braces in typeface changes;
they mark the beginning and end of the text that is to be in the
different typeface.

You can use whatever symbols, accented characters, or non-English
characters you need anywhere in your document; you can find a
complete list of what is available in the \textit{\LaTeX\ User's
Guide}\cite{Lamport:LaTeX}.

\subsection{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of the three are
discussed in the next sections.

\subsubsection{Inline (In-text) Equations}
A formula that appears in the running text is called an inline or
in-text formula.  It is produced by the \textbf{math} environment,
which can be invoked with the usual \texttt{{\char'134}begin. .
.{\char'134}end} construction or with the short form \texttt{\$. .
.\$}. You can use any of the symbols and structures, from $\alpha$
to $\omega$, available in \LaTeX\cite{Lamport:LaTeX}; this section
will simply show a few examples of in-text equations in context.
Notice how this equation: \begin{math}\lim_{n\rightarrow
\infty}x=0\end{math}, set here in in-line math style, looks
slightly different when set in display style.  (See next section).

\subsubsection{Display Equations}
A numbered display equation -- one set off by vertical space from
the text and centered horizontally -- is produced by the
\textbf{equation} environment. An unnumbered display equation is
produced by the \textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols and
structures available in \LaTeX; this section will just give a
couple of examples of display equations in context. First,
consider the equation, shown as an inline equation above:
\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
Notice how it is formatted somewhat differently in the
\textbf{displaymath} environment.  Now, we'll enter an unnumbered
equation:
\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
and follow it with another numbered equation:
\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\subsection{Citations}
Citations to articles \cite{bowman:reasoning, clark:pct,
braams:babel, herlihy:methodology}, conference proceedings
\cite{clark:pct} or books \cite{salas:calculus, Lamport:LaTeX}
listed in the Bibliography section of your article will occur
throughout the text of your article. You should use BibTeX to
automatically produce this bibliography; you simply need to insert
one of several citation commands with a key of the item cited in
the proper location in the \texttt{.tex} file
\cite{Lamport:LaTeX}. The key is a short reference you invent to
uniquely identify each work; in this sample document, the key is
the first author's surname and a word from the title.  This
identifying key is included with each item in the \texttt{.bib}
file for your article.

The details of the construction of the \texttt{.bib} file are
beyond the scope of this sample document, but more information can
be found in the \textit{Author's Guide}, and exhaustive details in
the \textit{\LaTeX\ User's Guide}\cite{Lamport:LaTeX}.

This article shows only the plainest form of the citation command,
using \texttt{{\char'134}cite}. This is what is stipulated in the
SIGS style specifications. No other citation format is endorsed or
supported.

\subsection{Tables}
Because tables cannot be split across pages, the best placement
for them is typically the top of the page nearest their initial
cite.  To ensure this proper ``floating'' placement of tables, use
the environment \textbf{table} to enclose the table's contents and
the table caption.  The contents of the table itself must go in
the \textbf{tabular} environment, to be aligned properly in rows
and columns, with the desired horizontal and vertical rules.
Again, detailed instructions on \textbf{tabular} material is found
in the \textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which Table 1
is included in the input file; compare the placement of the table
here with the table in the printed dvi output of this document.

\begin{table}
\centering \caption{Frequency of Special Characters}
\begin{tabular}{|c|c|l|} \hline
Non-English or Math&Frequency&Comments\\ \hline \O & 1 in 1,000&
For Swedish names\\ \hline $\pi$ & 1 in 5& Common in math\\ \hline
\$ & 4 in 5 & Used in business\\ \hline
$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
\hline\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of the page's
live area, use the environment \textbf{table*} to enclose the
table's contents and the table caption.  As with a single-column
table, this wide table will ``float" to a location deemed more
desirable. Immediately following this sentence is the point at
which Table 2 is included in the input file; again, it is
instructive to compare the placement of the table here with the
table in the printed dvi output of this document.

\begin{table*}
\centering \caption{Some Typical Commands}
\begin{tabular}{|c|c|l|} \hline
Command&A Number&Comments\\ \hline \texttt{{\char'134}alignauthor}
& 100& Author alignment\\ \hline
\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\
\hline \texttt{{\char'134}table}& 300 & For tables\\ \hline
\texttt{{\char'134}table*}& 400& For wider tables\\
\hline\end{tabular}
\end{table*}
% end the environment with {table*}, NOTE not {table}!

\subsection{Figures}
Like tables, figures cannot be split across pages; the best
placement for them is typically the top or the bottom of the page
nearest their initial cite.  To ensure this proper ``floating''
placement of figures, use the environment \textbf{figure} to
enclose the figure and its caption.

This sample document contains examples of \textbf{.eps} and
\textbf{.ps} files to be displayable with \LaTeX.  More details on
each of these is found in the \textit{Author's Guide}.

\begin{figure}
\centering \epsfig{file=fly.eps} \caption{A sample black and white
graphic (.eps format).}
\end{figure}

\begin{figure}
\centering \epsfig{file=fly.eps, height=1in, width=1in} \caption{A
sample black and white graphic (.eps format) that has been resized
with the \texttt{epsfig} command.}
\end{figure}

As was the case with tables, you may want a figure that spans two
columns.  To do this, and still to ensure proper ``floating''
placement of tables, use the environment \textbf{figure*} to
enclose the figure and its caption.
\begin{figure*}
\centering \epsfig{file=flies.eps} \caption{A sample black and
white graphic (.eps format) that needs to span two columns of
text.}
\end{figure*}
and don't forget to end the environment with {figure*}, not
{figure}!

Note that either {\textbf{.ps}} or {\textbf{.eps}} formats are
used; use the \texttt{{\char'134}epsfig} or
\texttt{{\char'134}psfig} commands as appropriate for the
different file types.

\begin{figure}
\centering \psfig{file=rosette.ps, height=1in, width=1in,}
\caption{A sample black and white graphic (.ps format) that has
been resized with the \texttt{psfig} command.} \vskip -6pt
\end{figure}

\subsection{Theorem-like Constructs}
Other common constructs that may occur in your article are the
forms for logical constructs like theorems, axioms, corollaries
and proofs.  There are two forms, one produced by the command
\texttt{{\char'134}newtheorem} and the other by the command
\texttt{{\char'134}newdef}; perhaps the clearest and easiest way
to distinguish them is to compare the two in the output of this
sample document:

This uses the \textbf{theorem} environment, created by
the\linebreak\texttt{{\char'134}newtheorem} command:
\newtheorem{theorem}{Theorem}
\begin{theorem}
Let $f$ be continuous on $[a,b]$.  If $G$ is an antiderivative for
$f$ on $[a,b]$, then
\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
\end{theorem}

The other uses the \textbf{definition} environment, created by the
\texttt{{\char'134}newdef} command:
\newdef{definition}{Definition}
\begin{definition}
If $z$ is irrational, then by $e^z$ we mean the unique number
which has logarithm $z$: \begin{displaymath}{\log e^z =
z}\end{displaymath}
\end{definition}

Two lists of constructs that use one of these forms is given in
the \textit{Author's  Guidelines}.

There is one other similar construct environment, which is already
set up for you; i.e. you must \textit{not} use a
\texttt{{\char'134}newdef} command to create it: the
\textbf{proof} environment.  Here is a example of its use:
\begin{proof}
Suppose on the contrary there exists a real number $L$ such that
\begin{displaymath}
\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
\end{displaymath}
Then
\begin{displaymath}
l=\lim_{x\rightarrow c} f(x) = \lim_{x\rightarrow c} \left[ g{x}
\cdot \frac{f(x)}{g(x)} \right ] = \lim_{x\rightarrow c} g(x)
\cdot \lim_{x\rightarrow c} \frac{f(x)}{g(x)} = 0\cdot L = 0,
\end{displaymath}
which contradicts our assumption that $l\neq 0$.
\end{proof}

Complete rules about using these environments and using the two
different creation commands are in the \textit{Author's Guide};
please consult it for more detailed instructions.  If you need to
use another construct, not listed therein, which you want to have
the same formatting as the Theorem or the
Definition\cite{salas:calculus} shown above, use the
\texttt{{\char'134}newtheorem} or the \texttt{{\char'134}newdef}
command, respectively, to create it.

\subsection*{A {\secit Caveat} for the \TeX\ Expert}
Because you have just been given permission to use the
\texttt{{\char'134}newdef} command to create a new form, you might
think you can use \TeX's \texttt{{\char'134}def} to create a new
command: \textit{Please refrain from doing this!} Remember that
your \LaTeX\ source code is primarily intended to create
camera-ready copy, but may be converted to other forms -- e.g.
HTML. If you inadvertently omit some or all of the
\texttt{{\char'134}def}s recompilation will be, to say the least,
problematic.

\section{Conclusions}
This paragraph will end the body of this sample document. Remember
that you might still have Acknowledgments or Appendices; brief
samples of these follow.  There is still the Bibliography to deal
with; and we will make a disclaimer about that here: with the
exception of the reference to the \LaTeX\ book, the citations in
this paper are to articles which have nothing to do with the
present subject and are used as examples only.
%\end{document}  % This is where a 'short' article might terminate

% Ugliest hack in human history. 
% Columns on Last Page Should Be Made As Close As Possible to Equal Length
\vspace{70 mm}
.
\vspace{10 mm}

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This section is optional; it is a location for you to acknowledge
grants, funding, editing assistance and what have you.  In the
present case, for example, the authors would like to thank Gerald
Murray of ACM for his help in codifying this \textit{Author's
Guide} and the \textbf{.cls} and \textbf{.tex} files that it
describes.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.

\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
\vspace{50 mm}
\newpage
%APPENDICES are optional

\appendix
%Appendix A
\section{Headings in Appendices}
The rules about hierarchical headings discussed above for the body
of the article are different in the appendices. In the
\textbf{appendix} environment, the command \textbf{section} is
used to indicate the start of each Appendix, with alphabetic order
designation (i.e. the first is A, the second B, etc.) and a title
(if you include one).  So, if you need hierarchical structure
\textit{within} an Appendix, start with \textbf{subsection} as the
highest level. Here is an outline of the body of this document in
Appendix-appropriate form:
\subsection{Introduction}
\subsection{The Body of the Paper}
\subsubsection{Type Changes and  Special Characters}
\subsubsection{Math Equations}
\paragraph{Inline (In-text) Equations}
\paragraph{Display Equations}
\subsubsection{Citations}
\subsubsection{Tables}
\subsubsection{Figures}
\subsubsection{Theorem-like Constructs}
\subsubsection*{A Caveat for the \TeX\ Expert}
\subsection{Conclusions}
\subsection{Acknowledgments}
\subsection{Additional Authors}
This section is inserted by \LaTeX; you do not insert it. You just
add the names and information in the
\texttt{{\char'134}additionalauthors} command at the start of the
document.
\subsection{References}
Generated by bibtex from your ~.bib file.  Run latex, then bibtex,
then latex twice (to resolve references) to create the ~.bbl file.
Insert that ~.bbl file into the .tex source file and comment out
the command \texttt{{\char'134}thebibliography}.
% This next section command marks the start of
% Appendix B, and does not continue the present hierarchy
\section{More Help for the Hardy}
The sig-alternate.cls file itself is chock-full of succinct and
helpful comments.  If you consider yourself a moderately
experienced to expert user of \LaTeX, you may find reading it
useful but please remember not to change it.
%\balancecolumns % GM June 2007
% That's all folks!

\balancecolumns
\end{document}

### 2015-02-08 research proposal/research proposal.tex
proposal
research approach

--- 2015-02-04 proposal.tex
@@
 %       5) NO headers and/or footers
-%
 %
@@
 \documentclass{sig-alternate-br}
+\usepackage{float}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{hyperref}
+\restylefloat{figure}
+\restylefloat{table}
+\begin{document}
 
-\begin{document}
 %
 % --- Author Metadata here --- DO NOT REMOVE OR CHANGE 
-\conferenceinfo{13$^{th}$ Twente Student Conference on IT}{June 21$^{st}$, 2010, Enschede, The Netherlands.}
-\CopyrightYear{2010} % Allows default copyright year (200X) to be over-ridden - IF NEED BE.
+%\conferenceinfo{13$^{th}$ Twente Student Conference on IT}{June 23$^{st}$, 2010, Enschede, The Netherlands.}
+\CopyrightYear{2015} % Allows default copyright year (200X) to be over-ridden - IF NEED BE.
 %\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
@@
 
-\title{Bachelor's Student Conference Proceedings Paper in LaTeX Template}
+\title{micro data server using raspberry pi}
 % In Bachelor Referaat at University of Twente the use of a subtitle is discouraged.
-% \subtitle{[Instructions]}
+ \subtitle{Research Proposal}
 
@@
 \alignauthor
-1st Author\\
+P.j.e. Velthuis\\
        \affaddr{University of Twente}\\
@@
        \affaddr{The Netherlands}\\
-       \email{1st author's email address}
+       \email{p.j.e.velthuis@student.utwente.nl}
 % 2nd. author
@@
 \begin{abstract}
-In this paper, we describe the formatting guidelines for ACM SIG Proceedings.  
+This document describes a draft research proposal in the
+area of cloud computing services. The main research question
+is: Is a cloud server consisting of Raspberry Pi efficient?
 \end{abstract}
@@
 
-\keywords{Keywords are your own designated keywords.}
+\keywords{Cloud computing, Raspberry Pi, ARM performance, micro data server}
 
-\section{Introduction}
-The \textit{proceedings} are the records of the conference. ACM 
-hopes to give these conference by-products a single, high-quality
-appearance. To do this, we ask that authors follow some simple 
-guidelines. In essence, we ask you to make your paper look exactly 
-like this document. The easiest way to do this is simply to down-load 
-a template and replace the content with your own material.
+\section{Motivation}
+The amount of cloud computing services is increasing fast \cite{armbrust:2009}. 
+Today there are a even some cloud Raspberry Pi services.
+The density of servers has increased a lot in the past\cite{density}.
+There are new technologies such as for example the ARM processor.
+In this research we want to look what the performance is of such  a ARM processor by using the Raspberry Pi.
+Many companies want to explore the possibilities of for example the Raspberry Pi.
+Some data centers even offer some Raspberry Pi co-location \cite{hosting,Pcextreme}.
+A good reason to do this is the very low power usage of a Raspberry Pi.
+A Raspberry Pi has a power usage between the 3-5 Watt and a server has a power usage between the 75 and 150 watt \cite{Powerusage}.
+This could mean that it is better to use a Raspberry Pi for specific small tasks that do not demand a whole server.
+During this research I want to further investigate this power usage.
+A Raspberry Pi can be the small data center for the future \cite{tso:2013}.
+The Raspberry is a rather cheap device for 35 euros.
+This makes it cheaper to do research in compared to a normal server.
+The current versions of the Raspberry Pi cannot perform the task of a large scale x86 server \cite{tso:2013}.
+Building a cloud like this can be a cost effective scale model\cite{tso:2013}.
 
-\section{Page size}
-All material on each page should fit within a rectangle centered on 
-the page, beginning 2.54 cm (1") from the top of the page and ending 
-with 2.54 cm (1") from the bottom.  The right and left margins should be 
-1.9 cm (.75").  The text should be in two 8.18 cm columns with a .83 cm 
-(.33") gutter. Page format is International A4.
+%\subsection{References and Citations}
+%Footnotes should be Times New Roman 9-point, and justified to the 
+%full width of the column.\footnote{A footnote in 9-point Times New Roman.}
 
-\section{Typeset text}
-\subsection{Normal or body text}
-Please use a 9-point Times Roman font, or other Roman font with 
-serifs, as close as possible in appearance to Times Roman in which 
-these guidelines have been set. The goal is to have a 9-point text, 
-as you see here. Please use sans-serif or non-proportional fonts 
-only for special purposes, such as distinguishing source code text. 
-If Times Roman is not available, try the font named Computer Modern
-Roman. On a Macintosh, use the font named Times. Right margins 
-should be justified, not ragged.
+%Use the "ACM Reference format" for references - that is, a numbered 
+%list at the end of the article, ordered alphabetically and formatted 
+%accordingly. See examples of some typical reference types, in the new 
+%"ACM Reference format", at the end of this document. Within this 
+%template, use the style named references for the text. Acceptable 
+%abbreviations, for journal names, can be found here: 
+%http://library.caltech.edu/reference/abbreviations/
 
-\subsection{Title and authors}
-The title (Helvetica 18-point bold), authors' names (Helvetica 
-12-point) and affiliations (Helvetica 10-point) run across the full 
-width of the page - one column wide. We also recommend an  e-mail 
-address (Helvetica 12-point). See the top of this page for three 
-addresses. If only one address is needed, center all address text. 
-For two addresses, use two centered tabs, and so on.
+%The references are also in 9 pt., but that section (see Section 7) is 
+%ragged right. References should be published materials accessible to 
+%the public. Internal technical reports may be cited only if they are 
+%easily accessible (i.e. you can give the address to obtain the report 
+%within your citation) and may be obtained by any reader. Proprietary
+%information may not be cited. Private communications should be 
+%acknowledged, not referenced  (e.g., "[Robertson, personal communication]")
 
-\subsection{First Page Copyright Notice}
-Please leave the Copyright Notice on the first page as it is but 
-change the date and the number of the conference, if necessary.
+%\subsection{Page Numbering, Headers and Footers}
+%Do not include headers, footers or page numbers in your submission. 
+%These will be added when the publications are assembled.
 
-\subsection{Subsequent Pages}
-For pages other than the first page, start at the top of the page, and 
-continue in double-column format.  The two columns on the last page 
-should be as close to equal length as possible.
+%\section{Figures / Captions}
+%Place Tables/Figures/Images in text as close to the reference as possible 
+%(See Figure \ref{fig:abc}).  It may extend across both columns.
 
-\begin{table}
-\centering \caption{Table captions should be placed above the table}
-\begin{tabular}{|c|c|c|c|} \hline
-\textbf{Graphics} & \textbf{Top} & \textbf{In-between} & \textbf{Bottom}\\ \hline 
-Tables&End&Last&First\\ \hline 
-Figures&Good&Similar&Very well\\
-\hline\end{tabular}
-\end{table}
+%\begin{figure}
+%\centering 
+%\epsfig{file=fly2.eps} 
+%\caption{Insert caption to place below figure.}
+%\label{fig:abc} %always place your label after your caption!
+\ %end{figure}
 
-\subsection{References and Citations}
-Footnotes should be Times New Roman 9-point, and justified to the 
-full width of the column.\footnote{A footnote in 9-point Times New Roman.}
-
-Use the "ACM Reference format" for references - that is, a numbered 
-list at the end of the article, ordered alphabetically and formatted 
-accordingly. See examples of some typical reference types, in the new 
-"ACM Reference format", at the end of this document. Within this 
-template, use the style named references for the text. Acceptable 
-abbreviations, for journal names, can be found here: 
-http://library.caltech.edu/reference/abbreviations/
-
-The references are also in 9 pt., but that section (see Section 7) is 
-ragged right. References should be published materials accessible to 
-the public. Internal technical reports may be cited only if they are 
-easily accessible (i.e. you can give the address to obtain the report 
-within your citation) and may be obtained by any reader. Proprietary
-information may not be cited. Private communications should be 
-acknowledged, not referenced  (e.g., "[Robertson, personal communication]")
-
-\subsection{Page Numbering, Headers and Footers}
-Do not include headers, footers or page numbers in your submission. 
-These will be added when the publications are assembled.
-
-\section{Figures / Captions}
-Place Tables/Figures/Images in text as close to the reference as possible 
-(See Figure \ref{fig:abc}).  It may extend across both columns.
-
-\begin{figure}
-\centering 
-\epsfig{file=fly2.eps} 
-\caption{Insert caption to place below figure.}
-\label{fig:abc} %always place your label after your caption!
-\end{figure}
-
-Captions should be Times New Roman 9-point bold.
+%Captions should be Times New Roman 9-point bold.
 They should be numbered (e.g., "Table 1" or "Figure 2"), please note that the word for Table and Figure are spelled out.
@@
 
-\section{Sections}
-The heading of a section should be in Times New Roman 12-point bold in all-capitals flush left with an additional 6-points of white space above the section head.
+%\section{Sections}
+%The heading of a section should be in Times New Roman 12-point bold in all-capitals flush left with an additional 6-points of white space above the section head.
 Sections and subsequent sub- sections should be numbered and flush left.
@@
 
-\subsection{Subsections}
-The heading of subsections should be in Times New Roman 12-point bold with only the initial letters capitalized.
+%\subsection{Subsections}
+%The heading of subsections should be in Times New Roman 12-point bold with only the initial letters capitalized.
 (Note: For subsections and subsubsections, a word like the or a is not capitalized unless it is the first word of the header.)
 
-\subsubsection{Subsubsections}
-The heading for subsubsections should be in Times New Roman 11-point italic with initial letters capitalized and 6-points of white space above the subsubsection head.
+%\subsubsection{Subsubsections}
+%The heading for subsubsections should be in Times New Roman 11-point italic with initial letters capitalized and 6-points of white space above the subsubsection head.
 
-\section{Acknowledgments}
-Our thanks to ACM SIGCHI for allowing us to modify templates they had developed.
+%\section{Acknowledgments}
+%Our thanks to ACM SIGCHI for allowing us to modify templates they had developed.
 
-\section{Introduction to Latex}
-Typically, the body of a paper is organized into a hierarchical
-structure, with numbered or unnumbered headings for sections,
-subsections, sub-subsections, and even smaller sections.  The
-command \texttt{{\char'134}section} that precedes this paragraph
-is part of such a hierarchy. \LaTeX\ handles the numbering and placement of these
-headings for you, when you use the appropriate heading commands
-around the titles of the headings.  If you want a sub-subsection
-or smaller part to be unnumbered in your output, simply append an
-asterisk to the command name.  Examples of both numbered and
-unnumbered headings will appear throughout the balance of this
-sample document.
+%\section{Introduction to Latex}
+%Typically, the body of a paper is organized into a hierarchical
+%structure, with numbered or unnumbered headings for sections,
+%subsections, sub-subsections, and even smaller sections.  The
+%command \texttt{{\char'134}section} that precedes this paragraph
+%is part of such a hierarchy. \LaTeX\ handles the numbering and placement of these
+%headings for you, when you use the appropriate heading commands
+%around the titles of the headings.  If you want a sub-subsection
+%or smaller part to be unnumbered in your output, simply append an
+%asterisk to the command name.  Examples of both numbered and
+%unnumbered headings will appear throughout the balance of this
+%sample document.
 
-Because the entire article is contained in the \textbf{document}
-environment, you can indicate the start of a new paragraph with a
-blank line in your input file; that is why this sentence forms a
-separate paragraph.
+%Because the entire article is contained in the \textbf{document}
+%environment, you can indicate the start of a new paragraph with a
+%blank line in your input file; that is why this sentence forms a
+%separate paragraph.
 
-\subsection{Type Changes and {\subsecit Special} Characters}
-We have already seen several typeface changes in this sample.  You
-can indicate italicized words or phrases in your text with the
-command \texttt{{\char'134}textit}; emboldening with the command
-\texttt{{\char'134}textbf} and typewriter-style (for instance, for
-computer code) with \texttt{{\char'134}texttt}.  But remember, you
-do not have to indicate typestyle changes when such changes are
-part of the \textit{structural} elements of your article; for
-instance, the heading of this subsection will be in a sans
-serif\footnote{A third footnote, here. Let's make this a rather
-short one to see how it looks.} typeface, but that is handled by
-the document class file. Take care with the use of\footnote{A
-fourth, and last, footnote.} the curly braces in typeface changes;
-they mark the beginning and end of the text that is to be in the
-different typeface.
+%\subsection{Type Changes and {\subsecit Special} Characters}
+%We have already seen several typeface changes in this sample.  You
+%can indicate italicized words or phrases in your text with the
+%command \texttt{{\char'134}textit}; emboldening with the command
+%\texttt{{\char'134}textbf} and typewriter-style (for instance, for
+%computer code) with \texttt{{\char'134}texttt}.  But remember, you
+%do not have to indicate typestyle changes when such changes are
+%part of the \textit{structural} elements of your article; for
+%instance, the heading of this subsection will be in a sans
 
-You can use whatever symbols, accented characters, or non-English
-characters you need anywhere in your document; you can find a
-complete list of what is available in the \textit{\LaTeX\ User's
-Guide}\cite{Lamport:LaTeX}.
+\section{Research questions}
+The main research question
+is: Is a cloud server consisting of Raspberry Pi efficient?
 
-\subsection{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of the three are
-discussed in the next sections.
-
-\subsubsection{Inline (In-text) Equations}
-A formula that appears in the running text is called an inline or
-in-text formula.  It is produced by the \textbf{math} environment,
-which can be invoked with the usual \texttt{{\char'134}begin. .
-.{\char'134}end} construction or with the short form \texttt{\$. .
-.\$}. You can use any of the symbols and structures, from $\alpha$
-to $\omega$, available in \LaTeX\cite{Lamport:LaTeX}; this section
-will simply show a few examples of in-text equations in context.
-Notice how this equation: \begin{math}\lim_{n\rightarrow
-\infty}x=0\end{math}, set here in in-line math style, looks
-slightly different when set in display style.  (See next section).
-
-\subsubsection{Display Equations}
-A numbered display equation -- one set off by vertical space from
-the text and centered horizontally -- is produced by the
-\textbf{equation} environment. An unnumbered display equation is
-produced by the \textbf{displaymath} environment.
-
-Again, in either environment, you can use any of the symbols and
-structures available in \LaTeX; this section will just give a
-couple of examples of display equations in context. First,
-consider the equation, shown as an inline equation above:
-\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
-Notice how it is formatted somewhat differently in the
-\textbf{displaymath} environment.  Now, we'll enter an unnumbered
-equation:
-\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
+In order to come to a good answer we first need to build our own Raspberry Pi setup.
+There needs to be decided with which benchmark the performance will be measured.
+After we have measured the performance we can see
 
@@
 supported.
+\subsection{What cloud services are there}
+Eucalyptus https://www.eucalyptus.com/eucalyptus-cloud/get-started
+Hazelcast
 
-\subsection{Tables}
-Because tables cannot be split across pages, the best placement
-for them is typically the top of the page nearest their initial
-cite.  To ensure this proper ``floating'' placement of tables, use
-the environment \textbf{table} to enclose the table's contents and
-the table caption.  The contents of the table itself must go in
-the \textbf{tabular} environment, to be aligned properly in rows
-and columns, with the desired horizontal and vertical rules.
-Again, detailed instructions on \textbf{tabular} material is found
-in the \textit{\LaTeX\ User's Guide}.
+\subsection{What cloud services are already running on Raspberry pi}
+In the PcExtreme article \cite{Pcextreme} there are running several services on a Raspberry Pi.
+For example a webserver, a DNS server, a chat server, a mail server, a vpn server or a monitoring server.
 
-Immediately following this sentence is the point at which Table 1
-is included in the input file; compare the placement of the table
-here with the table in the printed dvi output of this document.
+\subsection{What are the main characteristics of a Raspberry Pi cloud computer}
+
+\subsection{What software can be used for a Raspberry Pi cloud}
+To investigate this I want to make a experimentation cloud with Raspberry Pi's to see if it will work as a cloud.
+
+\subsection{Is it reachable to build small personal Raspberry Pi clouds for server}
+With this subquestion I want to find out if it is possible to let users have small Raspberry Pi servers such as now is happening at PcExtreme as an experiment.
+
+\section{Research approach}
+For the experiment we need a Raspberry Pi with a static Ip address and we need a sd card for the OS.
+A Raspberry Pi can be used as a webserver or DNS server.
+For the experiment we need a Raspberry Pi B that can make use of the Ethernet.
+
+Experiment making a VPN:
+\url{http://readwrite.com/2014/04/10/raspberry-pi-vpn-tutorial-server-secure-web-browsing}
+
+Glasgow Raspberry Pi
+\url{http://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=6679872}
+Limited software:
+lightweight,
+httpd,
+servers, 
+hadoop
+
+ICanCloud is a cloud simulation program.
+
+\url{http://www.lighttpd.net/}
+
+Raspberry Pi project Glasgow
+\url{https://raspberrypicloud.wordpress.com/}
+Runs Linux from sanddisk 16 gb
+
+Owncloud
+Data storage like dropbox
 
 \begin{table}
-\centering \caption{Frequency of Special Characters}
-\begin{tabular}{|c|c|l|} \hline
-Non-English or Math&Frequency&Comments\\ \hline \O & 1 in 1,000&
-For Swedish names\\ \hline $\pi$ & 1 in 5& Common in math\\ \hline
-\$ & 4 in 5 & Used in business\\ \hline
-$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-\hline\end{tabular}
+	\centering \caption{Cost breakdown of a testbed consisting 56 servers}
+
+\begin{tabular}{|c|c|c|} \hline
+\textbf{Server}&  \textbf{Power} \textbf{Needs Cooling?} \\ \hline
+Testbed  & $112,000 (@$2,000) 10,080W/h (@180W/h) & Yes \\ \hline
+PiCloud & $1,960 (@$35) 196W/h (@3.5W/h) & No \\ \hline
+\end{tabular}
+\label{tab:cost}
 \end{table}
 
-To set a wider table, which takes up the whole width of the page's
-live area, use the environment \textbf{table*} to enclose the
-table's contents and the table caption.  As with a single-column
-table, this wide table will ``float" to a location deemed more
-desirable. Immediately following this sentence is the point at
-which Table 2 is included in the input file; again, it is
-instructive to compare the placement of the table here with the
-table in the printed dvi output of this document.
+\section{Planning}
 
-\begin{table*}
-\centering \caption{Some Typical Commands}
-\begin{tabular}{|c|c|l|} \hline
-Command&A Number&Comments\\ \hline \texttt{{\char'134}alignauthor}
-& 100& Author alignment\\ \hline
-\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\
-\hline \texttt{{\char'134}table}& 300 & For tables\\ \hline
-\texttt{{\char'134}table*}& 400& For wider tables\\
-\hline\end{tabular}
-\end{table*}
-% end the environment with {table*}, NOTE not {table}!
+Hallootjes
+\begin{table}
+	\centering \caption{Planning}
+	\begin{tabular}{|c|c|c|} \hline
+		\textbf{Week} & \textbf{Date} & \textbf{Activity} \\ \hline 
+		6-7&6 Feb. -15 Feb&Collect literature and software\\ \hline 
+		11-14&5 March 12 April&Start building test environment\\ \hline
+		14&6 April - 12 April&Answer subquestion 1\\ \hline
+		15&13 April - 20 April&Answer subquestion 2\\ \hline
+		16&21 April - 28April&Answer subquestion 3\\ \hline
+		18&4 May-10 May& conclusion and check coherency \\ \hline
+		19&11 May-18 May& Finalize paper \\ \hline
+		\end{tabular}
+		\label{tab:planning}
+\end{table}
+Here above is the ~\ref{tab:planning}.
 
-\subsection{Figures}
-Like tables, figures cannot be split across pages; the best
-placement for them is typically the top or the bottom of the page
-nearest their initial cite.  To ensure this proper ``floating''
-placement of figures, use the environment \textbf{figure} to
-enclose the figure and its caption.
-
-This sample document contains examples of \textbf{.eps} and
-\textbf{.ps} files to be displayable with \LaTeX.  More details on
-each of these is found in the \textit{Author's Guide}.
-
-\begin{figure}
-\centering \epsfig{file=fly.eps} \caption{A sample black and white
-graphic (.eps format).}
-\end{figure}
-
-\begin{figure}
-\centering \epsfig{file=fly.eps, height=1in, width=1in} \caption{A
-sample black and white graphic (.eps format) that has been resized
-with the \texttt{epsfig} command.}
-\end{figure}
-
-As was the case with tables, you may want a figure that spans two
-columns.  To do this, and still to ensure proper ``floating''
-placement of tables, use the environment \textbf{figure*} to
-enclose the figure and its caption.
-\begin{figure*}
-\centering \epsfig{file=flies.eps} \caption{A sample black and
-white graphic (.eps format) that needs to span two columns of
-text.}
-\end{figure*}
-and don't forget to end the environment with {figure*}, not
-{figure}!
-
-Note that either {\textbf{.ps}} or {\textbf{.eps}} formats are
-used; use the \texttt{{\char'134}epsfig} or
-\texttt{{\char'134}psfig} commands as appropriate for the
-different file types.
-
-\begin{figure}
-\centering \psfig{file=rosette.ps, height=1in, width=1in,}
-\caption{A sample black and white graphic (.ps format) that has
-been resized with the \texttt{psfig} command.} \vskip -6pt
-\end{figure}
-
-\subsection{Theorem-like Constructs}
-Other common constructs that may occur in your article are the
-forms for logical constructs like theorems, axioms, corollaries
-and proofs.  There are two forms, one produced by the command
-\texttt{{\char'134}newtheorem} and the other by the command
-\texttt{{\char'134}newdef}; perhaps the clearest and easiest way
-to distinguish them is to compare the two in the output of this
-sample document:
-
-This uses the \textbf{theorem} environment, created by
-the\linebreak\texttt{{\char'134}newtheorem} command:
-\newtheorem{theorem}{Theorem}
-\begin{theorem}
-Let $f$ be continuous on $[a,b]$.  If $G$ is an antiderivative for
-$f$ on $[a,b]$, then
-\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
-\end{theorem}
-
-The other uses the \textbf{definition} environment, created by the
-\texttt{{\char'134}newdef} command:
-\newdef{definition}{Definition}
-\begin{definition}
-If $z$ is irrational, then by $e^z$ we mean the unique number
-which has logarithm $z$: \begin{displaymath}{\log e^z =
-z}\end{displaymath}
-\end{definition}
-
-Two lists of constructs that use one of these forms is given in
-the \textit{Author's  Guidelines}.
-
-There is one other similar construct environment, which is already
-set up for you; i.e. you must \textit{not} use a
-\texttt{{\char'134}newdef} command to create it: the
-\textbf{proof} environment.  Here is a example of its use:
-\begin{proof}
-Suppose on the contrary there exists a real number $L$ such that
-\begin{displaymath}
-\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
-\end{displaymath}
-Then
-\begin{displaymath}
-l=\lim_{x\rightarrow c} f(x) = \lim_{x\rightarrow c} \left[ g{x}
-\cdot \frac{f(x)}{g(x)} \right ] = \lim_{x\rightarrow c} g(x)
-\cdot \lim_{x\rightarrow c} \frac{f(x)}{g(x)} = 0\cdot L = 0,
-\end{displaymath}
-which contradicts our assumption that $l\neq 0$.
-\end{proof}
-
-Complete rules about using these environments and using the two
-different creation commands are in the \textit{Author's Guide};
-please consult it for more detailed instructions.  If you need to
-use another construct, not listed therein, which you want to have
-the same formatting as the Theorem or the
-Definition\cite{salas:calculus} shown above, use the
-\texttt{{\char'134}newtheorem} or the \texttt{{\char'134}newdef}
-command, respectively, to create it.
-
-\subsection*{A {\secit Caveat} for the \TeX\ Expert}
-Because you have just been given permission to use the
-\texttt{{\char'134}newdef} command to create a new form, you might
-think you can use \TeX's \texttt{{\char'134}def} to create a new
-command: \textit{Please refrain from doing this!} Remember that
-your \LaTeX\ source code is primarily intended to create
-camera-ready copy, but may be converted to other forms -- e.g.
-HTML. If you inadvertently omit some or all of the
-\texttt{{\char'134}def}s recompilation will be, to say the least,
-problematic.
-
-\section{Conclusions}
-This paragraph will end the body of this sample document. Remember
-that you might still have Acknowledgments or Appendices; brief
-samples of these follow.  There is still the Bibliography to deal
-with; and we will make a disclaimer about that here: with the
-exception of the reference to the \LaTeX\ book, the citations in
-this paper are to articles which have nothing to do with the
-present subject and are used as examples only.
-%\end{document}  % This is where a 'short' article might terminate
-
-% Ugliest hack in human history. 
-% Columns on Last Page Should Be Made As Close As Possible to Equal Length
-\vspace{70 mm}
-.
-\vspace{10 mm}
-
-%ACKNOWLEDGMENTS are optional
-\section{Acknowledgments}
-This section is optional; it is a location for you to acknowledge
-grants, funding, editing assistance and what have you.  In the
-present case, for example, the authors would like to thank Gerald
-Murray of ACM for his help in codifying this \textit{Author's
-Guide} and the \textbf{.cls} and \textbf{.tex} files that it
-describes.
+\section{State of the Art}
 
@@
 
-\appendix
-%Appendix A
-\section{Headings in Appendices}
-The rules about hierarchical headings discussed above for the body
-of the article are different in the appendices. In the
-\textbf{appendix} environment, the command \textbf{section} is
-used to indicate the start of each Appendix, with alphabetic order
-designation (i.e. the first is A, the second B, etc.) and a title
-(if you include one).  So, if you need hierarchical structure
-\textit{within} an Appendix, start with \textbf{subsection} as the
-highest level. Here is an outline of the body of this document in
-Appendix-appropriate form:
-\subsection{Introduction}
-\subsection{The Body of the Paper}
-\subsubsection{Type Changes and  Special Characters}
-\subsubsection{Math Equations}
-\paragraph{Inline (In-text) Equations}
-\paragraph{Display Equations}
-\subsubsection{Citations}
-\subsubsection{Tables}
-\subsubsection{Figures}
-\subsubsection{Theorem-like Constructs}
-\subsubsection*{A Caveat for the \TeX\ Expert}
-\subsection{Conclusions}
-\subsection{Acknowledgments}
-\subsection{Additional Authors}
-This section is inserted by \LaTeX; you do not insert it. You just
-add the names and information in the
-\texttt{{\char'134}additionalauthors} command at the start of the
-document.
-\subsection{References}
-Generated by bibtex from your ~.bib file.  Run latex, then bibtex,
-then latex twice (to resolve references) to create the ~.bbl file.
-Insert that ~.bbl file into the .tex source file and comment out
-the command \texttt{{\char'134}thebibliography}.
-% This next section command marks the start of
-% Appendix B, and does not continue the present hierarchy
-\section{More Help for the Hardy}
-The sig-alternate.cls file itself is chock-full of succinct and
-helpful comments.  If you consider yourself a moderately
-experienced to expert user of \LaTeX, you may find reading it
-useful but please remember not to change it.
-%\balancecolumns % GM June 2007
-% That's all folks!
-
-\balancecolumns
 \end{document}

### 2015-02-12 research proposal/research proposal.tex
bachelor proposal

@@
 
-%
-% You need the command \numberofauthors to handle the 'placement
-% and alignment' of the authors beneath the title.
-%
-% For aesthetic reasons, we recommend 'three authors at a time'
-% i.e. three 'name/affiliation blocks' be placed beneath the title.
-%
-% NOTE: You are NOT restricted in how many 'rows' of
-% "name/affiliations" may appear. We just ask that you restrict
-% the number of 'columns' to three.
-%
-% Because of the available 'opening page real-estate'
-% we ask you to refrain from putting more than six authors
-% (two rows with three columns) beneath the article title.
-% More than six makes the first-page appear very cluttered indeed.
-%
-% Use the \alignauthor commands to handle the names
-% and affiliations for an 'aesthetic maximum' of six authors.
-% Add names, affiliations, addresses for
-% the seventh etc. author(s) as the argument for the
-% \additionalauthors command.
-% These 'additional authors' will be output/set for you
-% without further effort on your part as the last section in
-% the body of your article BEFORE References or any Appendices.
-
-\numberofauthors{1} %  in this sample file, there are a *total*
-% of EIGHT authors. SIX appear on the 'first-page' (for formatting
-% reasons) and the remaining two appear in the \additionalauthors section.
-%
+\numberofauthors{1} 
 \author{ 
@@
 % 1st. author
-\alignauthor
-P.j.e. Velthuis\\
+\alignauthor P.j.e. Velthuis\\
        \affaddr{University of Twente}\\
@@
 }
-% There's nothing stopping you putting the seventh, eighth, etc.
-% author on the opening page (as the 'third row') but we ask,
-% for aesthetic reasons that you place these 'additional authors'
-% in the \additional authors block, viz.
-\additionalauthors{Additional authors: John Smith (The
-Th{\o}rv{\"a}ld Group, email: {\texttt{jsmith@affiliation.org}})
-and Julius P.~Kumquat (The Kumquat Consortium, email:
-{\texttt{jpkumquat@consortium.net}}).}
-\date{30 July 1999}
-% Just remember to make sure that the TOTAL number of authors
-% is the number that will appear on the first page PLUS the
-% number that will appear in the \additionalauthors section.
+
+%\additionalauthors{Additional authors: John Smith (The
+%Th{\o}rv{\"a}ld Group, email: {\texttt{jsmith@affiliation.org}})
+%and Julius P.~Kumquat (The Kumquat Consortium, email:
+%{\texttt{jpkumquat@consortium.net}}).}
+%\date{30 July 1999}
 
@@
 
-% A category with the (minimum) three required fields (NOT USED in Bachelor Referaat)
-% \category{H.4}{Information Systems Applications}{Miscellaneous}
-%A category including the fourth, optional field follows...
-% \category{D.2.8}{Software Engineering}{Metrics}[complexity
-% measures, performance measures]
-
 \keywords{Cloud computing, Raspberry Pi, ARM performance, micro data server}
@@
 \section{Motivation}
-The amount of cloud computing services is increasing fast \cite{armbrust:2009}. 
-Today there are a even some cloud Raspberry Pi services.
-The density of servers has increased a lot in the past\cite{density}.
+Today there are many cloud services. The amount of cloud computing services is increasing fast \cite{armbrust:2009}.  Despite the attention
+from the research community, research and development of
+Cloud Computing services is still in it's childhood\cite{tso:2013}. 
+ In this research the Raspberry Pi cloud services will be investigated.
+A reason for this is that the density of servers has increased a lot in the past\cite{density}.
 There are new technologies such as for example the ARM processor.
-In this research we want to look what the performance is of such  a ARM processor by using the Raspberry Pi.
-Many companies want to explore the possibilities of for example the Raspberry Pi.
-Some data centers even offer some Raspberry Pi co-location \cite{hosting,Pcextreme}.
-A good reason to do this is the very low power usage of a Raspberry Pi.
+Many companies want to explore the possibilities of for example the Raspberry Pi and his ARM Processor.
+Some data centers even offer some cloud computing using the Raspberry Pi.
+A reason for this is the co-location and the low power usage of a Raspberry Pi\cite{hosting,Pcextreme}.
 A Raspberry Pi has a power usage between the 3-5 Watt and a server has a power usage between the 75 and 150 watt \cite{Powerusage}.
@@
 Building a cloud like this can be a cost effective scale model\cite{tso:2013}.
+It's a Ideal testbed for testing distributed software.
 
@@
 supported.
-\subsection{What cloud services are there}
+\subsection{What is small scale cloud computing}
+In this research I want to do some small scale cloud computing.
+The main motivation behind is is that it is ways to expensive to simulate large scale cloud computing.
+Another reason is the Co-location that can be used with small scale cloud computing.
+Because of this it could be better in executing small tasks.
+More motivation is that it does not use a lot of space and power.
 Eucalyptus https://www.eucalyptus.com/eucalyptus-cloud/get-started
@@
 
-\subsection{What cloud services are already running on Raspberry pi}
+\subsection{What are the most promising cloud services}
 In the PcExtreme article \cite{Pcextreme} there are running several services on a Raspberry Pi.
 For example a webserver, a DNS server, a chat server, a mail server, a vpn server or a monitoring server. 
-
-\subsection{What are the main characteristics of a Raspberry Pi cloud computer}
-
-\subsection{What software can be used for a Raspberry Pi cloud}
+In this research I want to test some cloud services and programs to see if they are suitable for the Raspberry Pi. 
 To investigate this I want to make a experimentation cloud with Raspberry Pi's to see if it will work as a cloud.
 
-\subsection{Is it reachable to build small personal Raspberry Pi clouds for server}
+\subsection{Is it reachable to build small personal Raspberry Pi clouds for services}
 With this subquestion I want to find out if it is possible to let users have small Raspberry Pi servers such as now is happening at PcExtreme as an experiment.
+I also want to know what the performance of this small Raspberry Pi cloud is.
+
+\subsection{Is it possible to improve cloud programs using small scale Raspberry Pi's}
+
+\section{Research Methods}
+This research will investigate a cloud computer consisting of Raspberry Pi's.
+The research method for this would be the Design Science research method.
+this is a method to solve field problems.
+This research will make use of the design Science method proposed by Hevner\cite{hevner:2007}
 
@@
 For the experiment we need a Raspberry Pi B that can make use of the Ethernet.
+In the setup video is explained how I can make such a cluster.
+\url{https://www.youtube.com/watch?v=JtX9lVDsqzg}.
+If I have made such I cluster I can start doing some tests on it. We will use applications also super computers will use such as Mpich. We will use Fortran to rank our raspberry pi server. 
+I am for example curious about what the duration is between small seperated tasks and large tasks.
 
@@
 Data storage like dropbox
+
+Raspberry pi cluster
+\url{https://www.youtube.com/watch?v=vHJ4ZeXT_Zc}
+
+Test big task and several small tasks
+
+Raspberry py 2 windows
+\url{http://www.science20.com/the_conversation/upgraded_raspberry_pi_offers_windows_and_linux-152986}
+
+Southphampton
+\url{http://www.southampton.ac.uk/~sjc/raspberrypi/pi_supercomputer_southampton_web.pdf}
+
+Teach purpose Cassandra. Seems difficult to self implement.
+
+\url{http://devfluid.tumblr.com/post/49530425707/installing-cassandra-1-2-4-on-raspberry-pi}
+
+testing cassandra server
+\url{http://www.linux.com/news/embedded-mobile/mobile-linux/747326-teaching-cassandra-cluster-setups-with-the-raspberry-pi-}
+
+Testing difference
+Hadoop
+Cassandra
+MongoDB
+CouchDB
+
+\url{http://www.widriksson.com/raspberry-pi-hadoop-cluster/}
+Hadoop cluster
+
+spark possible faster than hadoop
+\url{http://spark.apache.org/}
 

### 2015-02-19 research proposal/research proposal.tex
more information

@@
 area of cloud computing services. The main research question
-is: Is a cloud server consisting of Raspberry Pi efficient?
+is: What is the performance of raspberry pi load balancing service using video streaming? To answer this question a micro raspberry pi video streaming service will be build. 
 \end{abstract}
 
-\keywords{Cloud computing, Raspberry Pi, ARM performance, micro data server}
+\keywords{Cloud computing, Raspberry Pi, ARM performance, micro data server, video streaming, load balancing}
 
 \section{Motivation}
-Today there are many cloud services. The amount of cloud computing services is increasing fast \cite{armbrust:2009}.  Despite the attention
+Today there are many cloud services. This amount of cloud computing services is increasing fast \cite{armbrust:2009}.  Despite the attention
 from the research community, research and development of
@@
 A reason for this is the co-location and the low power usage of a Raspberry Pi\cite{hosting,Pcextreme}.
-A Raspberry Pi has a power usage between the 3-5 Watt and a server has a power usage between the 75 and 150 watt \cite{Powerusage}.
+A Raspberry Pi has a power usage between the 3-5 Watt.
+A normal server has a power usage between the 75 and 150 watt \cite{Powerusage}.
 This could mean that it is better to use a Raspberry Pi for specific small tasks that do not demand a whole server.
-During this research I want to further investigate this power usage.
+During this research I want to further investigate the performance of the Raspberry pi as a server.
 A Raspberry Pi can be the small data center for the future \cite{tso:2013}.
@@
 This makes it cheaper to do research in compared to a normal server.
+This is also the mean reason why the Raspberry pi was ones created.
 The current versions of the Raspberry Pi cannot perform the task of a large scale x86 server \cite{tso:2013}.
 Building a cloud like this can be a cost effective scale model\cite{tso:2013}.
-It's a Ideal testbed for testing distributed software.
+It's a ideal testbed for testing distributed software.
+During this research we will investigate the performance of a raspberry pi as a video streamer to other computers.
+The reason I want to investigate it with video streaming is because this demands a lot of bandwidth from the network and could be one of the first things that should be improved.
 
-%\subsection{References and Citations}
-%Footnotes should be Times New Roman 9-point, and justified to the 
-%full width of the column.\footnote{A footnote in 9-point Times New Roman.}
+\section{Specific problem}
 
-%Use the "ACM Reference format" for references - that is, a numbered 
-%list at the end of the article, ordered alphabetically and formatted 
-%accordingly. See examples of some typical reference types, in the new 
-%"ACM Reference format", at the end of this document. Within this 
-%template, use the style named references for the text. Acceptable 
-%abbreviations, for journal names, can be found here: 
-%http://library.caltech.edu/reference/abbreviations/
-
-%The references are also in 9 pt., but that section (see Section 7) is 
-%ragged right. References should be published materials accessible to 
-%the public. Internal technical reports may be cited only if they are 
-%easily accessible (i.e. you can give the address to obtain the report 
-%within your citation) and may be obtained by any reader. Proprietary
-%information may not be cited. Private communications should be 
-%acknowledged, not referenced  (e.g., "[Robertson, personal communication]")
-
-%\subsection{Page Numbering, Headers and Footers}
-%Do not include headers, footers or page numbers in your submission. 
-%These will be added when the publications are assembled.
+Today a lot of people watch their movies online using video streaming. \url{http://www.volkskrant.nl/media/nederland-op-vijfde-plek-met-bijna-miljoen-netflix-abonnees~a3851031/}
+The Netherlands have for example one million subscribers for Netflix.
+Netflix is a video streaming service that makes HD movies watching possible.
+For this Netflix makes use of a content distribution network (CDN).
+On the internet
+this is also known as a on demand service \cite{Adhikari:2012}. Netflix makes use of
+MPEG-DASH a protocol that makes streaming over http possible \cite{martin:2013}.
+The problem is that Netflix is responsible for  29.7\% of the peak downstream traffic in US  \cite{Adhikari:2012}.
+In the Netherlands more and more users are making use of video streaming as Youtube and Netflix.
+In this research we want to investigate if it is possible to make small micro data centers with raspberry pi's.
+This research will try to find out how this cloud works.
+There will be taken a look in for example the load balancing of video streaming.
+In this way it can be possible to see improvements that can be made in the load balancing so that the servers can be used more efficient.
+This is also build to learn more from load balancing and a computer cluster.
+This can be really useful, because nowadays it's still done on relatively expensive servers.
 
@@
 %\label{fig:abc} %always place your label after your caption!
-\ %end{figure}
-
-%Captions should be Times New Roman 9-point bold.
-They should be numbered (e.g., "Table 1" or "Figure 2"), please note that the word for Table and Figure are spelled out.
-Figure's captions should be centered beneath the image or picture, and Table captions should be centered above the table body.
-
-%\section{Sections}
-%The heading of a section should be in Times New Roman 12-point bold in all-capitals flush left with an additional 6-points of white space above the section head.
-Sections and subsequent sub- sections should be numbered and flush left.
-For a section head and a subsection head together (such as Section 3 and subsection 3.1), use no additional space above the subsection head.
-
-%\subsection{Subsections}
-%The heading of subsections should be in Times New Roman 12-point bold with only the initial letters capitalized.
-(Note: For subsections and subsubsections, a word like the or a is not capitalized unless it is the first word of the header.)
-
-%\subsubsection{Subsubsections}
-%The heading for subsubsections should be in Times New Roman 11-point italic with initial letters capitalized and 6-points of white space above the subsubsection head.
-
-%\section{Acknowledgments}
-%Our thanks to ACM SIGCHI for allowing us to modify templates they had developed.
-
-%\section{Introduction to Latex}
-%Typically, the body of a paper is organized into a hierarchical
-%structure, with numbered or unnumbered headings for sections,
-%subsections, sub-subsections, and even smaller sections.  The
-%command \texttt{{\char'134}section} that precedes this paragraph
-%is part of such a hierarchy. \LaTeX\ handles the numbering and placement of these
-%headings for you, when you use the appropriate heading commands
-%around the titles of the headings.  If you want a sub-subsection
-%or smaller part to be unnumbered in your output, simply append an
-%asterisk to the command name.  Examples of both numbered and
-%unnumbered headings will appear throughout the balance of this
-%sample document.
-
-%Because the entire article is contained in the \textbf{document}
-%environment, you can indicate the start of a new paragraph with a
-%blank line in your input file; that is why this sentence forms a
-%separate paragraph.
-
-%\subsection{Type Changes and {\subsecit Special} Characters}
-%We have already seen several typeface changes in this sample.  You
-%can indicate italicized words or phrases in your text with the
-%command \texttt{{\char'134}textit}; emboldening with the command
-%\texttt{{\char'134}textbf} and typewriter-style (for instance, for
-%computer code) with \texttt{{\char'134}texttt}.  But remember, you
-%do not have to indicate typestyle changes when such changes are
-%part of the \textit{structural} elements of your article; for
-%instance, the heading of this subsection will be in a sans
+ %end{figure}
 
@@
 The main research question
-is: Is a cloud server consisting of Raspberry Pi efficient?
+is: What is the performance of a raspberry pi load balancing service using video streaming?
 
-In order to come to a good answer we first need to build our own Raspberry Pi setup.
-There needs to be decided with which benchmark the performance will be measured.
-After we have measured the performance we can see
+In order to come to a good answer we need to  research several things
 
-\subsection{Citations}
-Citations to articles \cite{bowman:reasoning, clark:pct,
-braams:babel, herlihy:methodology}, conference proceedings
-\cite{clark:pct} or books \cite{salas:calculus, Lamport:LaTeX}
-listed in the Bibliography section of your article will occur
-throughout the text of your article. You should use BibTeX to
-automatically produce this bibliography; you simply need to insert
-one of several citation commands with a key of the item cited in
-the proper location in the \texttt{.tex} file
-\cite{Lamport:LaTeX}. The key is a short reference you invent to
-uniquely identify each work; in this sample document, the key is
-the first author's surname and a word from the title.  This
-identifying key is included with each item in the \texttt{.bib}
-file for your article.
+build our own Raspberry Pi setup. There needs to be decided with which benchmark the performance will be measured. After we have measured the performance we can see
 
-The details of the construction of the \texttt{.bib} file are
-beyond the scope of this sample document, but more information can
-be found in the \textit{Author's Guide}, and exhaustive details in
-the \textit{\LaTeX\ User's Guide}\cite{Lamport:LaTeX}.
-
-This article shows only the plainest form of the citation command,
-using \texttt{{\char'134}cite}. This is what is stipulated in the
-SIGS style specifications. No other citation format is endorsed or
-supported.
-\subsection{What is small scale cloud computing}
+\subsection{What is small scale cloud computing?}
 In this research I want to do some small scale cloud computing.
@@
 Because of this it could be better in executing small tasks.
+Small scale cloud computing is cloud computing with smaller computation amounts than normal.
 More motivation is that it does not use a lot of space and power.
-Eucalyptus https://www.eucalyptus.com/eucalyptus-cloud/get-started
-Hazelcast
+Resources I could use for small scale cloud computing:
 
-\subsection{What are the most promising cloud services}
-In the PcExtreme article \cite{Pcextreme} there are running several services on a Raspberry Pi.
-For example a webserver, a DNS server, a chat server, a mail server, a vpn server or a monitoring server. 
-In this research I want to test some cloud services and programs to see if they are suitable for the Raspberry Pi. 
+\subsection{What is cloud video streaming}
+There are a lot of cloud services nowadays. These include a webserver, a DNS server, a chat server, a mail server, a vpn server or a monitoring server or even a video streaming service. 
+Today a lot of people watch their movies online using video streaming.
+\url{http://www.volkskrant.nl/media/nederland-op-vijfde-plek-met-bijna-miljoen-netflix-abonnees~a3851031/} The netherlands have for example one million subscribers for Netflix.
+Netflix is a video streaming service that makes HD movies watching possible.
+For this Netflix makes use of a content distribution network (CDN).
+On the internet this is also known as a on demand service.
+They make use of amazon its AWS with a AWS cloud, Amazon simpleDB , S3 and cassandra for file storage \cite{Adhikari:2012}.
+Netflix makes use of MPEG-DASH a protocol that makes streaming over http possible.
+In this research I want to investigate more in the video streaming as a cloud service.
 To investigate this I want to make a experimentation cloud with Raspberry Pi's to see if it will work as a cloud. 
+Resources I could use for cloud video streaming:
+
+\subsection{What kind of different load balancing techniques are there?}
+In distributed servers it is very important that good load balancing takes place. For this reason I want to further investigate in what kind of load balancing techniques there are. 
+Resources I could use for load balancing:
 
 \subsection{Is it reachable to build small personal Raspberry Pi clouds for services}
-With this subquestion I want to find out if it is possible to let users have small Raspberry Pi servers such as now is happening at PcExtreme as an experiment.
-I also want to know what the performance of this small Raspberry Pi cloud is.
+With this subquestion I want to find out if it is possible to let users have small Raspberry Pi servers I also want to know what the performance of this small Raspberry Pi cloud is. 
+Resources:
+\cite{Pcextreme}
 
-\subsection{Is it possible to improve cloud programs using small scale Raspberry Pi's}
+\subsection{Is it possible to improve load balancing using small scale Raspberry Pi's}
+For this research I want to investigate if it is possible to do more research in the 
+load balancing techniques that can be used in a raspberry pi. A example of this would be the round robin protocol.
+Resources:
 
@@
 For the experiment we need a Raspberry Pi with a static Ip address and we need a sd card for the OS.
-A Raspberry Pi can be used as a webserver or DNS server.
 For the experiment we need a Raspberry Pi B that can make use of the Ethernet.
-In the setup video is explained how I can make such a cluster.
-\url{https://www.youtube.com/watch?v=JtX9lVDsqzg}.
-If I have made such I cluster I can start doing some tests on it. We will use applications also super computers will use such as Mpich. We will use Fortran to rank our raspberry pi server. 
-I am for example curious about what the duration is between small seperated tasks and large tasks.
+This is because a Raspberry Pi can be used as a webserver and this is needed to have this in order to make video streaming possible.
+This webserver will make video streaming possible.
+It will have a VPN to make it possible to put video's on the Raspberry pi \cite{VPN:2014}.
+So I will first make this video streaming webserver. 
+After this we will make a cluster with one Raspberry Pi as a load balancer and the other two as a video stream pi.
+If I have made such I cluster I can start doing some tests on it.
+For example some test in streaming in different quality with load balancing.
+The setup of the raspberry Pi can be seen in the figure below ~\ref{fig:setup}.
 
-Experiment making a VPN:
-\url{http://readwrite.com/2014/04/10/raspberry-pi-vpn-tutorial-server-secure-web-browsing}
+\begin{figure}
+\centering 
+\includegraphics[width=0.4\textwidth]{raspberry pi setup.jpg}
+\caption{Insert caption to place below figure.}
+\label{fig:setup} %always place your label after your caption!
+\end{figure}
 
@@
 \url{http://www.lighttpd.net/}
-
+\url{https://www.digitalocean.com/community/tutorials/how-to-set-up-nginx-load-balancing}
+\url{http://www.networkinghowtos.com/howto/load-balancing-with-nginx/}
 Raspberry Pi project Glasgow
@@
 
-Hallootjes
-\begin{table}
+\begin{table}[H]
 	\centering \caption{Planning}
@@
 Here above is the ~\ref{tab:planning}.
+The main research question is split up into several sub questions.
+These subquestions have each one week for answering.
+After that there is time to write the conclusion and answer the main question.
+Then there is still some time left to finalize the paper.
 
 \section{State of the Art}
+Today there are many cloud services. This amount of cloud computing services is increasing fast \cite{armbrust:2009}.  Despite the attention
+from the research community, research and development of
+Cloud Computing services is still in it's childhood\cite{tso:2013}.
+Today there is a lot of people that use video streaming and this will become even more.
+People want to have everything has to be accessible through the network around the clock \cite{youseff:2008}.
+One thing that people want on demand are there series.
+Currently Netflix has 30\% of the downstream in the United States.
 
-%
-% The following two commands are all you need in the
-% initial runs of your .tex file to
-% produce the bibliography for the citations in your paper.
+In this paper we will make a load balancing service for the Raspberry Pi.
 

### 2015-02-22 paper/research proposal.tex
paper

--- 2015-02-19 research proposal/research proposal.tex
@@
-% This is "bach-ref-2009.tex" Updated january 29th 2010.
-% This file should be compiled with "sig-alternate-fixed.cls" January 2010.
-% It is based on the ACM style "sig-alternate.cls"
-% -------------------------------------------------------------------------
-% This example file demonstrates the use of the 'sig-alternate-fixed.cls'
-% V2.5 LaTeX2e document class file. It is for those submitting
-% articles to the Twente Student Conference on IT. Both this file as the 
-% document class file are based upon ACM documents.
-%
-% ----------------------------------------------------------------------------------------------------------------
 % This .tex file (and associated .cls) produces:
@@
 \usepackage{hyperref}
+
 \restylefloat{figure}
@@
 
-Today a lot of people watch their movies online using video streaming. \url{http://www.volkskrant.nl/media/nederland-op-vijfde-plek-met-bijna-miljoen-netflix-abonnees~a3851031/}
-The Netherlands have for example one million subscribers for Netflix.
+Today a lot of people watch their movies online using video streaming. 
+The Netherlands have for example one million subscribers for Netflix \cite{volkskrant}.
 Netflix is a video streaming service that makes HD movies watching possible.
@@
 This can be really useful, because nowadays it's still done on relatively expensive servers.
-
-%\section{Figures / Captions}
-%Place Tables/Figures/Images in text as close to the reference as possible 
-%(See Figure \ref{fig:abc}).  It may extend across both columns.
-
-%\begin{figure}
-%\centering 
-%\epsfig{file=fly2.eps} 
-%\caption{Insert caption to place below figure.}
-%\label{fig:abc} %always place your label after your caption!
- %end{figure}
 
@@
 Resources I could use for small scale cloud computing:
+\cite{Pcextreme,armbrust:2009,richardson:2012,abrahamsson:2013,southampton}
 
@@
 Today a lot of people watch their movies online using video streaming.
-\url{http://www.volkskrant.nl/media/nederland-op-vijfde-plek-met-bijna-miljoen-netflix-abonnees~a3851031/} The netherlands have for example one million subscribers for Netflix.
+The netherlands have for example one million subscribers for Netflix \cite{volkskrant}.
 Netflix is a video streaming service that makes HD movies watching possible.
@@
 Resources I could use for cloud video streaming:
+\cite{g-streamer,raspberry-video,video-1080p, plissonneau:2012}
 
@@
 Resources I could use for load balancing:
+\cite{nginx-load-balancing,nginx-load-balancing-2,computer-networking,wolf:1997,load-balancing}
 
@@
 Resources:
-\cite{Pcextreme}
+\cite{Pcextreme,nginx-load-balancing,nginx-load-balancing-2}
 
@@
 Resources:
+\cite{nginx-load-balancing,nginx-load-balancing-2}
 
@@
 this is a method to solve field problems.
-This research will make use of the design Science method proposed by Hevner\cite{hevner:2007}
+This research will make use of the design Science method proposed by Hevner\cite{hevner:2007}.
 
@@
 
-\begin{figure}
+\begin{figure}[H]
 \centering 
@@
 \end{figure}
-
-Glasgow Raspberry Pi
-\url{http://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=6679872}
-Limited software:
-lightweight,
-httpd,
-servers, 
-hadoop
-
-ICanCloud is a cloud simulation program.
-
-\url{http://www.lighttpd.net/}
-\url{https://www.digitalocean.com/community/tutorials/how-to-set-up-nginx-load-balancing}
-\url{http://www.networkinghowtos.com/howto/load-balancing-with-nginx/}
-Raspberry Pi project Glasgow
-\url{https://raspberrypicloud.wordpress.com/}
-Runs Linux from sanddisk 16 gb
-
-Owncloud
-Data storage like dropbox
-
-Raspberry pi cluster
-\url{https://www.youtube.com/watch?v=vHJ4ZeXT_Zc}
-
-Test big task and several small tasks
-
-Raspberry py 2 windows
-\url{http://www.science20.com/the_conversation/upgraded_raspberry_pi_offers_windows_and_linux-152986}
-
-Southphampton
-\url{http://www.southampton.ac.uk/~sjc/raspberrypi/pi_supercomputer_southampton_web.pdf}
-
-Teach purpose Cassandra. Seems difficult to self implement.
-
-\url{http://devfluid.tumblr.com/post/49530425707/installing-cassandra-1-2-4-on-raspberry-pi}
-
-testing cassandra server
-\url{http://www.linux.com/news/embedded-mobile/mobile-linux/747326-teaching-cassandra-cluster-setups-with-the-raspberry-pi-}
-
-Testing difference
-Hadoop
-Cassandra
-MongoDB
-CouchDB
-
-\url{http://www.widriksson.com/raspberry-pi-hadoop-cluster/}
-Hadoop cluster
-
-spark possible faster than hadoop
-\url{http://spark.apache.org/}
-
-\begin{table}
-	\centering \caption{Cost breakdown of a testbed consisting 56 servers}
-
-\begin{tabular}{|c|c|c|} \hline
-\textbf{Server}&  \textbf{Power} \textbf{Needs Cooling?} \\ \hline
-Testbed  & $112,000 (@$2,000) 10,080W/h (@180W/h) & Yes \\ \hline
-PiCloud & $1,960 (@$35) 196W/h (@3.5W/h) & No \\ \hline
-\end{tabular}
-\label{tab:cost}
-\end{table}
+For the load balancing we will make use of Nginx for this we will use the following sources:
+\cite{nginx-load-balancing, nginx-load-balancing-2}
 
@@
 		\textbf{Week} & \textbf{Date} & \textbf{Activity} \\ \hline 
-		6-7&6 Feb. -15 Feb&Collect literature and software\\ \hline 
-		11-14&5 March 12 April&Start building test environment\\ \hline
-		14&6 April - 12 April&Answer subquestion 1\\ \hline
-		15&13 April - 20 April&Answer subquestion 2\\ \hline
-		16&21 April - 28April&Answer subquestion 3\\ \hline
-		18&4 May-10 May& conclusion and check coherency \\ \hline
-		19&11 May-18 May& Finalize paper \\ \hline
+		6-9& 6 Feb. -27 Feb& Collect literature and software\\ \hline 
+		10& 2 March - 9 March& Deadline peer review and proposal \\ \hline
+		12& 16 March -22 March & \textbf{Deadline proposal} \\ \hline
+		13 & 23 March -30 March &  \textbf{Accept Reject proposal} \\ \hline
+		10-14& 2 March 12 April& Start building test environment \\ \hline
+		14& 6 April - 12 April& Answer subquestion 1  \\ \hline
+		15& 13 April - 20 April& Answer subquestion 2\\ \hline
+		16& 21 April - 28 April& Answer subquestion 3\\ \hline
+		14-16 & 6 April - 28 April & working on test environment \\ \hline
+		17& 1 May - 7 May & Answer subquestion 4 \\ \hline
+		18& 4 May-10 May& conclusion and check coherency \\ \hline
+		19& 11 May-18 May& Finalize paper \\ \hline
+		22& 1 June-7 June&  \textbf{Deadline paper} \\ \hline
+		26 &22 June - 26 June & \textbf{Conference} \\ \hline
 		\end{tabular}
+
 		\label{tab:planning}
 \end{table}
-Here above is the ~\ref{tab:planning}.
+Here above is the table~\ref{tab:planning}.
 The main research question is split up into several sub questions.
@@
 People want to have everything has to be accessible through the network around the clock \cite{youseff:2008}.
-One thing that people want on demand are there series.
+One thing that people want on demand are there film series.
 Currently Netflix has 30\% of the downstream in the United States.
+This downstream is huge and that means that there is optimization in this branch possible.
+To make the video on demand service of Netflix possible they use servers from Amazon.
 
-In this paper we will make a load balancing service for the Raspberry Pi.
+In this paper there will be research done on making a load balancing service for the Raspberry Pi.
+This service will consist of several raspberry Pi's.
+These Raspberry Pi's make together a small cloud computer.
+The Raspberry Pi is made for research and education purposes \cite{raspberry-pi}.
+The Raspberry Pi is a cheap device costing around 35 euro.
+It has a power consumption of only three watt and has quite good processor.
+For this reason it might be very useful for small scale cloud computing.
+The raspberry Pi is a small device and is excellent for a lot of small devices in a relatively small place.
+The Raspberry Pi doesn't use cooling and it can be used for very rapid elasticity and on-demand self-service.
+Because of it's cooling features and low power consumption it might be a good alternative for the nowadays high power consuming data centers.
+The raspberry pi is really small so it is a lot easier to place extra pi in a data center compared to a normal server.
+The Raspberry Pi has one drawback and that is that the processing power is relatively low.
+By using load balancing there will be taken a look at what load balancing techniques are successful for the Raspberry pi.
+
+In this research we will make a small raspberry cloud to do research on video streaming using HTTP.
+This will be done using the design Science method proposed by Hevner\cite{hevner:2007}.
+After we have done this for the Raspberry Pi there will be looked at streaming using Amazon.
+In this way we can see how the results are compared to streaming via Amazon.
+This research will try to find out if the raspberry has enough processing power to stream to multiple web clients.
+The cloud performance can now be better researched, because everything is at one location and the information about what processes are running on the pi are well defined.
+In this way we can take a better look at algorithms used in video streaming.
+This is mostly because there is not a lot of overhead.
 

### 2015-02-23 paper/paper.tex
changes

--- 2015-02-22 paper/research proposal.tex
@@
 
-\section{Motivation}
+\section{Introduction}
 Today there are many cloud services. This amount of cloud computing services is increasing fast \cite{armbrust:2009}.  Despite the attention
-from the research community, research and development of
-Cloud Computing services is still in it's childhood\cite{tso:2013}. 
+from the research community, research and development of Cloud Computing services is still in it's childhood\cite{tso:2013}. 
 In this research the Raspberry Pi cloud services will be investigated.
@@
 Some data centers even offer some cloud computing using the Raspberry Pi.
-A reason for this is the co-location and the low power usage of a Raspberry Pi\cite{hosting,Pcextreme}.
+A reason for this is the small location that the Raspberry Pi needs, and the low power usage of a Raspberry Pi\cite{hosting,Pcextreme}.
 A Raspberry Pi has a power usage between the 3-5 Watt.
@@
 This could mean that it is better to use a Raspberry Pi for specific small tasks that do not demand a whole server.
-During this research I want to further investigate the performance of the Raspberry pi as a server.
+During this research there will be a investigation on the performance of the Raspberry pi as a server.
 A Raspberry Pi can be the small data center for the future \cite{tso:2013}.
@@
 
-\section{Specific problem}
-
 Today a lot of people watch their movies online using video streaming. 
@@
 For this Netflix makes use of a content distribution network (CDN).
-On the internet
-this is also known as a on demand service \cite{Adhikari:2012}. Netflix makes use of
-MPEG-DASH a protocol that makes streaming over http possible \cite{martin:2013}.
+On the internet this is also known as a on demand service \cite{Adhikari:2012}.
+Netflix makes use of MPEG-DASH a protocol that makes streaming over http possible \cite{martin:2013}.
 The problem is that Netflix is responsible for  29.7\% of the peak downstream traffic in US  \cite{Adhikari:2012}.
 In the Netherlands more and more users are making use of video streaming as Youtube and Netflix.
-In this research we want to investigate if it is possible to make small micro data centers with raspberry pi's.
+In this research there will be a investigation on the possibility to make small micro data centers with raspberry pi's.
 This research will try to find out how this cloud works.
@@
 
-\section{Research questions}
-The main research question
-is: What is the performance of a raspberry pi load balancing service using video streaming?
+In this paper we will try to measure the performance of different load balancing techniques using the Raspberry Pi. For this the main research question will be: 
+\begin{center}
+ What is the performance of a raspberry pi load balancing techniques using video streaming?
+\end{center}
 
-In order to come to a good answer we need to  research several things
+In order to come to a good answer we need to  research several things.
+Therefore several sub-questions will be researched.
+These sub-questions will altogether provide a answer to the main research question.
 
-build our own Raspberry Pi setup. There needs to be decided with which benchmark the performance will be measured. After we have measured the performance we can see
+\begin{enumerate}
+	\item What is small scale cloud computing?
+	\item What is cloud video streaming?
+	\item What kind of different load balancing techniques are there?
+	\item Is it reachable to build small personal Raspberry Pi clouds for services?
+	\item Is it possible to improve load balancing using small scale Raspberry Pi's? 
+\end{enumerate}
 
-\subsection{What is small scale cloud computing?}
-In this research I want to do some small scale cloud computing.
+This research will be part literature study and a part of it will be building a small Raspberry Pi cloud to analyze balancing techniques on the Raspberry Pi.
+For this research cloud video streaming is one of the specific aspects that will be investigated.
+The load balancing techniques will be optimized for the video streaming.
+The first three research questions will describe the state of the art.
+The last two sub-questions will go into the technical research that will investigate the performance and possibility of Raspberry Pi's for cloud video streaming.
+They last one will investigate of their are improvements in load balancing possible.
+The five sub-questions are being looked at in the next five sections.
+Followed by a final section for conclusions and identified areas for future
+work.
+
+\section{Small scale computing}
+Today there are many cloud kinds of cloud computing.
+The amount of cloud computing services is increasing fast \cite{armbrust:2009}.
+It's now even possible to build your own small cloud using Raspberry Pi's \cite{southampton}.
+In this research there will be small scale cloud computing with the Raspberry Pi.
 The main motivation behind is is that it is ways to expensive to simulate large scale cloud computing.
-Another reason is the Co-location that can be used with small scale cloud computing.
+Another reason is the small location that is needed used with small scale cloud computing for Raspberry Pi's\cite{Pcextreme}.
+The Raspberry Pi is really small compared to a normal server \cite{cox:2014}.
 Because of this it could be better in executing small tasks.
-Small scale cloud computing is cloud computing with smaller computation amounts than normal.
-More motivation is that it does not use a lot of space and power.
-Resources I could use for small scale cloud computing:
-\cite{Pcextreme,armbrust:2009,richardson:2012,abrahamsson:2013,southampton}
+Small scale cloud computing is cloud computing with smaller computation amounts than normal \cite{cox:2014}.
+More motivation is that it does not use a lot and power.
 
-\subsection{What is cloud video streaming}
+To understand what small scale cloud computing really is we will look more at the specific cloud service called Infrastructure as a Service:
+
+\section{Video streaming}
 There are a lot of cloud services nowadays. These include a webserver, a DNS server, a chat server, a mail server, a vpn server or a monitoring server or even a video streaming service. 
@@
 
-\subsection{What kind of different load balancing techniques are there?}
+\section{Load balancing}
 In distributed servers it is very important that good load balancing takes place. For this reason I want to further investigate in what kind of load balancing techniques there are. 
@@
 
-\subsection{Is it reachable to build small personal Raspberry Pi clouds for services}
+\section{Raspberry pi}
 With this subquestion I want to find out if it is possible to let users have small Raspberry Pi servers I also want to know what the performance of this small Raspberry Pi cloud is. 
@@
 
-\subsection{Is it possible to improve load balancing using small scale Raspberry Pi's}
 For this research I want to investigate if it is possible to do more research in the 
@@
 \cite{nginx-load-balancing, nginx-load-balancing-2}
-
-\section{Planning}
-
-\begin{table}[H]
-	\centering \caption{Planning}
-\begin{tabular}{|c|c|c|} \hline
-		\textbf{Week} & \textbf{Date} & \textbf{Activity} \\ \hline 
-		6-9& 6 Feb. -27 Feb& Collect literature and software\\ \hline 
-		10& 2 March - 9 March& Deadline peer review and proposal \\ \hline
-		12& 16 March -22 March & \textbf{Deadline proposal} \\ \hline
-		13 & 23 March -30 March &  \textbf{Accept Reject proposal} \\ \hline
-		10-14& 2 March 12 April& Start building test environment \\ \hline
-		14& 6 April - 12 April& Answer subquestion 1  \\ \hline
-		15& 13 April - 20 April& Answer subquestion 2\\ \hline
-		16& 21 April - 28 April& Answer subquestion 3\\ \hline
-		14-16 & 6 April - 28 April & working on test environment \\ \hline
-		17& 1 May - 7 May & Answer subquestion 4 \\ \hline
-		18& 4 May-10 May& conclusion and check coherency \\ \hline
-		19& 11 May-18 May& Finalize paper \\ \hline
-		22& 1 June-7 June&  \textbf{Deadline paper} \\ \hline
-		26 &22 June - 26 June & \textbf{Conference} \\ \hline
-		\end{tabular}
-
-		\label{tab:planning}
-\end{table}
-Here above is the table~\ref{tab:planning}.
-The main research question is split up into several sub questions.
-These subquestions have each one week for answering.
-After that there is time to write the conclusion and answer the main question.
-Then there is still some time left to finalize the paper.
 
@@
 
+\section{Conclusion and future work}
+
+\section{Acknowledgments}
+
 \bibliographystyle{abbrv}

### 2015-02-23 research_proposal/research proposal.tex
changes

--- 2015-02-22 paper/research proposal.tex
@@
 area of cloud computing services. The main research question
-is: What is the performance of raspberry pi load balancing service using video streaming? To answer this question a micro raspberry pi video streaming service will be build. 
+is: What is the performance of raspberry pi load balancing techniques using video streaming? To answer this question a micro raspberry pi video streaming service will be build. 
 \end{abstract}
@@
 This could mean that it is better to use a Raspberry Pi for specific small tasks that do not demand a whole server.
-During this research I want to further investigate the performance of the Raspberry pi as a server.
+During this research there will be a investigation on the performance of the Raspberry pi as a server.
 A Raspberry Pi can be the small data center for the future \cite{tso:2013}.
-The Raspberry is a rather cheap device for 35 euros.
+The Raspberry is a rather cheap device for 35 euro.
 This makes it cheaper to do research in compared to a normal server.
@@
 During this research we will investigate the performance of a raspberry pi as a video streamer to other computers.
-The reason I want to investigate it with video streaming is because this demands a lot of bandwidth from the network and could be one of the first things that should be improved.
+The reason for investigating video streaming is because this demands a lot of bandwidth from the network and could be one of the first things that should be improved.
 
@@
 The main research question
-is: What is the performance of a raspberry pi load balancing service using video streaming?
+is: What is the performance of a raspberry pi load balancing techniques using video streaming?
 
-In order to come to a good answer we need to  research several things
-
-build our own Raspberry Pi setup. There needs to be decided with which benchmark the performance will be measured. After we have measured the performance we can see
+This research will be part literature study and a part of it will be building a small Raspberry Pi cloud to measure balancing techniques on the Raspberry Pi.
+Here below there are several questions to come to a good answer for the main research question.
 
 \subsection{What is small scale cloud computing?}
-In this research I want to do some small scale cloud computing.
-The main motivation behind is is that it is ways to expensive to simulate large scale cloud computing.
-Another reason is the Co-location that can be used with small scale cloud computing.
+In this research there will be small scale cloud computing with the Raspberry Pi.
+The main motivation behind is that it is ways to expensive to simulate large scale cloud computing.
+Resources for this:
+\cite{southampton, Powerusage, cox:2014}
+Another reason is the small location that is needed used with small scale cloud computing for Raspberry Pi's\cite{Pcextreme}.
 Because of this it could be better in executing small tasks.
 Small scale cloud computing is cloud computing with smaller computation amounts than normal.
-More motivation is that it does not use a lot of space and power.
-Resources I could use for small scale cloud computing:
+More motivation is that it does not use a lot cooling and power.
+Resources available for small scale cloud computing:
 \cite{Pcextreme,armbrust:2009,richardson:2012,abrahamsson:2013,southampton}
 
-\subsection{What is cloud video streaming}
-There are a lot of cloud services nowadays. These include a webserver, a DNS server, a chat server, a mail server, a vpn server or a monitoring server or even a video streaming service. 
-Today a lot of people watch their movies online using video streaming.
-The netherlands have for example one million subscribers for Netflix \cite{volkskrant}.
-Netflix is a video streaming service that makes HD movies watching possible.
-For this Netflix makes use of a content distribution network (CDN).
-On the internet this is also known as a on demand service.
-They make use of amazon its AWS with a AWS cloud, Amazon simpleDB , S3 and cassandra for file storage \cite{Adhikari:2012}.
+\subsection{What is cloud video streaming?}
+There are many kinds of cloud computing and cloud services.
+These include a webserver, a DNS server, a chat server, a mail server, a vpn server or a monitoring server or even a video streaming service.
+Information video streaming Netflix:
+\cite{volkskrant, Adhikari:2012}
 Netflix makes use of MPEG-DASH a protocol that makes streaming over http possible.
 In this research I want to investigate more in the video streaming as a cloud service.
-To investigate this I want to make a experimentation cloud with Raspberry Pi's to see if it will work as a cloud. 
-Resources I could use for cloud video streaming:
+To investigate what that is are the following resources:
 \cite{g-streamer,raspberry-video,video-1080p, plissonneau:2012}
@@
 \subsection{What kind of different load balancing techniques are there?}
-In distributed servers it is very important that good load balancing takes place. For this reason I want to further investigate in what kind of load balancing techniques there are. 
+In distributed servers it is very important that good load balancing takes place.
+For this reason I want to further investigate in what kind of load balancing techniques there are.
 Resources I could use for load balancing:
@@
 
-\subsection{Is it reachable to build small personal Raspberry Pi clouds for services}
+\subsection{Is it reachable to build small personal Raspberry Pi clouds for services?}
 With this subquestion I want to find out if it is possible to let users have small Raspberry Pi servers I also want to know what the performance of this small Raspberry Pi cloud is. 
@@
 
-\subsection{Is it possible to improve load balancing using small scale Raspberry Pi's}
+\subsection{Is it possible to improve load balancing using small scale Raspberry Pi's?}
 For this research I want to investigate if it is possible to do more research in the 
@@
 
-In this paper there will be research done on making a load balancing service for the Raspberry Pi.
-This service will consist of several raspberry Pi's.
-These Raspberry Pi's make together a small cloud computer.
 The Raspberry Pi is made for research and education purposes \cite{raspberry-pi}.

### 2015-03-09 paper/paper.tex
changes

@@
 \begin{abstract}
-This document describes a draft research proposal in the
-area of cloud computing services. The main research question
-is: What is the performance of raspberry pi load balancing service using video streaming? To answer this question a micro raspberry pi video streaming service will be build. 
+This paper describes the performance of raspberry pi load balancing service using video streaming.
 \end{abstract}
 
-\keywords{Cloud computing, Raspberry Pi, ARM performance, micro data server, video streaming, load balancing}
+\keywords{Cloud computing, Raspberry Pi,  micro data server, video streaming, load balancing}
 
 \section{Introduction}
-Today there are many cloud services. This amount of cloud computing services is increasing fast \cite{armbrust:2009}.  Despite the attention
-from the research community, research and development of Cloud Computing services is still in it's childhood\cite{tso:2013}. 
+Today cloud computing becomes more important.
+The amount of cloud computing services is increasing fast \cite{armbrust:2009}.
+Despite the attention from the research community, research and development of Cloud Computing services is still in it's childhood~\cite{tso:2013}.
+Cloud computing is a trend IT that people move computing and data away from desktop and portable PCs into large data centers~\cite{dikaiakos:2009}.
+People will in the future access internet services over lightweight portable devices.
 In this research the Raspberry Pi cloud services will be investigated.
-A reason for this is that the density of servers has increased a lot in the past\cite{density}.
+A reason for this is that the density of servers has increased a lot in the past~\cite{density}.
 There are new technologies such as for example the ARM processor.
@@
 A Raspberry Pi has a power usage between the 3-5 Watt.
-A normal server has a power usage between the 75 and 150 watt \cite{Powerusage}.
+A normal server has a power usage between the 75 and 250 watt \cite{Powerusage,beloglazov2012energy}.
 This could mean that it is better to use a Raspberry Pi for specific small tasks that do not demand a whole server.
@@
 The amount of cloud computing services is increasing fast \cite{armbrust:2009}.
-It's now even possible to build your own small cloud using Raspberry Pi's \cite{southampton}.
+It's now even possible to build your own small cloud using Raspberry Pi's \cite{southampton,abrahamsson:2013}.
 In this research there will be small scale cloud computing with the Raspberry Pi.
-The main motivation behind is is that it is ways to expensive to simulate large scale cloud computing.
+The main motivation behind this is that it is ways to expensive to simulate large scale cloud computing.
 Another reason is the small location that is needed used with small scale cloud computing for Raspberry Pi's\cite{Pcextreme}.
@@
 Small scale cloud computing is cloud computing with smaller computation amounts than normal \cite{cox:2014}.
-More motivation is that it does not use a lot and power.
+More motivation is that it does not use a lot cooling and power \cite{tso:2013}.
+Most clients of cloud computing buy the services instead of the hardware and having to set up the servers themselves.
+The Amazon Elastic Compute Cloud (Amazon EC2) is one of the most widely used infrastructure platforms that these clients use \cite{hofer:2011}.
+This elasticity of computing resources is very important~\cite{Miettinen:2010:EEM:1863103.1863107}.
 
-To understand what small scale cloud computing really is we will look more at the specific cloud service called Infrastructure as a Service:
+\subsection{What is it?}
+To understand what small scale cloud computing really is we will look more at the specific cloud service called Infrastructure as a Service.
+To this specific cloud service belongs the online storage.
+Today a lot of companies have their own virtual machines running in large data centers \cite{beloglazov:2010}.
+These instances can most often be scaled dynamically to the customer it's need.
+Using these instances makes it easier management and varying workloads better possible.
+The Raspberry Pi is a lot cheaper and has less power consumption, because of this it can be interesting
+to host virtual machines on the Raspberry Pi.
+The reason we call it small scale is because it is using small Raspberry's instead of large servers.
+Some providers offer a special hybrid cloud.
+You can then connect a private cloud to a public cloud \cite{qian:2009}.
+
+\subsection{Storage}
+In the cloud there are several storage systems.
+The cloud storage has become an integral part of our modern and mobile lives.
+Nowadays people own more often multiple devices.
+Cloud storage made it possible that the files we need are available where and when we want them.
+There are several ways to do this storage.
+Dropbox for example stores your information on a local folder on your device, after it has done that it will sync with an online version \cite{drago2012inside, dropbox}.
+In this way your other devices or the friends you shared the information with will have that information.
+In this way offline editing is also possible and this makes dropbox really powerful.
+\newline
+Today there are a lot of problems with security for cloud storage and that's why some people like to do it by themselves.
+For this there is a cloud service called ownCloud \cite{owncloud}.
+This service gives you the possibility to host the data where you want.
+You can even build your own cloud storage system by using ownCloud open source.
+The security aspect is important, because this can lead to loss or leak of data.
+Sometimes this can even have legal consequences \cite{hofer:2011}.
+For all important software used for cloud storage this means that they should be stored server side \cite{hofer:2011}.
+\newline
+Another problem that is very important is the reachability of the data centers that are used by the cloud. Netflix responsible for 29.7\% of the peak downstream traffic in US  \cite{Adhikari:2012}.
+
+\subsection{Power usage}
+Power usage efficiency is nowadays becoming a more important aspect in cloud computing.
+This is one of the main problems in cloud computing.
+Data centers require a lot of electrical power.
+Therefore we perhaps need to more Green Cloud Computing solutions that reduce the electrical power consumption and reduce the environmental impact of data centers~\cite{beloglazov2012energy}.
+Besides the power the data center consumes it can be important to look at the traffic pattern.
+It can make a huge different in sending data in small bursts or in one large burst \cite{Miettinen:2010:EEM:1863103.1863107}.
+With the increase of lightweight portable devices the energy efficiency becomes more important.
+This means that a trade-of has to be made between local processing and computation offloading \cite{Miettinen:2010:EEM:1863103.1863107}.
+This is computation offloading makes cloud computing more and more important.
 
 \section{Video streaming}
-There are a lot of cloud services nowadays. These include a webserver, a DNS server, a chat server, a mail server, a vpn server or a monitoring server or even a video streaming service. 
-Today a lot of people watch their movies online using video streaming.
+There are a lot of cloud services nowadays. These include a webserver, a DNS server, a chat server, a mail server, a vpn server or a monitoring server or even a video streaming service. \newline
+Today a lot of people watch their movies online using video streaming and this amount of people is increasing.
 The netherlands have for example one million subscribers for Netflix \cite{volkskrant}.
+One thing that these users want is the on demand video streaming.
+They don't want to store the data itself and they want to have a wide choice of different videos.
 Netflix is a video streaming service that makes HD movies watching possible.
@@
 On the internet this is also known as a on demand service.
-They make use of amazon its AWS with a AWS cloud, Amazon simpleDB , S3 and cassandra for file storage \cite{Adhikari:2012}.
+They make use of amazon its AWS, Amazon simpleDB , S3 and cassandra for file storage \cite{Adhikari:2012}.
 Netflix makes use of MPEG-DASH a protocol that makes streaming over http possible.
-In this research I want to investigate more in the video streaming as a cloud service.
-To investigate this I want to make a experimentation cloud with Raspberry Pi's to see if it will work as a cloud. 
+Currently Netflix has 30\% of the downstream in the United States~\cite{computer-networking}.
+To make this video streaming possible Netflix does some things in the cloud.
+These are content ingestion, content processing and uploading different versions to the CDN (Content Distribution Networks)~\cite{Adhikari:2012}.
+Content ingestion means that Netflix receives the studio master version of the movies and uploads these to the cloud.
+In the cloud there are then created many different formats for each movie.
+Once all these versions have been created they are distributed over the multiple CDNS.
+
+The video streaming happens with TCP.
+TCP sends frames to the client and in these frames is the video stored.
+Of course if the available TCP send rate is large enough then the video will play without any delays.
+But if the TCP send rate is less then needed then the video play will alternate between periods of continuous playout and periods of freezing~\cite{computer-networking}.
+Its very important that video freezing or audio playing faster then the video does not happen.
+This is why multimedia applications have high performance requirements.
+For this their are models to predict the performance and techniques to find a minimal cost bandwidth allocation that will result in all user requirements being met.
+
+\subsection{HTTP streaming}
+HTTP streaming is one way to stream a video.
+In HTTP streaming the HTTP GET request specifies the specific range of bytes the client wants to retrieve from the desired video~\cite{computer-networking}.
+In this way the client can correctly receive the video.
+If the client receives to much then its buffer for video playing can get full.
+To prevent throwing data away the server will then stop sending.
+To prevent throwing data away the client will have a not to large buffer.
+\newline
+There is also a new kind of HTTP streaming called DASH (Dynamic Adaptive Streaming over HTTP)~\cite{computer-networking}.
+In DASH the video is encoded into several different versions.
+If the bandwidth is high, then the client selects chunks from a high-rate version and the way around~\cite{computer-networking}.
+The possibility to switch between bit rate versions is in video streaming very important.
+To make a smooth transition between these versions possible there are intermediate versions so that the client will see less suddenly the change in video quality.
+In HTTP streaming the server stores the video with a different URL.
+
+To investigate video streaming there will be an experimentation cloud with Raspberry Pi's to see if these small mini computers will work as a cloud. 
 Resources I could use for cloud video streaming:
@@
 \section{Load balancing}
-In distributed servers it is very important that good load balancing takes place. For this reason I want to further investigate in what kind of load balancing techniques there are. 
-Resources I could use for load balancing:
-\cite{nginx-load-balancing,nginx-load-balancing-2,computer-networking,wolf:1997,load-balancing}
+In distributed servers it is very important that good load balancing takes place.
+There are several choices that have to be made by choosing a load balancer for a service.
+These choices can for example be performance, reliability and features.There are several load balancing techniques out there, for example priority queuing~\cite{computer-networking}.
+This means that packets in the output queue are prioritized.
+This is typically done in a first in first out way.
+Another type of queuing is the round robin.
+Round robin puts packets into different classes.
+It will first look for a packet in a given class and if there is none in that class it will look for the next packet \cite{computer-networking}.
+A more abstract form of round robin is weighted fair queuing.
+The difference between these is that each class may receive a differential amount of service in any interval of time \cite{computer-networking}.
+\subsection{Video streaming and load balancing}
+For video streaming several load balancing techniques can be used.
+There can be a non-uniform demand for different movies.
+One solution to overcome this problem would be to replicate the most popular movies.
+One obvious problem is then that it is expensive in terms of storage space required.
+To solve this you can use dynamic replication to solve the load demand~\cite{dan1996load}.
+By using this you move portions of a movie to less used storage devices.
+The allocation of these movies only happen when there is a to high increase on one specific storage device.
+In this way load imbalances can be prevented \cite{dan1996load}.
+\newline
+Load balancers are generally grouped in two layers.
+Layer 4 (FTP,IP, UDP, TCP )and layer 7 the application layer.
+Layer 7 load balancers distribute request based upon data in the application layer, this can for example be HTTP.
+A lot of video streaming services use http streaming \cite{Adhikari:2012}.
 
-\section{Raspberry pi}
-With this subquestion I want to find out if it is possible to let users have small Raspberry Pi servers I also want to know what the performance of this small Raspberry Pi cloud is. 
-Resources:
-\cite{Pcextreme,nginx-load-balancing,nginx-load-balancing-2}
-
-For this research I want to investigate if it is possible to do more research in the 
-load balancing techniques that can be used in a raspberry pi. A example of this would be the round robin protocol.
-Resources:
-\cite{nginx-load-balancing,nginx-load-balancing-2}
+\cite{wolf:1997,load-balancing}
 
@@
 this is a method to solve field problems.
-This research will make use of the design Science method proposed by Hevner\cite{hevner:2007}.
+This research will make use of the design Science method proposed by Hevner~\cite{hevner:2007}.
+This design method has three variants.
+\begin{figure}[H]
+	\centering 
+	\includegraphics[width=0.4\textwidth]{Design_science.png}
+	\caption{Design Science}
+	\label{fig:design} %always place your label after your caption!
+\end{figure}
+The \textbf{relevance cycle} is important, because you first have to identify the problems and opportunities.
+The \textbf{design cycle} is where you actually build the design.
+The \textbf{rigor cycle} matters because it can give you two types of additional knowledge.
+It provides past knowledge to ensure its invention and it's there to guarantee that the now product is a research contribution.
 
@@
 \includegraphics[width=0.4\textwidth]{raspberry pi setup.jpg}
-\caption{Insert caption to place below figure.}
+\caption{Raspberry Setup}
 \label{fig:setup} %always place your label after your caption!
@@
 
+\section{Raspberry pi}
+\begin{figure}[H]
+\centering 
+\includegraphics[width=0.4\textwidth]{Pi2ModB1GB_-comp.jpeg}
+\caption{Raspberry Pi 2 model B}
+\label{fig:raspberry} %always place your label after your caption!
+\end{figure}
+\begin{table}[H]
+	\centering \caption{Specificaties}
+	\begin{tabular}{|c|c|} \hline
+		Ethernet & 100 MBps \\ \hline
+		USB & 4 x USB 2.0 \\ \hline
+		Video out & HDMI 1.4 \\ \hline
+		Audio & 2 x analog \\ \hline
+		CPU & 900MHz quad-core ARM Cortex-A7 \\ \hline
+		card slot & Micro SD  \\ \hline
+	\end{tabular}
+		\label{tab:Specificaties}
+\end{table}
+The Raspberry Pi only consumes 3 watts, because of this it doesn't need active cooling. 
+With this subquestion I want to find out if it is possible to let users have small Raspberry Pi servers I also want to know what the performance of this small Raspberry Pi cloud is. 
+Resources:
+\cite{Pcextreme,nginx-load-balancing,nginx-load-balancing-2}
+
+For this research I want to investigate if it is possible to do more research in the 
+load balancing techniques that can be used in a raspberry pi. A example of this would be the round robin queuing~\cite{nginx-load-balancing,nginx-load-balancing-2}.
+
+\subsection{Raspberry Pi cloud projects}
+there have been several cloud projects with the raspberry Pi. \newline
+One of these has been the supercomputer build by Southampton~\cite{cox:2014}.
+Here they build it with 64 raspberry Pi's .
+They used a Message Passing interface to communicate between the raspberry pi's.
+The research was done in order to see what the performance of a low-power high performance cluster is.
+\newline
+The project of the university of Glasgow~\cite{tso:2013}.
+This data center has 56 Raspberry Pi's.
+It is build for research and education purposes for a cloud data center.
+They have a hadoop running on their servers.
+\newline
+There was another project called the Beowulf cluster~\cite{beowolf-setup}.
+This project was created for a phd assignment.
+This cluster is build for collaboratively processing sensor data.
+A Beowulf cluster is simply a collection
+of identical, (typically) commodity computer hardware based systems~\cite{beowolf-setup}.
+The big advantage of the Raspberry Pi in this project was that it is cheap and it does not need a cluster administrator to watch over everything you do.
+
 \section{State of the Art}
-Today there are many cloud services. This amount of cloud computing services is increasing fast \cite{armbrust:2009}.  Despite the attention
-from the research community, research and development of
-Cloud Computing services is still in it's childhood\cite{tso:2013}.
-Today there is a lot of people that use video streaming and this will become even more.
  People want to have everything has to be accessible through the network around the clock \cite{youseff:2008}.
@@
 \section{Acknowledgments}
+This paper would not have been possible without the help of Björn Postema and Nick Shot.
 

### 2015-03-09 research_proposal/research proposal.tex
changes

@@
 \usepackage{hyperref}
-
+\usepackage{tabularx}
+\usepackage{graphicx}
 \restylefloat{figure}
@@
 
-\title{micro data server using raspberry pi}
+\title{Micro Data Server using Raspberry Pi for Video Streaming}
 % In Bachelor Referaat at University of Twente the use of a subtitle is discouraged.
@@
 % 1st. author
-\alignauthor P.j.e. Velthuis\\
+\alignauthor P.J.E. Velthuis\\
        \affaddr{University of Twente}\\
@@
 \begin{abstract}
-This document describes a draft research proposal in the
-area of cloud computing services. The main research question
-is: What is the performance of raspberry pi load balancing techniques using video streaming? To answer this question a micro raspberry pi video streaming service will be build. 
+This document describes a research proposal in the
+area of cloud computing services.
+Cloud computing is a trend IT that customers move computing and data away from desktop and portable PCs into large data centers.
+These data centers require a lot of power and cooling.
+Nowadays 30 \% of the data coming from these data centers is video streaming.
+The Raspberry Pi is a device that might improve these problems.
+The main research question
+is therefore: Is it possible to improve availability algorithms for video streaming by using small scale Raspberry Pi’s data center?
+To answer this question a micro Raspberry Pi video streaming service will be build.
 \end{abstract}
 
-\keywords{Cloud computing, Raspberry Pi, ARM performance, micro data server, video streaming, load balancing}
+\keywords{Cloud computing, Raspberry Pi, micro data server, video streaming, load balancing}
 
 \section{Motivation}
-Today there are many cloud services. This amount of cloud computing services is increasing fast \cite{armbrust:2009}.  Despite the attention
-from the research community, research and development of
-Cloud Computing services is still in it's childhood\cite{tso:2013}. 
-In this research the Raspberry Pi cloud services will be investigated.
-A reason for this is that the density of servers has increased a lot in the past\cite{density}.
-There are new technologies such as for example the ARM processor.
-Many companies want to explore the possibilities of for example the Raspberry Pi and his ARM Processor.
-Some data centers even offer some cloud computing using the Raspberry Pi.
-A reason for this is the small location that the Raspberry Pi needs, and the low power usage of a Raspberry Pi\cite{hosting,Pcextreme}.
+The amount of cloud computing services is increasing fast \cite{armbrust:2009}.
+But despite the attention from the research community, research and development of Cloud Computing services is still in its early days~\cite{tso:2013}.
+\newline
+Cloud computing is a trend IT that customers move computing and data away from desktop and portable PCs into large data centers \cite{dikaiakos:2009}.
+In the future most internet users access internet services over lightweight portable devices.
+This requires a lot of data bandwidth.
+Video streaming is something that requires a lot of bandwidth.
+This bandwidth usage causes bottlenecks and small data servers can be build after these bottlenecks.
+This makes research on this topic very interesting.
+\newline
+In this research a small data server consisting of Raspberry Pi´s will be investigated.
+A reason for this is that data centers require a lot of space and cooling.
+There are now new technologies such as for example the powerful ARM processor.
+Many companies want to explore the possibilities of for example the Raspberry Pi and his ARM Processor \cite{Pcextreme}.
+Some data centers already offer some cloud computing using the Raspberry Pi.
+A reason for this is the small location that the Raspberry Pi needs, and the low power usage of a Raspberry Pi \cite{hosting,Pcextreme}.
 A Raspberry Pi has a power usage between the 3-5 Watt.
-A normal server has a power usage between the 75 and 150 watt \cite{Powerusage}.
-This could mean that it is better to use a Raspberry Pi for specific small tasks that do not demand a whole server.
-During this research there will be a investigation on the performance of the Raspberry pi as a server.
+A normal server has a power usage between the 75 and 250 Watt~\cite{Powerusage,beloglazov2012energy}.
+However the Raspberry Pi has less computing power then a normal server.
+The low power consumption and its computing power could mean that it is better to use a Raspberry Pi for specific small tasks that do not demand a whole server.
+During this research there will be a investigation on the performance of the Raspberry Pi as a small data server.
+\newline
 A Raspberry Pi can be the small data center for the future \cite{tso:2013}.
-The Raspberry is a rather cheap device for 35 euro.
+The Raspberry is a relatively cheap device for 40 euro.
 This makes it cheaper to do research in compared to a normal server.
-This is also the mean reason why the Raspberry pi was ones created.
-The current versions of the Raspberry Pi cannot perform the task of a large scale x86 server \cite{tso:2013}.
 Building a cloud like this can be a cost effective scale model\cite{tso:2013}.
 It's a ideal testbed for testing distributed software.
-During this research we will investigate the performance of a raspberry pi as a video streamer to other computers.
-The reason for investigating video streaming is because this demands a lot of bandwidth from the network and could be one of the first things that should be improved.
 
@@
 
-Today a lot of people watch their movies online using video streaming. 
-The Netherlands have for example one million subscribers for Netflix \cite{volkskrant}.
-Netflix is a video streaming service that makes HD movies watching possible.
+The Netherlands have one million subscribers for Netflix \cite{volkskrant}.
+Netflix is a popular video streaming service that makes HD movies watching possible.
 For this Netflix makes use of a content distribution network (CDN).
-On the internet this is also known as a on demand service \cite{Adhikari:2012}.
-Netflix makes use of MPEG-DASH a protocol that makes streaming over http possible \cite{martin:2013}.
+On the internet this is known as a on demand service \cite{Adhikari:2012}.
+Netflix makes use of MPEG-DASH a protocol that makes streaming over HTTP possible \cite{martin:2013}.
 The problem is that Netflix is responsible for  29.7\% of the peak downstream traffic in US \cite{Adhikari:2012}.
+\newline
 In the Netherlands more and more users are making use of video streaming as Youtube and Netflix.
-In this research there will be a investigation on the possibility to make small micro data centers with raspberry pi's.
-This research will try to find out how this cloud works.
-There will be taken a look in for example the load balancing of video streaming.
-In this way it can be possible to see improvements that can be made in the load balancing so that the servers can be used more efficient.
-This is also build to learn more from load balancing and a computer cluster.
-This can be really useful, because nowadays it's still done on relatively expensive servers.
+This makes it interesting to do more research in video streaming by cloud computers.
+Most of the research nowadays happen on expensive large servers \cite{tso:2013}.
+For this it can be very useful to see if it is possible to do research on a small computer like a Raspberry Pi.
+The problem is that we do not know if video streaming on a small raspberry pi cluster is possible.
 
@@
 The main research question
-is: What is the performance of a raspberry pi load balancing techniques using video streaming?
+\begin{center} 
+Is it possible to improve availability algorithms for video streaming by using small scale Raspberry Pi’s data center? \end{center}
+This research will be part literature study and a part of it will be building a small Raspberry Pi cloud to measure the availability of the video streaming.
+Here below there are several questions to come to a good answer for the main research question.
+\newline \newline
+\subsection{Why are small scale data centers being used?}
+In this research there will be a small scale cloud data center with the Raspberry Pi.
+The main motivation behind this is that it is ways to expensive to simulate large scale cloud computing.
+Resources for this motivation:
+\cite{southampton, Powerusage, cox:2014} \newline
+Another reason is the small location that is needed using a small scall data center. On the size of the data center is currently done a lot of research \cite{Pcextreme}. \newline
+Small scale cloud computing is cloud computing with smaller computation amounts than normal.
+This can mean that it is better for different tasks.
+More motivation is that it does not use a lot cooling and power \cite{tso:2013}.
+Resources available for small scale cloud computing:
+\cite{Pcextreme,armbrust:2009,richardson:2012,abrahamsson:2013,southampton, tso:2013, beloglazov:2010, qian:2009, hofer:2011, drago2012inside, dropbox, owncloud, Miettinen:2010:EEM:1863103.1863107, beloglazov2012energy,cox:2014}
 
-This research will be part literature study and a part of it will be building a small Raspberry Pi cloud to measure balancing techniques on the Raspberry Pi.
-Here below there are several questions to come to a good answer for the main research question.
+\subsection{Is it useful to use Raspberry Pi’s for video streaming?}
+ The Netherlands have one million subscribers for Netflix \cite{volkskrant}.
+Netflix is a video streaming service that makes HD movies watching possible.
+This requires a lot of internet bandwidth and it could be useful to do the streaming in small scale data centers nearby.
+To investigate what Netflix really is there are the following resources:
+\cite{volkskrant, Adhikari:2012} \newline
+Netflix makes use of MPEG-DASH a protocol that makes streaming over HTTP possible.
+In this research there will be an investigation in the video streaming as a cloud service in a small scale data center.
+To investigate what that is there are the following resources:
+\cite{raspberry-video,video-1080p, plissonneau:2012, computer-networking}
 
-\subsection{What is small scale cloud computing?}
-In this research there will be small scale cloud computing with the Raspberry Pi.
-The main motivation behind is that it is ways to expensive to simulate large scale cloud computing.
-Resources for this:
-\cite{southampton, Powerusage, cox:2014}
-Another reason is the small location that is needed used with small scale cloud computing for Raspberry Pi's\cite{Pcextreme}.
-Because of this it could be better in executing small tasks.
-Small scale cloud computing is cloud computing with smaller computation amounts than normal.
-More motivation is that it does not use a lot cooling and power.
-Resources available for small scale cloud computing:
-\cite{Pcextreme,armbrust:2009,richardson:2012,abrahamsson:2013,southampton}
+\subsection{What is the perfect setup for a Raspberry Pi video streaming cluster?}
+This research question will look into previous cloud cluster projects: 
+\cite{abrahamsson:2013,southampton, tso:2013, beloglazov:2010,cox:2014} \newline
+From this a perfect setup for the hardware of the Raspberry Pi's will be build. There will be taken a look into the different software that has to be used. For example: 
+\cite{raspberry-video,video-1080p, permission, nmon,bandwidth,ab}
 
-\subsection{What is cloud video streaming?}
-There are many kinds of cloud computing and cloud services.
-These include a webserver, a DNS server, a chat server, a mail server, a vpn server or a monitoring server or even a video streaming service.
-Information video streaming Netflix:
-\cite{volkskrant, Adhikari:2012}
-Netflix makes use of MPEG-DASH a protocol that makes streaming over http possible.
-In this research I want to investigate more in the video streaming as a cloud service.
-To investigate what that is are the following resources:
-\cite{g-streamer,raspberry-video,video-1080p, plissonneau:2012}
-
-\subsection{What kind of different load balancing techniques are there?}
-In distributed servers it is very important that good load balancing takes place.
-For this reason I want to further investigate in what kind of load balancing techniques there are.
-Resources I could use for load balancing:
-\cite{nginx-load-balancing,nginx-load-balancing-2,computer-networking,wolf:1997,load-balancing}
-
-\subsection{Is it reachable to build small personal Raspberry Pi clouds for services?}
-With this subquestion I want to find out if it is possible to let users have small Raspberry Pi servers I also want to know what the performance of this small Raspberry Pi cloud is. 
-Resources:
-\cite{Pcextreme,nginx-load-balancing,nginx-load-balancing-2}
-
-\subsection{Is it possible to improve load balancing using small scale Raspberry Pi's?}
-For this research I want to investigate if it is possible to do more research in the 
-load balancing techniques that can be used in a raspberry pi. A example of this would be the round robin protocol.
-Resources:
-\cite{nginx-load-balancing,nginx-load-balancing-2}
+\subsection{How does the availability change using different load balancing techniques with the Raspberry Pi?}
+With this subquestion we will look into the different load balancing techniques.
+In a video streaming service it's very important to have high performance and availability.
+That's why it's interesting to do more research on this.
+Resources for load balancing on Raspberry Pi:
+\cite{nginx-load-balancing,nginx-load-balancing-2, nginx-load-balancing-3, Raspberry-media-server, dropbox-clone} \newline
+Things that are interesting to look into are for example bandwidth usage, power usage, i/o throughput. For this the following resources will be used: 
+\cite{nmon,bandwidth,ab}
 
@@
 this is a method to solve field problems.
-This research will make use of the design Science method proposed by Hevner\cite{hevner:2007}.
+This research will make use of the design Science method proposed by Hevner~\cite{hevner:2007}.
+\begin{figure}[H]
+	\centering 
+	\includegraphics[width=0.4\textwidth]{Design_science.png}
+	\caption{Design Science}
+	\label{fig:design} %always place your label after your caption!
+\end{figure}
+For this design research the research will specify the requirements, existing solutions, new solutions and the result of this new solution. After that a conclusion will be given.
 
 \section{Research approach}
-For the experiment we need a Raspberry Pi with a static Ip address and we need a sd card for the OS.
-For the experiment we need a Raspberry Pi B that can make use of the Ethernet.
+\begin{figure}[H]
+	\centering 
+	\includegraphics[width=0.4\textwidth]{Pi2ModB1GB_-comp.jpeg}
+	\caption{Raspberry Pi 2 model B}
+	\label{fig:raspberry} %always place your label after your caption!
+\end{figure}
+\begin{table}[H]
+	\centering \caption{Specificaties}
+	\begin{tabular}{|c|c|} \hline
+		Ethernet & 100 MBps \\ \hline
+		USB & 4 x USB 2.0 \\ \hline
+		Video out & HDMI 1.4 \\ \hline
+		Audio & 2 x analog \\ \hline
+		CPU & 900MHz quad-core ARM Cortex-A7 \\ \hline
+		card slot & Micro SD  \\ \hline
+	\end{tabular}
+	\label{tab:Specificaties}
+\end{table}
+For the experiment we need a Raspberry Pi B or Raspberry Pi 2 that can make use of the Ethernet.
 This is because a Raspberry Pi can be used as a webserver and this is needed to have this in order to make video streaming possible.
 This webserver will make video streaming possible.
-It will have a VPN to make it possible to put video's on the Raspberry pi \cite{VPN:2014}.
-So I will first make this video streaming webserver. 
+Beside the Raspberry Pi a several other things will be needed.
+For this we have a cost structure:
+\begin{table}[H]
+	\centering 
+	\caption{Cost summary \cite{iapc}}
+	\begin{tabular}{|c|c|c|c|c|c} \hline
+		Device & cost piece& use & amount & total cost \\ \hline
+		Raspberry 
+		Pi 2 & 39,50 & cloud cluster & 8 & 316  \\ \hline
+		UTP kabel & 1,10 & data kabel & 8 & 8,80  \\ \hline
+		Micro usb kabel&1 & charging & 8 & 8  \\ \hline
+		switch & 40 & internet & 1 & 40  \\ \hline
+		& & & &  372,80  \\ \hline
+	\end{tabular}
+	\label{tab:cost}
+\end{table}
+
+So first he video streaming webserver will be made. 
 After this we will make a cluster with one Raspberry Pi as a load balancer and the other two as a video stream pi.
-If I have made such I cluster I can start doing some tests on it.
+The university of Southampton has made a cluster possible \cite{southampton}.
+So I think it is also possible for video streaming.
+With this there several performance tests can be done.
 For example some test in streaming in different quality with load balancing.
@@
 \includegraphics[width=0.4\textwidth]{raspberry pi setup.jpg}
-\caption{Insert caption to place below figure.}
+\caption{Setup}
 \label{fig:setup} %always place your label after your caption!
 \end{figure}
-For the load balancing we will make use of Nginx for this we will use the following sources:
-\cite{nginx-load-balancing, nginx-load-balancing-2}
+
+\begin{table}[H]
+	\centering \caption{Variables}
+	\begin{tabular}{|c|} \hline
+		\textbf{Input}  \\ \hline
+		Data from SD card \\ \hline
+		Data from Internet \\ \hline
+		Electrical Power \\ \hline
+		Cooling \\ \hline
+		Measurement tools \\ \hline
+		\textbf{System}  \\ \hline
+		Operating system (Raspbian) \\ \hline
+		Measurement software \\ \hline
+		Processing power \\ \hline
+	\textbf{Output} \\ \hline
+		data  over network (video stream)\\ \hline
+		data over HDMI \\ \hline
+	\end{tabular}
+	\label{tab:variables}
+
+\end{table}
+The system will make use of several variables~\ref{tab:variables}.
+We can distinguish three types which we need to keep in our mind during the research.
+We have input variables that define the input.
+The system has not a lot of variables, because you can choose for example a operating system, but not change the software in the operating system.
+By using the software of the system we can get the different result in the output variables.
 
@@
 \begin{tabular}{|c|c|c|} \hline
-		\textbf{Week} & \textbf{Date} & \textbf{Activity} \\ \hline 
-		6-9& 6 Feb. -27 Feb& Collect literature and software\\ \hline 
-		10& 2 March - 9 March& Deadline peer review and proposal \\ \hline
-		12& 16 March -22 March & \textbf{Deadline proposal} \\ \hline
-		13 & 23 March -30 March &  \textbf{Accept Reject proposal} \\ \hline
-		10-14& 2 March 12 April& Start building test environment \\ \hline
-		14& 6 April - 12 April& Answer subquestion 1  \\ \hline
-		15& 13 April - 20 April& Answer subquestion 2\\ \hline
-		16& 21 April - 28 April& Answer subquestion 3\\ \hline
-		14-16 & 6 April - 28 April & working on test environment \\ \hline
-		17& 1 May - 7 May & Answer subquestion 4 \\ \hline
-		18& 4 May-10 May& conclusion and check coherency \\ \hline
-		19& 11 May-18 May& Finalize paper \\ \hline
-		22& 1 June-7 June&  \textbf{Deadline paper} \\ \hline
-		26 &22 June - 26 June & \textbf{Conference} \\ \hline
+		\textbf{Week} & \textbf{Start Date} & \textbf{Activity} \\ \hline 
+		6-13& 6 Feb& Collect literature and software\\ \hline 
+		12& 16 March& Deadline peer review and proposal \\ \hline
+		14& 23-30 March & \textbf{Deadline proposal} \\ \hline
+		15 & 23-30 March &  \textbf{Accept Reject proposal} \\ \hline
+		15-14& 30 March& Start building test environment \\ \hline
+		16& 6 April & Answer subquestion 1  \\ \hline
+		17& 13 April & Answer subquestion 2\\ \hline
+		18& 21 April & Answer subquestion 3\\ \hline
+		16-18 & 6 April  & working on test environment \\ \hline
+		17& 1 May  & Answer subquestion 4 \\ \hline
+		18& 4 May & conclusion and check coherency \\ \hline
+		19& 11 May & Finalize paper \\ \hline
+		22& 1 June &  \textbf{Deadline paper} \\ \hline
+		23-25& 8 june & presentation preperation \\ \hline
+		26 & 22 June & \textbf{Conference} \\ \hline
 		\end{tabular}
@@
 \section{State of the Art}
-Today there are many cloud services. This amount of cloud computing services is increasing fast \cite{armbrust:2009}.  Despite the attention
+The amount of cloud computing services is increasing fast \cite{armbrust:2009}. Despite the attention
 from the research community, research and development of
-Cloud Computing services is still in it's childhood\cite{tso:2013}.
-Today there is a lot of people that use video streaming and this will become even more.
-People want to have everything has to be accessible through the network around the clock \cite{youseff:2008}.
+Cloud Computing services is still in it's early days~\cite{tso:2013}.
+Today there is a lot of customers that use video streaming and this will become even more.
+Customers want to have everything has to be accessible through the network around the clock \cite{youseff:2008}.
 One thing that people want on demand are there film series.
-Currently Netflix has 30\% of the downstream in the United States.
+Currently Netflix has 30\% of the downstream in the United States~\cite{computer-networking}.
 This downstream is huge and that means that there is optimization in this branch possible.
@@
 The Raspberry Pi is made for research and education purposes \cite{raspberry-pi}.
-The Raspberry Pi is a cheap device costing around 35 euro.
+The Raspberry Pi is a cheap device costing around 40 euro.
 It has a power consumption of only three watt and has quite good processor.
@@
 In this research we will make a small raspberry cloud to do research on video streaming using HTTP.
-This will be done using the design Science method proposed by Hevner\cite{hevner:2007}.
-After we have done this for the Raspberry Pi there will be looked at streaming using Amazon.
-In this way we can see how the results are compared to streaming via Amazon.
-This research will try to find out if the raspberry has enough processing power to stream to multiple web clients.
+This will be done using the design Science method proposed by Hevner~\cite{hevner:2007}.
+This research will try to find out if the raspberry has enough processing power and bandwidth to be a suitable streamer to multiple web clients.
 The cloud performance can now be better researched, because everything is at one location and the information about what processes are running on the pi are well defined.

### 2015-03-21 research_proposal/research proposal.tex
research proposal finished

@@
 \restylefloat{table}
+\usepackage{xcolor}
+\newcommand\todo[1]{
+	\textcolor{green}{#1}
+	}
 \begin{document}
@@
 
-\title{Micro Data Server using Raspberry Pi for Video Streaming}
+\title{Small Data Center using Raspberry Pi for Video Streaming}
 % In Bachelor Referaat at University of Twente the use of a subtitle is discouraged.
@@
 Nowadays 30 \% of the data coming from these data centers is video streaming.
-The Raspberry Pi is a device that might improve these problems.
-The main research question
-is therefore: Is it possible to improve availability algorithms for video streaming by using small scale Raspberry Pi’s data center?
+The Raspberry Pi is a not so costly device that can do research in Video streaming.
+The main research question is therefore: How well does the Raspberry Pi perform in small scale data centers with video streaming?
 To answer this question a micro Raspberry Pi video streaming service will be build.
@@
 \section{Motivation}
-The amount of cloud computing services is increasing fast \cite{armbrust:2009}.
-But despite the attention from the research community, research and development of Cloud Computing services is still in its early days~\cite{tso:2013}.
-\newline
-Cloud computing is a trend IT that customers move computing and data away from desktop and portable PCs into large data centers \cite{dikaiakos:2009}.
-In the future most internet users access internet services over lightweight portable devices.
-This requires a lot of data bandwidth.
-Video streaming is something that requires a lot of bandwidth.
-This bandwidth usage causes bottlenecks and small data servers can be build after these bottlenecks.
-This makes research on this topic very interesting.
+Today most of us have some data in the cloud. But despite the attention from the community, research and development of Cloud Computing services are still in its early days~\cite{tso:2013}. \newline
+Cloud computing is a trend IT that moves customers  computing and data away from desktop and portable PCs into large data centers \cite{dikaiakos:2009}.
+In the future most internet users will access internet services over lightweight portable devices requiring a lot of data bandwidth \cite{dikaiakos:2009}.
+Video streaming for example requires a lot of bandwidth \cite{Adhikari:2012}.
+This bandwidth usage causes bottlenecks.
+To prevent these bottlenecks we build data centers around the globe.
+On these data servers a lot of improvements can be made.
+\todo{bron zoeken}
  \newline
@@
 There are now new technologies such as for example the powerful ARM processor.
-Many companies want to explore the possibilities of for example the Raspberry Pi and his ARM Processor \cite{Pcextreme}.
+Many companies want to explore the possibilities of for example the Raspberry Pi, this because of it's powerful processor compared to the price \cite{Pcextreme}.
 Some data centers already offer some cloud computing using the Raspberry Pi.
-A reason for this is the small location that the Raspberry Pi needs, and the low power usage of a Raspberry Pi \cite{hosting,Pcextreme}.
+Another reason for this is the small location that the Raspberry Pi needs, and the low power usage of a Raspberry Pi \cite{hosting,Pcextreme}.
 A Raspberry Pi has a power usage between the 3-5 Watt.
@@
 However the Raspberry Pi has less computing power then a normal server.
-The low power consumption and its computing power could mean that it is better to use a Raspberry Pi for specific small tasks that do not demand a whole server.
+The low power consumption and its computing power could mean that it is better to use a Raspberry Pi for specific small tasks that do not demand an entire.
 During this research there will be a investigation on the performance of the Raspberry Pi as a small data server.
@@
 A Raspberry Pi can be the small data center for the future \cite{tso:2013}.
-The Raspberry is a relatively cheap device for 40 euro.
+The Raspberry is a less costly device and is sold for 40 euro.
 This makes it cheaper to do research in compared to a normal server.
@@
 The problem is that Netflix is responsible for  29.7\% of the peak downstream traffic in US \cite{Adhikari:2012}.
+Because of this downstream the two main providers Comcast and  AT\&T were limiting the downstream of Netflix.
+This caused a lot of criticism and a new law for net neutrality has been made \cite{net-neutrality}.
 \newline
 In the Netherlands more and more users are making use of video streaming as Youtube and Netflix.
-This makes it interesting to do more research in video streaming by cloud computers.
+The downstreaming problems and the more users making use of streaming make it interesting to do more research in video streaming by cloud computers.
 Most of the research nowadays happen on expensive large servers \cite{tso:2013}.
 For this it can be very useful to see if it is possible to do research on a small computer like a Raspberry Pi.
-The problem is that we do not know if video streaming on a small raspberry pi cluster is possible.
+The problem is that we do not know if video streaming on a small Raspberry Pi cluster is possible.
 
@@
 \begin{center} 
-Is it possible to improve availability algorithms for video streaming by using small scale Raspberry Pi’s data center? \end{center}
+How well does the Raspberry Pi perform in small scale data centers with video streaming? 
+\end{center}
 This research will be part literature study and a part of it will be building a small Raspberry Pi cloud to measure the availability of the video streaming.
 Here below there are several questions to come to a good answer for the main research question.
-\newline \newline
-\subsection{Why are small scale data centers being used?}
+
+\subsection{What are small scale data centers with video streaming and why are they used?}
 In this research there will be a small scale cloud data center with the Raspberry Pi.
-The main motivation behind this is that it is ways to expensive to simulate large scale cloud computing.
+The main motivation behind this is that it is ways to expensive to do it on multiple large servers.
 Resources for this motivation:
 \cite{southampton, Powerusage, cox:2014} \newline
-Another reason is the small location that is needed using a small scall data center. On the size of the data center is currently done a lot of research \cite{Pcextreme}. \newline
+Another reason is that little space is needed using a small scall data center. On the size of the data center is currently done a lot of research \cite{Pcextreme}. \newline
 Small scale cloud computing is cloud computing with smaller computation amounts than normal.
@@
 
-\subsection{Is it useful to use Raspberry Pi’s for video streaming?}
+\subsection{Is the Raspberry Pi’s usable for video streaming?}
  The Netherlands have one million subscribers for Netflix \cite{volkskrant}.
@@
 This requires a lot of internet bandwidth and it could be useful to do the streaming in small scale data centers nearby.
-To investigate what Netflix really is there are the following resources:
+To investigate how video streaming at Netflix really works there are the following resources:
 \cite{volkskrant, Adhikari:2012} \newline
 Netflix makes use of MPEG-DASH a protocol that makes streaming over HTTP possible.
-In this research there will be an investigation in the video streaming as a cloud service in a small scale data center.
+In this research there will be an investigation in the video streaming as a cloud service for a Raspberry Pi.
 To investigate what that is there are the following resources:
@@
 
-\subsection{What is the perfect setup for a Raspberry Pi video streaming cluster?}
+\subsection{How to fit the Raspberry Pi's into a data center considering cooling, space allocation and power?}
 This research question will look into previous cloud cluster projects: 
 \cite{abrahamsson:2013,southampton, tso:2013, beloglazov:2010,cox:2014} \newline
-From this a perfect setup for the hardware of the Raspberry Pi's will be build. There will be taken a look into the different software that has to be used. For example: 
-\cite{raspberry-video,video-1080p, permission, nmon,bandwidth,ab}
+From this a good setup for this Raspberry Pi project will be build.
+For this power, cooling and location will be taken into account.
+With this an advise can be made about how to fit the Raspberry Pi into the data center.
+\subsection{What setup does a Raspberry Pi cloud with video streaming require?}
+This research question will look into previous cloud cluster projects: 
+\cite{abrahamsson:2013,southampton, tso:2013, beloglazov:2010,cox:2014} \newline
+ There will be taken a look into the different software that has to be used. For example: 
+\cite{raspberry-video,video-1080p, permission, nmon,bandwidth,ab, mosberger1998httperf, httperf-2, raspbian}
 
-\subsection{How does the availability change using different load balancing techniques with the Raspberry Pi?}
+\subsection{How is availability in a Raspberry pi cluster with video streaming affected by various load balancing techniques?}
 With this subquestion we will look into the different load balancing techniques.
@@
 	\caption{Cost summary \cite{iapc}}
-	\begin{tabular}{|c|c|c|c|c|c} \hline
-		Device & cost piece& use & amount & total cost \\ \hline
-		Raspberry 
-		Pi 2 & 39,50 & cloud cluster & 8 & 316  \\ \hline
-		UTP kabel & 1,10 & data kabel & 8 & 8,80  \\ \hline
-		Micro usb kabel&1 & charging & 8 & 8  \\ \hline
+	\begin{tabular}{|c|c|c|c|c|p{5cm}} \hline
+		Device 			& cost piece	& use 			& amount & total cost \\ \hline
+		Raspberry Pi 2 	& 32,60 		& cloud cluster & 8 & 316  \\ \hline
+		UTP cable		& 1,10 			& data cable 	& 8 & 8,80  \\ \hline
+		Micro usb cable	& 1 			& charging 		& 8 & 8  \\ \hline
 		switch 			& 40 			& internet 		& 1 & 40  \\ \hline
+		micro SD 		& 				& 				& 	& \\ \hline
 		& & & &  372,80  \\ \hline
@@
 For example some test in streaming in different quality with load balancing.
-The setup of the raspberry Pi can be seen in the figure below ~\ref{fig:setup}.
+The setup of the Raspberry Pi can be seen in the figure below ~\ref{fig:setup}.
 
@@
 
-\begin{table}[H]
-	\centering \caption{Variables}
-	\begin{tabular}{|c|} \hline
-		\textbf{Input}  \\ \hline
-		Data from SD card \\ \hline
-		Data from Internet \\ \hline
-		Electrical Power \\ \hline
-		Cooling \\ \hline
-		Measurement tools \\ \hline
-		\textbf{System}  \\ \hline
-		Operating system (Raspbian) \\ \hline
-		Measurement software \\ \hline
-		Processing power \\ \hline
-	\textbf{Output} \\ \hline
-		data  over network (video stream)\\ \hline
-		data over HDMI \\ \hline
-	\end{tabular}
-	\label{tab:variables}
-
-\end{table}
-The system will make use of several variables~\ref{tab:variables}.
-We can distinguish three types which we need to keep in our mind during the research.
-We have input variables that define the input.
-The system has not a lot of variables, because you can choose for example a operating system, but not change the software in the operating system.
-By using the software of the system we can get the different result in the output variables.
-
 \section{Planning}
@@
 		6-13& 6 Feb& Collect literature and software\\ \hline 	
-		12& 16 March& Deadline peer review and proposal \\ \hline
 		14& 23-30 March & \textbf{Deadline proposal} \\ \hline
-		15 & 23-30 March &  \textbf{Accept Reject proposal} \\ \hline
-		15-14& 30 March& Start building test environment \\ \hline
-		16& 6 April & Answer subquestion 1  \\ \hline
-		17& 13 April & Answer subquestion 2\\ \hline
-		18& 21 April & Answer subquestion 3\\ \hline
+		16 & 1 April &  \textbf{Accept Reject proposal} \\ \hline
+		14-15& 30 March& Start building test environment \\ \hline
+		17& 6 April & Answer subquestion 1  \\ \hline
+		18& 13 April & Answer subquestion 2\\ \hline
+		19& 21 April & Answer subquestion 3\\ \hline
 		16-18 & 6 April  & working on test environment \\ \hline
-		17& 1 May  & Answer subquestion 4 \\ \hline
-		18& 4 May & conclusion and check coherency \\ \hline
-		19& 11 May & Finalize paper \\ \hline
+		20& 1 May  & Answer subquestion 4 \\ \hline
+		21& 4 May & conclusion and check coherency \\ \hline
+		21-22& 11 May & Finalize paper \\ \hline
 		22& 1 June &  \textbf{Deadline paper} \\ \hline
-		23-25& 8 june & presentation preperation \\ \hline
+		23& 8 June & Peer review \\ \hline
+		24-25& 15 june & presentation preperation \\ \hline
 		26 & 22 June & \textbf{Conference} \\ \hline
@@
 The Raspberry Pi is made for research and education purposes \cite{raspberry-pi}.
-The Raspberry Pi is a cheap device costing around 40 euro.
-It has a power consumption of only three watt and has quite good processor.
+The Raspberry Pi is a not so costly device costing around 40 euro.
+It has a power consumption of only three watt and has for the price a processor that is extremely well equipped to execute small tasks.
 For this reason it might be very useful for small scale cloud computing.
-The raspberry Pi is a small device and is excellent for a lot of small devices in a relatively small place.
+The Raspberry Pi is a small device and is excellent for a lot of small devices in a relatively small place.
 The Raspberry Pi doesn't use cooling and it can be used for very rapid elasticity and on-demand self-service.
 Because of it's cooling features and low power consumption it might be a good alternative for the nowadays high power consuming data centers.
-The raspberry pi is really small so it is a lot easier to place extra pi in a data center compared to a normal server.
+The Raspberry Pi is really small so it is a lot easier to place extra pi in a data center compared to a normal server.
 The Raspberry Pi has one drawback and that is that the processing power is relatively low.
@@
 
-In this research we will make a small raspberry cloud to do research on video streaming using HTTP.
+In this research we will make a small Raspberry Pi cloud to do research on video streaming using HTTP.
 This will be done using the design Science method proposed by Hevner~\cite{hevner:2007}.
-This research will try to find out if the raspberry has enough processing power and bandwidth to be a suitable streamer to multiple web clients.
+This research will try to find out if the Raspberry Pi has enough processing power and bandwidth to be a suitable streamer to multiple web clients.
 The cloud performance can now be better researched, because everything is at one location and the information about what processes are running on the pi are well defined.

### 2015-05-26 paper/paper.tex
new version

--- 2015-02-23 paper/paper.tex
@@
 % e.g.
-% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
 % \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
 %
-% ---------------------------------------------------------------------------------------------------------------
+
 % This .tex source is an example which *does* use
@@
 %
-
 % refers to the cls file being used
@@
 \usepackage{hyperref}
+\usepackage{xcolor}
+\usepackage{enumitem}
+\usepackage{tabularx}
 
+\newcommand\todo[1]{
+	\textcolor{green}{#1}
+}
 \restylefloat{figure}
@@
 
-\title{micro data server using raspberry pi}
+\title{Small Data Center using Raspberry Pi 2 for Video Streaming}
 % In Bachelor Referaat at University of Twente the use of a subtitle is discouraged.
- \subtitle{Research Proposal}
+ \subtitle{}
 
@@
 \begin{abstract}
-This document describes a draft research proposal in the
-area of cloud computing services. The main research question
-is: What is the performance of raspberry pi load balancing service using video streaming? To answer this question a micro raspberry pi video streaming service will be build. 
+This is a paper in the area of cloud computing.
+Cloud computing is a trend IT that customers move computing and data away from desktop and portable PCs into data centers.
+These data centers require a lot of power and cooling.
+Nowadays approximately 30\% of the data coming from these data centers is video streaming.
+The Raspberry Pi 2 is a low cost device that can be used in a cloud for video streaming.
+In this paper a further investigation in the Raspberry Pi 2 cloud is done.
+This research is a design research in which a design is made for a video streaming cloud consisting of Raspberry Pi's.
 \end{abstract}
 
-\keywords{Cloud computing, Raspberry Pi, ARM performance, micro data server, video streaming, load balancing}
+\keywords{Cloud computing, Raspberry Pi 2,  micro data center, video streaming, load balancing}
 
 \section{Introduction}
-Today there are many cloud services. This amount of cloud computing services is increasing fast \cite{armbrust:2009}.  Despite the attention
-from the research community, research and development of Cloud Computing services is still in it's childhood\cite{tso:2013}. 
-In this research the Raspberry Pi cloud services will be investigated.
-A reason for this is that the density of servers has increased a lot in the past\cite{density}.
-There are new technologies such as for example the ARM processor.
-Many companies want to explore the possibilities of for example the Raspberry Pi and his ARM Processor.
-Some data centers even offer some cloud computing using the Raspberry Pi.
-A reason for this is the small location that the Raspberry Pi needs, and the low power usage of a Raspberry Pi\cite{hosting,Pcextreme}.
-A Raspberry Pi has a power usage between the 3-5 Watt.
-A normal server has a power usage between the 75 and 150 watt \cite{Powerusage}.
-This could mean that it is better to use a Raspberry Pi for specific small tasks that do not demand a whole server.
-During this research there will be a investigation on the performance of the Raspberry pi as a server.
-A Raspberry Pi can be the small data center for the future \cite{tso:2013}.
-The Raspberry is a rather cheap device for 35 euros.
-This makes it cheaper to do research in compared to a normal server.
-This is also the mean reason why the Raspberry pi was ones created.
-The current versions of the Raspberry Pi cannot perform the task of a large scale x86 server \cite{tso:2013}.
+Today most of us have some data in the cloud. But despite the attention from the community, research and development of Cloud Computing services are still in its early days~\cite{tso:2013}. \newline
+Cloud computing is a trend in IT that moves customers computing and data away from desktop and portable PCs into large data centers \cite{dikaiakos:2009}.
+In the future most internet users are expected to access internet services over lightweight portable devices requiring a lot of data bandwidth \cite{dikaiakos:2009}.
+This bandwidth usage causes bottlenecks.
+To prevent these bottlenecks people build data centers around the globe.
+On these data servers a lot of improvements can be made \cite{abrahamsson:2013,beloglazov:2010}.
+These data servers for example require a lot of space and cooling.
+There are now new technologies such as for example the powerful ARM processor.
+Many companies want to explore the possibilities of the Raspberry Pi 2 , because of its ARM processor and the price \cite{Pcextreme}.
+Some data centers already offer some cloud computing using the Raspberry Pi 2.
+\newline
+A Raspberry Pi 2 has a power usage between the 3-5 Watt and is a small computer.
+A normal server has a power usage between the 75 and 250 watt~\cite{Pcextreme,beloglazov2012energy}.
+The low power consumption and its computing power could mean that it is better to use a Raspberry Pi 2 for specific small tasks that do not demand an entire server.
+For this reason research will be done on the performance of the Raspberry Pi 2 as a small data center.
+\newline
+A Raspberry Pi cloud can be the small data center for the future \cite{tso:2013}.
+The Raspberry is sold for 40 euro, this price makes it cheaper to do research in compared to a normal server.
 Building a cloud like this can be a cost effective scale model\cite{tso:2013}.
 It's a ideal testbed for testing distributed software.
-During this research we will investigate the performance of a raspberry pi as a video streamer to other computers.
-The reason I want to investigate it with video streaming is because this demands a lot of bandwidth from the network and could be one of the first things that should be improved.
 
-Today a lot of people watch their movies online using video streaming. 
-The Netherlands have for example one million subscribers for Netflix \cite{volkskrant}.
-Netflix is a video streaming service that makes HD movies watching possible.
+The Netherlands have one million subscribers for Netflix \cite{volkskrant}.
+Netflix is a popular video streaming service that makes HD movies watching possible.
 For this Netflix makes use of a content distribution network (CDN).
-On the internet this is also known as a on demand service \cite{Adhikari:2012}.
-Netflix makes use of MPEG-DASH a protocol that makes streaming over http possible \cite{martin:2013}.
-The problem is that Netflix is responsible for  29.7\% of the peak downstream traffic in US  \cite{Adhikari:2012}.
-In the Netherlands more and more users are making use of video streaming as Youtube and Netflix.
-In this research there will be a investigation on the possibility to make small micro data centers with raspberry pi's.
-This research will try to find out how this cloud works.
-There will be taken a look in for example the load balancing of video streaming.
-In this way it can be possible to see improvements that can be made in the load balancing so that the servers can be used more efficient.
-This is also build to learn more from load balancing and a computer cluster.
-This can be really useful, because nowadays it's still done on relatively expensive servers.
+On the internet this is known as an on demand service \cite{Adhikari:2012}.
+Netflix makes use of MPEG-DASH a protocol that makes streaming over HTTP possible \cite{martin:2013}.
+The problem is that Netflix is responsible for  29,7\% of the peak downstream traffic in US \cite{Adhikari:2012}.
+Because of this downstream the two main providers Comcast and  AT\&T were limiting the downstream of Netflix.
+This caused a lot of criticism and a new law for net neutrality has been made as a solution for this criticism \cite{net-neutrality}.
+\newline
+In the Netherlands video streaming services such as Youtube and Netflix have an increasing amount of users.
+The data streaming problems coming from these increasing amount of users make it interesting to do more research in data centers with video streaming.
+Most of the research in computer science nowadays happen on expensive large servers \cite{tso:2013}.
+For this it can be very useful to see if it is possible to do research on a small computer like a Raspberry Pi 2.
+The problem is that we do not know if video streaming in a cloud consisting of Raspberry Pi's is possible.
 
-In this paper we will try to measure the performance of different load balancing techniques using the Raspberry Pi. For this the main research question will be: 
+In this paper there will be an investigation in how useful the Raspberry Pi 2 is in a data center with video streaming.
+To come to an answer there will be taken a look into the performance of the Raspberry Pi 2.
+For this the main research question will be:
 \begin{center}
- What is the performance of a raspberry pi load balancing techniques using video streaming?
+How well does the Raspberry Pi 2 perform in small scale data centers with video streaming? 
 \end{center}
@@
 In order to come to a good answer we need to  research several things.
-Therefore several sub-questions will be researched.
+Therefore some sub-questions will be researched.
 These sub-questions will altogether provide a answer to the main research question.
@@
 \begin{enumerate}
-	\item What is small scale cloud computing?
-	\item What is cloud video streaming?
-	\item What kind of different load balancing techniques are there?
-	\item Is it reachable to build small personal Raspberry Pi clouds for services?
-	\item Is it possible to improve load balancing using small scale Raspberry Pi's? 
+	\item What are small scale data centers with video streaming and why are they used?
+	\item Is the Raspberry Pi's usable for video streaming?
+	\item How to fit the Raspberry Pi's into a data center considering cooling, space allocation and power?
+	\item What setup does a Raspberry Pi cloud with video streaming require?
+	\item How is availability in a Raspberry pi cluster with video streaming affected by various load balancing techniques? 
 \end{enumerate}
 
-This research will be part literature study and a part of it will be building a small Raspberry Pi cloud to analyze balancing techniques on the Raspberry Pi.
+This research is part literature study and a part of it is building a small Raspberry Pi cloud to analyze balancing techniques on the Raspberry Pi 2.
 For this research cloud video streaming is one of the specific aspects that will be investigated.
-The load balancing techniques will be optimized for the video streaming.
-The first three research questions will describe the state of the art.
-The last two sub-questions will go into the technical research that will investigate the performance and possibility of Raspberry Pi's for cloud video streaming.
-They last one will investigate of their are improvements in load balancing possible.
-The five sub-questions are being looked at in the next five sections.
-Followed by a final section for conclusions and identified areas for future
-work.
-
-\section{Small scale computing}
-Today there are many cloud kinds of cloud computing.
-The amount of cloud computing services is increasing fast \cite{armbrust:2009}.
-It's now even possible to build your own small cloud using Raspberry Pi's \cite{southampton}.
-In this research there will be small scale cloud computing with the Raspberry Pi.
-The main motivation behind is is that it is ways to expensive to simulate large scale cloud computing.
-Another reason is the small location that is needed used with small scale cloud computing for Raspberry Pi's\cite{Pcextreme}.
-The Raspberry Pi is really small compared to a normal server \cite{cox:2014}.
-Because of this it could be better in executing small tasks.
-Small scale cloud computing is cloud computing with smaller computation amounts than normal \cite{cox:2014}.
-More motivation is that it does not use a lot and power.
-
-To understand what small scale cloud computing really is we will look more at the specific cloud service called Infrastructure as a Service:
-
-\section{Video streaming}
-There are a lot of cloud services nowadays. These include a webserver, a DNS server, a chat server, a mail server, a vpn server or a monitoring server or even a video streaming service. 
-Today a lot of people watch their movies online using video streaming.
-The netherlands have for example one million subscribers for Netflix \cite{volkskrant}.
-Netflix is a video streaming service that makes HD movies watching possible.
-For this Netflix makes use of a content distribution network (CDN).
-On the internet this is also known as a on demand service.
-They make use of amazon its AWS with a AWS cloud, Amazon simpleDB , S3 and cassandra for file storage \cite{Adhikari:2012}.
-Netflix makes use of MPEG-DASH a protocol that makes streaming over http possible.
-In this research I want to investigate more in the video streaming as a cloud service.
-To investigate this I want to make a experimentation cloud with Raspberry Pi's to see if it will work as a cloud. 
-Resources I could use for cloud video streaming:
-\cite{g-streamer,raspberry-video,video-1080p, plissonneau:2012}
-
-\section{Load balancing}
-In distributed servers it is very important that good load balancing takes place. For this reason I want to further investigate in what kind of load balancing techniques there are. 
-Resources I could use for load balancing:
-\cite{nginx-load-balancing,nginx-load-balancing-2,computer-networking,wolf:1997,load-balancing}
-
-\section{Raspberry pi}
-With this subquestion I want to find out if it is possible to let users have small Raspberry Pi servers I also want to know what the performance of this small Raspberry Pi cloud is. 
-Resources:
-\cite{Pcextreme,nginx-load-balancing,nginx-load-balancing-2}
-
-For this research I want to investigate if it is possible to do more research in the 
-load balancing techniques that can be used in a raspberry pi. A example of this would be the round robin protocol.
-Resources:
-\cite{nginx-load-balancing,nginx-load-balancing-2}
+The first two research questions describe the state of the art.
+The last three sub-questions go into the technical research that will investigate the performance and possibility of Raspberry Pi's for cloud video streaming.
+The five sub-questions are being looked at in the next sections.
+Followed by a final section for conclusions and identified areas for future work.
 
@@
 this is a method to solve field problems.
-This research will make use of the design Science method proposed by Hevner\cite{hevner:2007}.
+This research will make use of the Design Science method proposed by Hevner~\cite{hevner:2007}.
+This design method has three parts.
+\begin{figure}[H]
+	\centering 
+	\includegraphics[width=0.4\textwidth]{Design_science.png}
+	\caption{Design Science}
+	\label{fig:design} %always place your label after your caption!
+\end{figure}
+The \textbf{relevance cycle} is important, because you first have to identify the problems and opportunities.
+To identify these problems we will gave some more background information in the next section.
+The \textbf{design cycle} is where you actually build the design.
+This will be highlighted in the Setup \& Experiment section.
+The \textbf{rigor cycle} matters because it can give you two types of additional knowledge.
+It provides past knowledge to ensure its invention and it's there to guarantee that the new product is a research contribution.
+This will for example be taken into account in the Result section.
 
-\section{Research approach}
-For the experiment we need a Raspberry Pi with a static Ip address and we need a sd card for the OS.
-For the experiment we need a Raspberry Pi B that can make use of the Ethernet.
-This is because a Raspberry Pi can be used as a webserver and this is needed to have this in order to make video streaming possible.
-This webserver will make video streaming possible.
-It will have a VPN to make it possible to put video's on the Raspberry pi \cite{VPN:2014}.
-So I will first make this video streaming webserver. 
-After this we will make a cluster with one Raspberry Pi as a load balancer and the other two as a video stream pi.
-If I have made such I cluster I can start doing some tests on it.
-For example some test in streaming in different quality with load balancing.
-The setup of the raspberry Pi can be seen in the figure below ~\ref{fig:setup}.
+\todo{UML sequence diagram}
+
+\section{Background}
+\subsection{Small scale computing}
+Small scale cloud computing is cloud computing with smaller computation amounts than normal \cite{cox:2014}.
+Most users that operate in the cloud buy the services instead of buying the hardware and having to set up the servers themselves.
+This service is called Infrastructure as a Service.
+To this specific cloud service belongs the online storage of data.
+The Amazon Elastic Compute Cloud (Amazon EC2) is one of the most widely used infrastructure platforms that these clients use \cite{hofer:2011}.
+This elasticity of computing resources is very important \cite{Miettinen:2010:EEM:1863103.1863107}.
+A lot of companies have their own virtual machines running in large data centers \cite{beloglazov:2010}.
+The advantage is that these instances can be scaled dynamically to the customer it's need.
+Using these instances makes easier management of the computers and varying workloads possible.
+
+Several cloud services have a huge demand on the network. This high demand can sometimes make it possible that data centers are unreachable.
+That is a reason why many companies have their own data centers.
+These data centers are small and not energy efficient.
+Another reason why companies have their own data center is because they don't want their data to be in somebody else his hands.
+Netflix a cloud service is responsible for approximately 30\% of the peak downstream traffic in US \cite{Adhikari:2012, computer-networking}.
+To improve this there are several data patterns possible, it can for example make a huge different in sending data in small bursts or in one large burst.
+
+A CDN makes use of small data centers.
+This is because in a CDN you can get your data that is from America from a more nearby storage place.
+For example a website may be hosted in America.
+This website is connected to a CDN and in this way its possible to get your data from a more nearby server that has a copy of that website.
+For example if you live in Amsterdam you can perhaps get your data from London where the CDN is located instead of America.
+In this way the latency is decreased and there is a shorter connection distance and you have faster load times.
+
+Power Usage Efficiency (PUE) is nowadays becoming a more important aspect in cloud computing.
+Keeping the power usage low is one of the main challenges of cloud computing.
+The data centers now are only 12 till 20\% of the time operating, while all the servers inside are still using energy.
+Keeping these data centers up requires a lot of electrical power.
+Therefore we perhaps need to more Green Cloud Computing solutions that reduce the electrical power consumption and reduce the environmental impact of data centers~\cite{beloglazov2012energy}.
+For example with data centers that are using microservers.
+More information about this is in the next section.
+\newline
+With the increase of lightweight portable devices the energy efficiency becomes more important.
+For example can the data center do the graphic calculations needed to create a good video, however then more data needs to be send of the network.
+This will save energy, but will increase the data over the network.
+This means that a trade-off has to be made between local processing and computation offloading \cite{Miettinen:2010:EEM:1863103.1863107}.
+Computation offloading makes the data centers do the calculations, therefore making cloud computing more important.
+
+\subsection{Microserver}
+Microservers come to good use in small data centers \cite{microserver}.
+They are smaller in size, computer power and consume less electricity.
+This makes them perfect for high traffic usage tasks.
+Its cheaper to a small device than a big server inside a data center, so smaller microservers make a data center more dynamic.
+The ability to add and remove more easily microservers can save a lot of energy.
+It's also better for optimization.
+A micro server often has a different processor compared to a normal server.
+ARM is a processor a micro server might use.
+This processor does not have so much overhead compared to a Intel one.
+The Intel processor is better at complex tasks, while the Arm processor is better at small tasks \cite{microserver}.
+The difference in these processes is because of their design.
+The ARM has the possibility to optimize it for a special task.
+In the data center of the future more of these dedicated processors will be used.
+
+\subsection{Streaming}\label{sec:stream}
+Video streaming happens with TCP or HTTP.
+TCP sends frames to the client and in these frames is the video stored.
+Of course if the available TCP send rate is large enough then the video will play without any delays.
+But if the TCP send rate is less then needed then the video play will alternate between periods of continuous playout and periods of freezing~\cite{computer-networking}.
+Its very important that video freezing or audio playing faster then the video does not happen.
+This is why multimedia applications have high performance requirements.
+\begin{figure}[H]
+	\centering 
+	\includegraphics[width=0.4\textwidth]{VideoStreaming.jpg}
+	\caption{Raspberry Pi 2 model B}
+	\label{fig:stream} %always place your label after your caption!
+\end{figure}
+HTTP streaming is used for streaming a video.
+In HTTP streaming the HTTP GET request specifies the specific range of bytes the client wants to retrieve from the desired video~\cite{computer-networking}.
+In this way the client can correctly receive the video, if it receives too much data then its buffer for video playing can get full.
+To prevent throwing data away the server will then stop sending.
+To prevent throwing data away the client will have a not to large buffer.
+\newline
+There is a important streaming technique called adaptive streaming.
+This streaming algorithm is often used for video on demand (VOD).
+It improves the experience for the end-user by adapting the video quality dynamically to the viewers network condition \cite{ffmpeg}.
+This techniques looks to the clients CPU possibility and it's network possibilities.
+It delivers small sized chunks at multiple bitrates.
+This techniques is used for HTTP Live Streaming (HLS).
+This makes use of RTMP streaming and HTTP.
+This way of streaming is released in 2014.
+It codifies video in the H.264 format.\newline
+There is another special kind of HTTP streaming called DASH (Dynamic Adaptive Streaming over HTTP)~\cite{computer-networking}.
+In DASH the video is encoded into several different versions.
+If the bandwidth is high, then the client selects chunks from a high-rate version and the way around~\cite{computer-networking}.
+The possibility to switch between bit rate versions is in video streaming very important.
+To make a smooth transition between these versions possible there are intermediate versions so that the client will see less suddenly the change in video quality.
+In HTTP streaming the server stores the video with a different URL.
+
+\subsection{Video streaming and load balancing}
+For video streaming several load balancing techniques can be used.
+There are several choices that have to be made by choosing a load balancer for a service.
+These choices can for example be performance, reliability and features.
+There can be a non-uniform demand for different movies.
+One solution to overcome this problem would be to replicate the most popular movies.
+One obvious problem is then that it is expensive in terms of storage space required.
+To solve this you can use dynamic replication to solve the load demand~\cite{dan1996load}.
+By using this you move portions of a movie to less used storage devices.
+The allocation of these movies only happen when there is a to high increase on one specific storage device.
+In this way load imbalances can be prevented \cite{dan1996load}.
+\newline
+Load balancers are generally grouped in two layers.
+Layer 4 (FTP,IP, UDP, TCP )and layer 7 the application layer.
+Layer 7 load balancers distribute request based upon data in the application layer.
+Here below are some protocols and languages used for this:
+\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
+	\item HTTP, is the hypertext transfer protocol. In section \ref{sec:stream} are mentioned some usages of this protocol. A lot of video streaming services use HTTP streaming \cite{Adhikari:2012}.  
+	\item RTMP is a real time messaging protocol ~\cite{rtmp}.
+It is developed for streaming data between a player and a server.
+It is encapsulated in HTTP to traverse firewalls.
+It gives more video player options compared to normal HTTP thus giving the user a better experience.
+A disadvantage compared to normal HTTP is that it is sensitive for data spikes.
+These data spikes can result in a overload of the buffer which results in a empty buffer, this can lead to a stop in the video playing.
+	\item Synchronized Multimedia Integration Language (SMIL) describes multimedia presentations \cite{smil}.
+SMIL refers to media objects by URLs, allowing them to be shared between presentations and stored on different servers for load balancing.
+\end{enumerate}
+
+\subsection{Video streaming in a data center}
+
+Nowadays a lot of people watch their movies online using video streaming and this amount of people is increasing.
+The Netherlands have for example one million subscribers for Netflix \cite{volkskrant}.
+One thing that these users want is the on demand video streaming.
+They do not want to store the data itself and they want to have a wide choice of different videos.
+Netflix is a video streaming service that makes HD movies watching possible.
+This is known as a on demand service.
+For this Netflix makes use of a content distribution network (CDN).
+They make use of amazon its AWS, simpleDB , S3 and Cassandra for file storage \cite{Adhikari:2012}.
+Netflix makes use of MPEG-DASH a protocol that makes streaming over HTTP possible.
+To make this possible Netflix does several things in the cloud.
+
+ \begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
+ 	\item Content ingestion, this means that Netflix receives the studio master version of the movies and uploads these to the cloud. 
+ 	\item Content processing, this means that in the cloud many different formats are created for each movie.
+ 	\item Uploading different versions to the CDN,	this means that all the versions that have been made are distributed over the CDN.
+ \end{enumerate}
+Netflix ~\cite{Adhikari:2012}
+
+\subsubsection{Video stream CDN}
+Video streamer Netflix has  it's own CDN.
+This CDN is fully operational in 2015 and now they still use some other CDN's like Akamai.
+Reasons for having an own CDN is that the load balancing can be better improved.
+The CDN that Netflix has created is called Open Connect.
+To make their CDN possible they work together with the ISP providers.
+They use high performance HTTP delivery to get the content to the users.
+By having their own CDN they can get the video's faster to their users, because they can optimize their video stream algorithms for their own CDN.
+Besides this its possible that in this way the data going over the network can be decreased.
+
+\section{Related work}
+
+There have been several cloud projects with the Raspberry Pi. \newline
+One of these has been the supercomputer build by Southampton~\cite{cox:2014}.
+Here they build it with 64 raspberry Pi's .
+They used a Message Passing interface to communicate between the Raspberry Pi's.
+The research was done in order to see what the performance of a low-power high performance cluster is.
+\newline
+The project of the university of Glasgow~\cite{tso:2013}.
+This data center has 56 Raspberry Pi's.
+It is build for research and education purposes for a cloud data center.
+They have a Hadoop running on their servers.
+\newline
+There was another project called the Beowulf cluster~\cite{beowolf-setup}.
+This project was created for a PhD assignment.
+This cluster is build for collaboratively processing sensor data.
+A Beowulf cluster is simply a collection of identical, commodity computer hardware based systems~\cite{beowolf-setup}.
+The big advantage of the Raspberry Pi in this project was that it is cheap and it does not need a cluster administrator to watch over everything you do.
+
+For Video streaming there are several projects. These projects are often done by service providers such as Google with their video streamer Youtube. \newline
+NGINX is busy with their Video streaming project.
+NGINX works together with Netflix to give users the best video watching experience.
+NGINX is a scalable service with high performance load balancing.
+Netflix is together with NGINX busy with their project Open Connect.
+This project wants to improve the load balancing for video streaming over the whole network.
+\newline
+Another service is WOWZA \cite{wowza}.
+WOWZA provides video streaming for a lot of companies and universities.
+WOWZA has done several projects for video streaming and has build with the University of Maine a content management system for their online videos.
+One mayor video stream service is of course Youtube \cite{youtube}.
+Youtube was once started as a project with the aim to remove the technical barriers to share videos online.
+Nowadays Youtube is still working hard on optimizing their video streaming service.
+Youtube has a online API so developers can join in and start their own projects.
+Youtube has its own projects for example helping mobile gamers stream their video, helping with live streaming and many more.
+
+\section{System description}\label{sec:system}
 
@@
 	\centering 
-\includegraphics[width=0.4\textwidth]{raspberry pi setup.jpg}
-\caption{Insert caption to place below figure.}
+	\includegraphics[width=0.4\textwidth]{Pi2ModB1GB_-comp.jpeg}
+	\caption{Raspberry Pi 2 model B}
+	\label{fig:raspberry} %always place your label after your caption!
+\end{figure}
+\begin{table}[H]
+	\centering \caption{Specifications}
+	\begin{tabular}{|c|c|} \hline
+		Ethernet & 100 Mbps \\ \hline
+		USB & 4 x USB 2.0 \\ \hline
+		Video out & HDMI 1.4 \\ \hline
+		Audio & 2 x analog \\ \hline
+		CPU & 900MHz quad-core ARM Cortex-A7 \\ \hline
+		card slot & Micro SD  \\ \hline
+	\end{tabular}
+	\label{tab:Specificaties}
+\end{table}
+The Raspberry Pi 2 (RPi 2)only consumes 3 watts, because of this it doesn't need active cooling.
+The RPi 2 does have a limited ethernet cable of only 100 Mbps.
+This can be a huge drawback when large amounts of data need to be distributed over the Network.
+It is however very useful for a investigation in load balancing for video streaming.
+A small network cable offers still room for analyzing the video stream.
+The USB 2.0 has not a huge capabilities to share the data from a external harddisk to a user, but it will be enough for this small simulation.
+A normal Seagate harddisks demands 10 Watt when it is actively streaming videos and when it's standby it has a consumption of 0.1  Watt.
+
+This research makes use of three Raspberry Pi's one router and one switch.
+All these Pi's need power, therefore there is a power supply and 3 micro USB cables.
+There are three sd cards needed for the Operating System, and other software, to make the RPi 2 work.
+A cost structure for this can be found in the appendix section~\nameref{sec:cost}.
+
+For some benchmark test a laptop is plugged in, so that several tests can be done from the laptop.
+
+\section{Setup \& Experiment}
+
+\subsection{Experiment approach}
+This setup can be build by following the section \ref{sec:software} in the appendix.
+More details about the setup can be found in section \ref{sec:setup}.
+A RPi 2 is used for video streaming with load balancing.
+For the experiment Raspberry Pi's with a static ip address are needed.
+This so we can connect easily to them with SSH.
+For the experiment we need a Raspberry Pi 2 that can make use of the Ethernet.
+This is because a RPi 2 is used as a webserver to make video streaming possible.
+This webserver will make video streaming possible.
+It will have a VPN to make it possible to put video's on the RPi 2.
+After this a cluster with one RPi 2 as a load balancer and the other two as a video stream Pi will be build.
+If such a cluster is made tests can be done and improvements can be made.
+For example some test in streaming in different quality with load balancing.
+The setup of the Raspberry Pi 2:
+
+\begin{figure}[H]
+	\centering 
+	\includegraphics[width=0.5\textwidth]{raspsetup.jpg}
+	\caption{Raspberry Setup}
 	\label{fig:setup} %always place your label after your caption!
 \end{figure}
-For the load balancing we will make use of Nginx for this we will use the following sources:
-\cite{nginx-load-balancing, nginx-load-balancing-2}
+\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex] 
+\item The client who wants to get the video. 
+\item The router who redirects the client to the load balancer.
+The router will also have the video streamers in this network.
+If there are to much Raspberry Pi's in a network to connect to a single router a switch can be placed between them.
+\item The load balancer who redirects the client to the right video streamer.
+\item The video streamer who streams the video to the client.
+\item The video streamer who streams the video to the client.
+\end{enumerate}
+In the section \ref{sec:setup} the software is defined to create a cluster like this.
 
-\section{State of the Art}
-Today there are many cloud services. This amount of cloud computing services is increasing fast \cite{armbrust:2009}.  Despite the attention
-from the research community, research and development of
-Cloud Computing services is still in it's childhood\cite{tso:2013}.
-Today there is a lot of people that use video streaming and this will become even more.
-People want to have everything has to be accessible through the network around the clock \cite{youseff:2008}.
-One thing that people want on demand are there film series.
-Currently Netflix has 30\% of the downstream in the United States.
-This downstream is huge and that means that there is optimization in this branch possible.
-To make the video on demand service of Netflix possible they use servers from Amazon.
+\subsection{Raspberry Pi 2 inside a data center}
 
-In this paper there will be research done on making a load balancing service for the Raspberry Pi.
-This service will consist of several raspberry Pi's.
-These Raspberry Pi's make together a small cloud computer.
-The Raspberry Pi is made for research and education purposes \cite{raspberry-pi}.
-The Raspberry Pi is a cheap device costing around 35 euro.
-It has a power consumption of only three watt and has quite good processor.
-For this reason it might be very useful for small scale cloud computing.
-The raspberry Pi is a small device and is excellent for a lot of small devices in a relatively small place.
-The Raspberry Pi doesn't use cooling and it can be used for very rapid elasticity and on-demand self-service.
-Because of it's cooling features and low power consumption it might be a good alternative for the nowadays high power consuming data centers.
-The raspberry pi is really small so it is a lot easier to place extra pi in a data center compared to a normal server.
-The Raspberry Pi has one drawback and that is that the processing power is relatively low.
-By using load balancing there will be taken a look at what load balancing techniques are successful for the Raspberry pi.
+In the end it would be ideal if the RPi 2 will fit inside a data center.
+It is possible to fit a lot of Raspberry Pi's inside a data center.
+PCextreme has made it possible to fit 500 Pi's inside a single data rack \cite{Pcextreme}.
+For this special designed boards are needed.
+With a special board you can for example reboot them from a distance.
+\newline In this research we only have 8 Pi's and these fit easily inside the rack.
+The cooling of the data rack is more than sufficient to cool all these Raspberry's.
+The power consumption of the RPi 2 is low as you can see in table \ref{tab:cpu} below.
+The RPi 2 is also easy to replace inside a data center and it can easily be turned on and of, this makes it suitable inside a server rack.
+A problem that will exist with the Raspberry Pi 2 inside the data center is that every time a Pi's have troubles a help team inside the data center has to fix this for its customer.
+It is harder to get  a fully automated re-installation as for example a vServer more easily does.
 
-In this research we will make a small raspberry cloud to do research on video streaming using HTTP.
-This will be done using the design Science method proposed by Hevner\cite{hevner:2007}.
-After we have done this for the Raspberry Pi there will be looked at streaming using Amazon.
-In this way we can see how the results are compared to streaming via Amazon.
-This research will try to find out if the raspberry has enough processing power to stream to multiple web clients.
-The cloud performance can now be better researched, because everything is at one location and the information about what processes are running on the pi are well defined.
-In this way we can take a better look at algorithms used in video streaming.
-This is mostly because there is not a lot of overhead.
+The setup for this project looked like this:
+\begin{figure}[H]
+	\centering 
+	\includegraphics[width=0.50\textwidth]{setup.jpg}
+	\caption{Project Setup}
+	\label{fig:projectsetup} %always place your label after your caption!
+\end{figure}
+The figure \ref{fig:projectsetup} is photo of the project setup.
+This project setup is comparable with figure \ref{fig:setup}.
+The numbers in the front pint to the Raspberry Pi's that are also showed in figure \ref{fig:setup}.
+The number in the back shows the little router that is behind the power supply.
+In this picture there is a extra switch to connect all the Raspberry Pi's.
+To redo this experiment there are only three Raspberry Pi's necessary.
+\newline
+This setup can be placed inside of a data center.
+The switch and the router will then be removed and the rest will be fit nicely into the server rack.
+The setup that has been made now could easily fit on the project table, so that it was easy to reach them and a lot of research on them could be done.
 
-\section{Conclusion and future work}
+To verify that a Pi can operate inside a data center some tests have been done.
+For these tests a multimeter has been used.
+The Elro M990 multimeter has been used.
+The program sysbench has been used to run several CPU tests for the Raspberry Pi 2 its four cores.
+This is a benchmark test to get a quick impression about the performance of the system.
+The ampère and volt is measured with the multimeter during the test.
+the This gave the following results:
+\begin{table}[H]
+	\centering \caption{CPU test}
+	\begin{tabular}{|c|c|c|} \hline
+		Core & Ampère (A) & Volt\\ \hline
+		1 & 0.339 & 4.84 \\ \hline
+		2 & 0.365 & 4 \\ \hline
+		3 & 0.392 & 4 \\ \hline
+		4 & 0.443 & 4 \\ \hline
+	\end{tabular}
+	\label{tab:cpu}
+\end{table}
+
+The idle usage of the Raspberry Pi 2 is 0.312 Ampère and 4.86 Volt.
+In the table there is showed that with a benchmark test of only one core the Ampère going through the system is only 0.339, this means that it is barely increasing when using one core fully or idle.
+A normal server needs about 500 watt.
+Each Raspberry Pi has a consumption of about 3.5 watt, so about 500/3.5=140 Pi's will be possible instead of a single server.
+By using these small modular systems the power consumption inside a data center can be improved.
+
+\subsection{Raspberry Pi 2 setup}\label{sec:setup}
+In this setup we are going to make a Netflix kind of video stream service. \newline
+\textbf{Dietpi} is the software we use as operating system \cite{dietpi}.
+This is a diet version of Raspbian the normal Raspberry Pi operating service.
+The Raspbian again is a diet version of Linux.
+This makes that Dietpi only has the most necessary software to operate.
+In this way the memory usage for the operating system stays low.
+This low memory usage is important, because the creation of different video formats requires a lot of process power.
+For most systems you want as less unnecessary overhead as possible.
+\newline
+\textbf{NGINX}~\cite{nginx}: For the load balancing and streaming over HTTP NGINX will be used.
+A RTMP module from Arut for NGINX will be used to make a media streaming server over HTTP \cite{arut}.
+NGINX is optimized for ARM.
+This is a processor the Raspberry Pi 2 is using.
+One other reason to choose for NGINX and not for a apache webserver is that it uses less memory.
+NGINX has a more efficient model than apache, and because of this it can handle more HTTP requests.
+Besides this is for NGINX and Apache the most documentation available on how to do video streaming.
+\newline
+\textbf{FFmpeg} is a cross-platform solution to record, convert and stream audio and video \cite{ffmpeg}.
+Using this software makes adaptive streaming and streaming in different formats possible.
+\newline
+\textbf{JW Player}~\cite{jwplayer}: JW Player is a HTML5/flash embedded media player.
+It is a open source media player.
+Besides this also JW player can make it possible to do some load balancing dependable on the bit rate that is coming from the video.
+It supports dynamic streaming, dynamic streaming consists of multiple single streams with the same content, all in a different quality \cite{jwplayer}.
+from different streams.
+The Player uses server modules to stream the video to the client using the formats HTTP FLV or H264.\newline
+Cassandra is a database that helps replicating data across multiple data centers \cite{cassandra}.
+In the case of this project there are videos stored.
+This data can automatically be replicated across the nodes for fault-tolerance.
+In this way its possible to have the data still available when a node crashes.
+
+\subsection{Raspberry Pi 2  testing}
+
+In this testing section several test will be done these are: 
+\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex] 
+	\item CPU test
+	\item RTMP stream test
+	\item SMIL test
+	\item CPU test with stream
+	\item Cassandra test for file location
+\end{enumerate}
+
+The Raspberry Pi's are stress tested to make sure that they are operating in the right way. For this the program stress for Linux is used. 
+This application checks if the CPU is working correctly.
+
+To stress test and see if the server is streaming correctly we use Apache JMeter~\cite{jmeter}.
+This test with Apache JMeter is used to see how many streams a Raspberry Pi 2 can handle.
+This test is done with a laptop and RPi2.
+First a test case is created in Apache JMeter then a RTMP video stream is started and this is checked in a media player and a webpage in a webbrowser.
+The result is that the RPi 2 can handle a maximum of 25 users for streaming MP4 files at a user at the same time.
+Depending on what protocol is used the video can freeze, or the video will be displayed on a lower bit rate.
+If it goes to a lower bit rate it will try to switch back to a higher bitrate with higher quality video when this is possible.
+
+Streaming videos can be done by NGINX.
+To test if this is working properly we can test it with a media player like VLC or use a web browser were you can type in the RTMP stream coming from the RPi 2.
+Test the RTMP stream with different kind of MPEG-4 (MP4 ) files so you can see the quality difference.
+Test the RTMP stream by copying it in a media player.
+After that with the JW player support in the browser you can also test it inside your browser.
+The RTMP stream is streaming about 800 kbit/s for a small 300 MB movie.
+Theoretically this would mean that according to the formula max users=bandwidth/bit rate stream it will result in 118 users.
+This is with the Raspberry Pi 2 having a 100 Mbit connection.
+The RPi 2 has with the Iperf test a maximum connection of  94.4 Mbps~\cite{ipref}.
+With a USB 2.0 gigabit adapter this could increase in a 470 Mbit connection resulting in a increasing amount of users for each Raspberry Pi 2.
+
+Testing qualities with top command gives with a stream of a audio file of 7 min, 11 MB and in MP4 format a result of 10m resident size value. 
+With video streaming this gives a resident value of 14m for a file of 230 MB.
+These processes mostly done by FFmpeg and only a small part is done by NGINX.
+For Video on Demand most is done by NGINX and it was clearly visible that this kind of streaming is causing less freezing.
+This is because you can already start watching before the video is loaded.
+Video on demand (VOD)is better equipped to load the stream then only RTMP.
+With only RTMP it's only possible to watch what is at that moment being played like normal television.
+It also doesn't adjust the bit stream depending on the quality you need.
+Something VOD does.
+\newline
+Besides this some streaming with SMIL protocol has been done.
+This makes it possible to choose your own video streaming rate for the same file, for example 120p or 480p version of a movie.
+You now can choose the quality by yourself.
+This is something that Youtube does.
+There is also a possibility to switch the quality depending on the amount of data that can get over the network.
+During the test with 100 connections there was freezing when the users can set their own quality.
+When it is done automatically this was not the case.
+In apache JMeter it was also possible to see some latency when testing.
+For this testing videos of different qualities have been made.
+To make a video of 230 MB into the 3 different lower qualities it requires 200 \% of the CPU power.
+This is a lot of this has to be done for a lot of movies.
+So a server that needs to encode a lot of different videos might need a stronger processor.
+
+For the file location and database it would be nice to run the Cassandra data server.
+This data server is also used by Netflix to keep track of it's files.
+It turned out that it was possible to run Cassandra.
+cqlsh command it is possible to so that the cluster is running.
+
+\section{Result}
+
+For this project a good setup for video streaming has been built.
+This result has be made possible with NGINX and several other programs.
+The Raspberry Pi 2 has made load balancing possible with NGINX and JW Player.
+Besides that it is possible to stream video's over the HTTP with RTMP encapsulated to the user.
+NGINX has a efficient algorithm to transfer the HTTP with RTMP encapsulated data to the users.
+It has also a efficient algorithm to do normal load balancing.
+\newline
+The Raspberry Pi 2 can make videos of different qualities with FFmpeg and it is perfectly capable of distributing these videos of the other Pi's.
+FFmpeg has a huge demand of the processor power and this can be a problem when a lot of videos have to be encoded.
+The RPi 2 has a slow internet connection and this means that it streaming capacity is rather limited.
+The maximum RTMP stream output for my RPi 2 was for one around 800 kb/s.
+This can be different for the size and duration of your MP4 stream or FLV.
+The video streaming with Video on Demand or adaptive streaming has a good performance.
+It is only limited to around 100 users.
+The RPi 2 has a rather limited connection, this makes video streaming with the RPi 2 still not to useful.
+However this experiment shows that the RPi 2 is capable of video streaming.
+In the future the Raspberry Pi 2 can be better than a normal server, because its more dedicated ARM processor.
+
+In the table \ref{tab:Specificaties} its stated that the Raspberry only has 100 Mbps.
+Video streaming Its limited ethernet connection is a problem when it comes to video streaming.
+However with a larger Ethernet cable and a fast connection to a harddisk it would be much better for video streaming then the traditional video streaming from bigger servers.
+
+\section{Discussion \& Conclusion}
+Small scale data centers are important for the data transfer over the internet.
+It can avoid internet bottlenecks.
+Besides that are the smaller cloud computers often better in executing small tasks instead of the bigger ones.
+In an ideal case you want to have elasticity over the network.
+In this way you can increase and decrease the computation of a data center nearby the user, so that data doesn't have to travel so far.For video streaming you want the data as near to the user as possible in order to get him the best quality at the right speed, so that the video doesn't freeze.
+For video streaming the client needs to buffer a part of the movie.
+If the server is nearby then it's more easy to adjust the settings of these buffer.
+\newline
+The Raspberry Pi 2 can be useful for video streaming.
+It can definitely be used for further research into video streaming algorithms.
+This can be algorithms such as video distribution algorithms.
+The Raspberry Pi 2 is a microserver and has a processor for small tasks which is video streaming.
+The Raspberry Pi 2 does have some drawbacks for video streaming, but is perfect for education purposes.
+\newline
+It is possible to fit 500 Raspberry Pi's inside a single server rack. \newline
+For the setup a diet version of the Raspbian operating system is used called Dietpi. Besides this it makes use of NGINX for the server with a streaming module for video. \newline
+In the research several load balancing techniques were used.
+Cassandra is used in this research to distribute and locate the videos over different Raspberry Pi's.
+Adaptive streaming is used for Video on demand and normal RTMP streaming is used to setup streams.
+Improvements on those load balancing techniques were not possible in the scope of this research, but might be possible in future research.
+\todo{any last words	}
+
+\section{Future work}
+New possibilities with faster USB and Ethernet cable.
+It is possible to create a gigabit connection over USB 2.0.
+This will make better video streaming possible and more users can be reached over the HTTP.
+Work together with streaming services such as NGINX to further develop video streaming services hosted by ARM processors.
+In the future it would also be possible to run a Cassandra service for the Raspberry Pi 2 this will make the file location of video's possible in a cluster.
+Netflix is currently looking for a specialist in  Peer-to-Peer distribution for their videos \cite{netflix}.
+Peer-to-Peer distribution can be interesting with Raspberry Pi.
+Besides this it might be interesting to look into Peer-to-Peer distribution in general and for video streaming in specific, there can be taken a look into the technology and legal aspect of  Peer-to-Peer distribution.
 
 \section{Acknowledgments}
-
+This paper would not have been possible without the help of Björn Postema and Nick Shot.
+\clearpage
 \bibliographystyle{abbrv}
@@
 \vspace{50 mm}
-\newpage
+
 %APPENDICES are optional
 
+\clearpage
+\appendix
+
+\section{Cost structure}\label{sec:cost}
+\begin{figure}[H]
+	\includegraphics[scale=0.65]{Kostenoverzicht_cluster.pdf}
+	\label{fig:cost}
+	\caption{Cost structure}
+\end{figure}
+
+\section{Software configuration}\label{sec:software}
+
+\subsection{Raspberry Pi 2}
+
+\subsubsection{GitHub}
+For more information about the project its possible to see the GitHub repository. Comments or questions about the code can also be asked there. \newline
+The link is: \newline
+\url{https://github.com/PaulVelthuis93/VideoStreaming}
+
 \end{document}

### 2015-05-26 research_proposal/research proposal.tex
new version

@@
 \usepackage{subcaption}
-\usepackage{hyperref}
+\usepackage[breaklinks]{hyperref}
 \usepackage{tabularx}
 \usepackage{graphicx}
+\usepackage{url}
+\usepackage{pdfpages}
+
+%% Define a new 'leo' style for the package that will use a smaller font.
+\makeatletter
+\def\url@leostyle{%
+	\@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\ttfamily}}}
+\makeatother
+%% Now actually use the newly defined style.
+\urlstyle{leo}
+
 \restylefloat{figure}
@@
 
-\title{Small Data Center using Raspberry Pi for Video Streaming}
+\title{Micro Data Center using Raspberry Pi for Video Streaming}
 % In Bachelor Referaat at University of Twente the use of a subtitle is discouraged.
@@
        \affaddr{University of Twente}\\
-       \affaddr{P.O. Box 217, 7500AE Enschede}\\
+       \affaddr{P.O. Box 217, 7500 AE Enschede}\\
        \affaddr{The Netherlands}\\
@@
 \begin{abstract}
-This document describes a research proposal in the
-area of cloud computing services.
-Cloud computing is a trend IT that customers move computing and data away from desktop and portable PCs into large data centers.
+This document describes a research proposal in the area of cloud computing.
+Cloud computing is a trend IT that customers move computing power and data away from desktop and portable PCs into data centers.
 These data centers require a lot of power and cooling.
 Nowadays 30 \% of the data coming from these data centers is video streaming.
-The Raspberry Pi is a not so costly device that can do research in Video streaming.
-The main research question is therefore: How well does the Raspberry Pi perform in small scale data centers with video streaming?
-To answer this question a micro Raspberry Pi video streaming service will be build.
+The Raspberry Pi is a low cost device that can be used in a cloud for video streaming.
+The Raspberry Pi might be useful for video streaming, because of the cooling and space it needs.
+The main research question is therefore: How well does the Raspberry Pi perform in micro scale data centers with video streaming?
+To answer this question there will be a investigation on how video streaming in data centers work.
+After that a design research in how to fit such a Raspberry Pi in a data center will be done.
+To make the video stream cloud work there is a investigation in the software.
+To conclude there will be taken a  look in the different load balancing techniques to see if improvements in this area are possible.
 \end{abstract}
 
-\keywords{Cloud computing, Raspberry Pi, micro data server, video streaming, load balancing}
+\keywords{Cloud computing, Raspberry Pi, micro data center, video streaming, load balancing}
 
 \section{Motivation}
-Today most of us have some data in the cloud. But despite the attention from the community, research and development of Cloud Computing services are still in its early days~\cite{tso:2013}. \newline
-Cloud computing is a trend IT that moves customers  computing and data away from desktop and portable PCs into large data centers \cite{dikaiakos:2009}.
+Today most of us have some data in the cloud. But despite the attention from the community, research and development of Cloud Computing is still in its early days~\cite{tso:2013}. \newline
+Cloud computing is  the trend that IT moves data away from desktop and portable PCs into large data centers \cite{dikaiakos:2009}.
 In the future most internet users will access internet services over lightweight portable devices requiring a lot of data bandwidth \cite{dikaiakos:2009}.
-Video streaming for example requires a lot of bandwidth \cite{Adhikari:2012}.
-This bandwidth usage causes bottlenecks.
+These huge amount of data going over the network usage cause bottlenecks.
 To prevent these bottlenecks we build data centers around the globe.
-On these data servers a lot of improvements can be made.
-\todo{bron zoeken}
+On these data servers a lot of improvements can be made \cite{bennett2007netflix,abrahamsson:2013,beloglazov:2010}.
+These data servers for example require a lot of space and cooling.
+There are now new technologies such as the powerful ARM processor.
+Many companies want to explore the possibilities of for example the Raspberry Pi, because of its ARM processor and the price \cite{Pcextreme}.
+Some data centers already offer some cloud computing using the Raspberry Pi.
 \newline
-In this research a small data server consisting of Raspberry Pi´s will be investigated.
-A reason for this is that data centers require a lot of space and cooling.
-There are now new technologies such as for example the powerful ARM processor.
-Many companies want to explore the possibilities of for example the Raspberry Pi, this because of it's powerful processor compared to the price \cite{Pcextreme}.
-Some data centers already offer some cloud computing using the Raspberry Pi.
-Another reason for this is the small location that the Raspberry Pi needs, and the low power usage of a Raspberry Pi \cite{hosting,Pcextreme}.
-A Raspberry Pi has a power usage between the 3-5 Watt.
-A normal server has a power usage between the 75 and 250 Watt~\cite{Powerusage,beloglazov2012energy}.
-However the Raspberry Pi has less computing power then a normal server.
-The low power consumption and its computing power could mean that it is better to use a Raspberry Pi for specific small tasks that do not demand an entire.
-During this research there will be a investigation on the performance of the Raspberry Pi as a small data server.
+A Raspberry Pi has a power usage between the 3-5 Watt and is a micro computer.
+A normal server has a power usage between the 75 and 250 watt~\cite{Powerusage,beloglazov2012energy}.
+The low power consumption and its computing power could mean that it is better to use a Raspberry Pi for specific small tasks that do not demand an entire server.
+For this reason research will be done on the performance of the Raspberry Pi as a micro data center.
 \newline
-A Raspberry Pi can be the small data center for the future \cite{tso:2013}.
-The Raspberry is a less costly device and is sold for 40 euro.
-This makes it cheaper to do research in compared to a normal server.
-Building a cloud like this can be a cost effective scale model\cite{tso:2013}.
+A Raspberry Pi cloud can be the micro data center for the future \cite{tso:2013}.
+The Raspberry is a low cost device and is sold for 40 euro.
+This lowers the cost for experimental research compared to a normal server.
+Building a cloud like this can be a cost effective scale model \cite{tso:2013}.
 It's a ideal testbed for testing distributed software.
 
-\section{Specific problem}
+\section{Problem Statement}
 
@@
 For this Netflix makes use of a content distribution network (CDN).
-On the internet this is known as a on demand service \cite{Adhikari:2012}.
+On the internet this is known as an on demand service \cite{Adhikari:2012}.
 Netflix makes use of MPEG-DASH a protocol that makes streaming over HTTP possible \cite{martin:2013}.
-The problem is that Netflix is responsible for  29.7\% of the peak downstream traffic in US \cite{Adhikari:2012}.
+The problem is that Netflix is responsible for  29.7\% of the peak downstream traffic in US \cite{Adhikari:2012, computer-networking}.
 Because of this downstream the two main providers Comcast and  AT\&T were limiting the downstream of Netflix.
@@
 \newline
-In the Netherlands more and more users are making use of video streaming as Youtube and Netflix.
-The downstreaming problems and the more users making use of streaming make it interesting to do more research in video streaming by cloud computers.
-Most of the research nowadays happen on expensive large servers \cite{tso:2013}.
-For this it can be very useful to see if it is possible to do research on a small computer like a Raspberry Pi.
-The problem is that we do not know if video streaming on a small Raspberry Pi cluster is possible.
+In the Netherlands an increasing number of users are making use of video streaming as Youtube and Netflix.
+The data streaming problems and the increasing amount of data that is going over the internet make it interesting to do more research in data centers with video streaming.
+Most of the research nowadays happens on expensive large servers \cite{tso:2013}.
+For this it can be very useful to see if it is possible to do research on a micro computer like a Raspberry Pi.
+The problem is that we do not know if video streaming in a cloud consisting of Raspberry Pi's is possible.
 
@@
 \begin{center} 
-How well does the Raspberry Pi perform in small scale data centers with video streaming? 
+How well does the Raspberry Pi perform in micro scale data centers with video streaming? 
 \end{center}
-This research will be part literature study and a part of it will be building a small Raspberry Pi cloud to measure the availability of the video streaming.
+This research will be part literature study and a part of it will be a design study for a small Raspberry Pi cloud to measure the availability of the video streaming.
 Here below there are several questions to come to a good answer for the main research question.
 
-\subsection{What are small scale data centers with video streaming and why are they used?}
-In this research there will be a small scale cloud data center with the Raspberry Pi.
+\subsection{What are micro scale data centers with video streaming and why are they used?}
+In this research there will be a micro scale cloud data center with the Raspberry Pi.
 The main motivation behind this is that it is ways to expensive to do it on multiple large servers.
@@
 \cite{southampton, Powerusage, cox:2014} \newline
-Another reason is that little space is needed using a small scall data center. On the size of the data center is currently done a lot of research \cite{Pcextreme}. \newline
+Another reason is that little space is needed using a micro scale data center. On the size of the data center is currently done a lot of research \cite{Pcextreme}. \newline
 Small scale cloud computing is cloud computing with smaller computation amounts than normal.
@@
 More motivation is that it does not use a lot cooling and power \cite{tso:2013}.
-Resources available for small scale cloud computing:
+Resources available for micro scale cloud computing:
 \cite{Pcextreme,armbrust:2009,richardson:2012,abrahamsson:2013,southampton, tso:2013, beloglazov:2010, qian:2009, hofer:2011, drago2012inside, dropbox, owncloud, Miettinen:2010:EEM:1863103.1863107, beloglazov2012energy,cox:2014}
 
-\subsection{Is the Raspberry Pi’s usable for video streaming?}
+\subsection{Is the Raspberry Pi feasible for video streaming?}
 The Netherlands have one million subscribers for Netflix \cite{volkskrant}.
 Netflix is a video streaming service that makes HD movies watching possible.
-This requires a lot of internet bandwidth and it could be useful to do the streaming in small scale data centers nearby.
-To investigate how video streaming at Netflix really works there are the following resources:
+This requires a lot of internet bandwidth and it could be useful to do the streaming in micro scale data centers nearby.
+To investigate how video streaming at big companies like Netflix really  work there are the following resources:
 \cite{volkskrant, Adhikari:2012} \newline
-Netflix makes use of MPEG-DASH a protocol that makes streaming over HTTP possible.
 In this research there will be an investigation in the video streaming as a cloud service for a Raspberry Pi.
-To investigate what that is there are the following resources:
+There will be an investigation in if it is feasible to use the Raspberry Pi for video streaming.
+For this investigation the following resources will be used:
 \cite{raspberry-video,video-1080p, plissonneau:2012, computer-networking}
@@
 For this power, cooling and location will be taken into account.
+We will provide a design with analysis to see if our setup is good.
 With this an advise can be made about how to fit the Raspberry Pi into the data center.
+
 \subsection{What setup does a Raspberry Pi cloud with video streaming require?}
@@
 \cite{abrahamsson:2013,southampton, tso:2013, beloglazov:2010,cox:2014} \newline
- There will be taken a look into the different software that has to be used. For example: 
+There will be taken a look into the different software that have to be used for a video streaming cloud consisting of Raspberry Pi's.
+To determine what software setup is needed the following resources will be used:
 \cite{raspberry-video,video-1080p, permission, nmon,bandwidth,ab, mosberger1998httperf, httperf-2, raspbian}
 
-\subsection{How is availability in a Raspberry pi cluster with video streaming affected by various load balancing techniques?}
-With this subquestion we will look into the different load balancing techniques.
-In a video streaming service it's very important to have high performance and availability.
-That's why it's interesting to do more research on this.
-Resources for load balancing on Raspberry Pi:
+\subsection{How is availability in a Raspberry Pi cluster with video streaming affected by various load balancing techniques?}
+In a video streaming service it's very important to have high  availability of the video and a high bandwidth usage.
+For this different load balancing techniques can be used.
+Information for load balancing on the Raspberry Pi:
 \cite{nginx-load-balancing,nginx-load-balancing-2, nginx-load-balancing-3, Raspberry-media-server, dropbox-clone} \newline
-Things that are interesting to look into are for example bandwidth usage, power usage, i/o throughput. For this the following resources will be used: 
+Specific performance parts are very interesting to look into more deeply, for example bandwidth usage, power usage, I/O throughput.
+These three parts are important in video streaming.
+To gain more information about the performance of these aspects on the Raspberry Pi following resources will be used:
 \cite{nmon,bandwidth,ab}
+
+\todo{ MPEG codex look into}
 
@@
 This research will investigate a cloud computer consisting of Raspberry Pi's.
-The research method for this would be the Design Science research method.
-this is a method to solve field problems.
-This research will make use of the design Science method proposed by Hevner~\cite{hevner:2007}.
+The research method that will be used is the Design Science research method.
+This is a set of analytical techniques and perspectives for performing research in Information systems like the Raspberry Pi.
+This research method is proposed by Hevner~\cite{hevner:2007}.
 \begin{figure}[H]
@@
 \end{figure}
-For this design research the research will specify the requirements, existing solutions, new solutions and the result of this new solution. After that a conclusion will be given.
+In the research requirements will be specified.
+These requirements will be gathered from existing solutions.
+In the research new solutions combined with existing solutions and the result of this new solution will be given.
+After that a conclusion will follow.
 
@@
 \end{table}
-For the experiment we need a Raspberry Pi B or Raspberry Pi 2 that can make use of the Ethernet.
-This is because a Raspberry Pi can be used as a webserver and this is needed to have this in order to make video streaming possible.
-This webserver will make video streaming possible.
+For the experiment we need a Raspberry Pi 2 that can make use of the Ethernet.
+This is because a Raspberry Pi can be used as a webserver and this is needed in order to make video streaming possible.
 Beside the Raspberry Pi a several other things will be needed.
-For this we have a cost structure:
-\begin{table}[H]
-	\centering 
-	\caption{Cost summary \cite{iapc}}
-	\begin{tabular}{|c|c|c|c|c|p{5cm}} \hline
-		Device 			& cost piece	& use 			& amount & total cost \\ \hline
-		Raspberry Pi 2 	& 32,60 		& cloud cluster & 8 & 316  \\ \hline
-		UTP cable		& 1,10 			& data cable 	& 8 & 8,80  \\ \hline
-		Micro usb cable	& 1 			& charging 		& 8 & 8  \\ \hline
-		switch 			& 40 			& internet 		& 1 & 40  \\ \hline
-		micro SD 		& 				& 				& 	& \\ \hline
-		& & & &  372,80  \\ \hline
-	\end{tabular}
-	\label{tab:cost}
-\end{table}
-
-So first he video streaming webserver will be made. 
-After this we will make a cluster with one Raspberry Pi as a load balancer and the other two as a video stream pi.
-The university of Southampton has made a cluster possible \cite{southampton}.
-So I think it is also possible for video streaming.
-With this there several performance tests can be done.
+For this we have a cost structure.
+You can view the cost structure in the appendix.
+\newline
+So first the video streaming webserver will be made. 
+After this we will make a cluster with one Raspberry Pi as a load balancer and the others as a video stream pi.
+For the video streaming performance several tests can be done.
 For example some test in streaming in different quality with load balancing.
-The setup of the Raspberry Pi can be seen in the figure below ~\ref{fig:setup}.
 
@@
 \end{figure}
+The setup of the Raspberry Pi can be seen in the figure above ~\ref{fig:setup}.
 
@@
 		16 & 1 April &  \textbf{Accept Reject proposal} \\ \hline
-		14-15& 30 March& Start building test environment \\ \hline
-		17& 6 April & Answer subquestion 1  \\ \hline
-		18& 13 April & Answer subquestion 2\\ \hline
-		19& 21 April & Answer subquestion 3\\ \hline
-		16-18 & 6 April  & working on test environment \\ \hline
-		20& 1 May  & Answer subquestion 4 \\ \hline
-		21& 4 May & conclusion and check coherency \\ \hline
-		21-22& 11 May & Finalize paper \\ \hline
+		April May& 6 March& Building test environment \\ \hline
+		16& 12 April & Answer subquestion 1  \\ \hline
+		17& 21 April & Answer subquestion 2\\ \hline
+		18& 27 April & Answer subquestion 3\\ \hline		
+		20& 11 May  & Answer subquestion 4 \\ \hline
+		21& 18 May & conclusion and check coherency \\ \hline
+		21-22& 18 May & Finalize paper \\ \hline
 		22& 1 June &  \textbf{Deadline paper} \\ \hline
 		23& 8 June & Peer review \\ \hline
-		24-25& 15 june & presentation preperation \\ \hline
+		24-25& 15 June & presentation preparation \\ \hline
 		26 & 22 June & \textbf{Conference} \\ \hline
@@
 After that there is time to write the conclusion and answer the main question.
-Then there is still some time left to finalize the paper.
+Then there is still some time left to finalize the paper and make the presentation.
 
 \section{State of the Art}
-The amount of cloud computing services is increasing fast \cite{armbrust:2009}. Despite the attention
+Today most of us have some data in the cloud. But Despite the attention
 from the research community, research and development of
-Cloud Computing services is still in it's early days~\cite{tso:2013}.
-Today there is a lot of customers that use video streaming and this will become even more.
+Cloud Computing services is still in it's early days~\cite{tso:2013}.Cloud computing is  the trend that IT moves data away from desktop and portable PCs into large data centers \cite{dikaiakos:2009}.
 Customers want to have everything has to be accessible through the network around the clock \cite{youseff:2008}.
 One thing that people want on demand are there film series.
-Currently Netflix has 30\% of the downstream in the United States~\cite{computer-networking}.
-This downstream is huge and that means that there is optimization in this branch possible.
-To make the video on demand service of Netflix possible they use servers from Amazon.
+Currently Netflix has 30\% of the data downstream in the United States~\cite{computer-networking}.
+This data downstream is high.
+To make the video on demand service like Netflix possible they use servers.
+On these data servers a lot of improvements can be made \cite{bennett2007netflix,abrahamsson:2013,beloglazov:2010}.
 
 The Raspberry Pi is made for research and education purposes \cite{raspberry-pi}.
-The Raspberry Pi is a not so costly device costing around 40 euro.
-It has a power consumption of only three watt and has for the price a processor that is extremely well equipped to execute small tasks.
-For this reason it might be very useful for small scale cloud computing.
+The Raspberry Pi is a low cost device costing around 40 euro.
+It has a power consumption of only three watt and has for the price a processor that is well equipped to execute small tasks.
 The Raspberry Pi is a small device and is excellent for a lot of small devices in a relatively small place.
 The Raspberry Pi doesn't use cooling and it can be used for very rapid elasticity and on-demand self-service.
-Because of it's cooling features and low power consumption it might be a good alternative for the nowadays high power consuming data centers.
-The Raspberry Pi is really small so it is a lot easier to place extra pi in a data center compared to a normal server.
-The Raspberry Pi has one drawback and that is that the processing power is relatively low.
-By using load balancing there will be taken a look at what load balancing techniques are successful for the Raspberry pi.
+Because of it's cooling features and low power consumption compared to a normal server it might be a good alternative for the nowadays high power consuming data centers.
+The Raspberry Pi is really small so it seems to be a lot easier to place extra Pi in a data center.
 
@@
 This will be done using the design Science method proposed by Hevner~\cite{hevner:2007}.
-This research will try to find out if the Raspberry Pi has enough processing power and bandwidth to be a suitable streamer to multiple web clients.
-The cloud performance can now be better researched, because everything is at one location and the information about what processes are running on the pi are well defined.
-In this way we can take a better look at algorithms used in video streaming.
-This is mostly because there is not a lot of overhead.
+This research will try to find out if the Raspberry Pi performs good enough to serve as a micro cloud to be a suitable streamer to multiple web clients.
+The load balancing techniques that can be used for this will also be researched.
+The research on this cloud can help the scientific world.
+This because everything will be at one place which is in many cloud projects not the case.
+Besides that the information about what processes are running on the Raspberry Pi are well defined.
+In this way we can take a better look at algorithms used in video streaming and cloud performance.
 
@@
 %APPENDICES are optional
-
+\appendix
+\section{Cost structure}
+\begin{figure}[H]
+\includegraphics[scale=0.65]{Kostenoverzicht_cluster.pdf}
+\label{fig:cost}
+\caption{Cost structure}
+\end{figure}
 \end{document}

### 2015-05-27 paper/paper.tex
changes

@@
 	\item RTMP stream test
+	\item Video on demand test
 	\item SMIL test
-	\item CPU test with stream
 	\item Cassandra test for file location
@@
 
-The Raspberry Pi's are stress tested to make sure that they are operating in the right way. For this the program stress for Linux is used. 
-This application checks if the CPU is working correctly.
+\subsubsection{CPU test}
+
+The Raspberry Pi's are stress tested to make sure that they are operating correctly.
+For this the program stress for Linux is used to monitor its health.
+All eight Raspberry Pi 2 have been tested using this program and they were working correctly.
+
+Another test is done with FFmpeg.
+FFmpeg needs a lot of CPU power to create new videos in different formats.
+To test this the top command of Linux was used.
+This measures the processor activity in real time.
+In this test a 230 MB 720p MPEG-4 (MP4 ) video has been made into three different lower qualities videos, it required 200 \% of the CPU power.
+The output is a 120p, 240p and 480p video file.
+At 200 \% CPU 2 cores has to be used out of the four to produce the video, this would result in the fact that the Raspberry Pi can only process two videos into different formats at the same time.
+When you have streamers that have only limited data available they will not have all the different formats.
+These streamers need to quickly produce these videos to different formats and this can lead till difficulties.
+\newline
+If the videos are streamed by using NGINX they use not so much processor power.
+The CPU power that is needed for a single stream is about 2 \% and this barely increases when more clients are listening to it.
+This test is done by using web browsers and the Linux top command.
+
+\subsubsection{RTMP stream test}
 
@@
 This test with Apache JMeter is used to see how many streams a Raspberry Pi 2 can handle.
-This test is done with a laptop and RPi2.
-First a test case is created in Apache JMeter then a RTMP video stream is started and this is checked in a media player and a webpage in a webbrowser.
-The result is that the RPi 2 can handle a maximum of 25 users for streaming MP4 files at a user at the same time.
-Depending on what protocol is used the video can freeze, or the video will be displayed on a lower bit rate.
-If it goes to a lower bit rate it will try to switch back to a higher bitrate with higher quality video when this is possible.
-
-Streaming videos can be done by NGINX.
-To test if this is working properly we can test it with a media player like VLC or use a web browser were you can type in the RTMP stream coming from the RPi 2.
-Test the RTMP stream with different kind of MPEG-4 (MP4 ) files so you can see the quality difference.
-Test the RTMP stream by copying it in a media player.
-After that with the JW player support in the browser you can also test it inside your browser.
+This test is done with a laptop and RPi 2.
+First a test case is created in Apache JMeter then a RTMP video stream is started and this is checked in a media player and a web page in a web browser.
+The result of this test is that it can handle 25 users for streaming MPEG-4 (MP4 ) files at a user at the same time.
+If there are more users used the video might freeze.
+This can result in a bad experience for the user watching the video.
+The RTMP stream will stream the video only in 720p format.
+Another test is by opening a media player like VLC were you can type in the RTMP stream address coming from the RPi 2.
+If the RTMP stream with the 230 MB video of 49 minutes is opened you can see that the video freezes some times do to buffering problems.
+\newline
 The RTMP stream is streaming about 800 kbit/s for a small 300 MB movie.
@@
 With a USB 2.0 gigabit adapter this could increase in a 470 Mbit connection resulting in a increasing amount of users for each Raspberry Pi 2.
+\newline
+If then a different stream is created with for example a audio file of 9 minutes there is no freezing with the VLC player.
+To test it in the browser a JW player is embedded inside the web page.
+This browser stream can be maxed with the 118 users that are theoretically possible with the 800 kbit/s stream of the small movie.
 
-Testing qualities with top command gives with a stream of a audio file of 7 min, 11 MB and in MP4 format a result of 10m resident size value. 
-With video streaming this gives a resident value of 14m for a file of 230 MB.
-These processes mostly done by FFmpeg and only a small part is done by NGINX.
+\subsubsection{Video on demand test}
+For the video on demand test a RTMP stream with FFmpeg has been created and NGINX was started to share the video. 
 For Video on Demand most is done by NGINX and it was clearly visible that this kind of streaming is causing less freezing.
@@
 Something VOD does.
-\newline
-Besides this some streaming with SMIL protocol has been done.
+
+\subsubsection{SMIL test}
+Streaming with SMIL protocol has been done.
 This makes it possible to choose your own video streaming rate for the same file, for example 120p or 480p version of a movie.
@@
 For this testing videos of different qualities have been made.
-To make a video of 230 MB into the 3 different lower qualities it requires 200 \% of the CPU power.
-This is a lot of this has to be done for a lot of movies.
-So a server that needs to encode a lot of different videos might need a stronger processor.
 
+\subsubsection{Cassandra test}
 For the file location and database it would be nice to run the Cassandra data server.
@@
 The link is: \newline
-\url{https://github.com/PaulVelthuis93/VideoStreaming}
+\url{https://github.com/PaulVelthuis93/bachelorreferaat}
 

### 2015-05-29 paper/paper.tex
changes

@@
 \usepackage{tabularx}
-
+\usepackage[numbers]{natbib}
+\setlength{\bibsep}{0.0pt}
 \newcommand\todo[1]{
@@
 \section{Introduction}
-Today most of us have some data in the cloud. But despite the attention from the community, research and development of Cloud Computing services are still in its early days~\cite{tso:2013}. \newline
-Cloud computing is a trend in IT that moves customers computing and data away from desktop and portable PCs into large data centers \cite{dikaiakos:2009}.
+Today most of us have some data in the cloud. But despite the attention from the community, research and development of Cloud Computing services are still in its early days~\citep{tso:2013}. \newline
+Cloud computing is a trend in IT that moves customers computing and data away from desktop and portable PCs into large data centers \citep{dikaiakos:2009}.
 In the future most internet users are expected to access internet services over lightweight portable devices requiring a lot of data bandwidth \cite{dikaiakos:2009}.
@@
 The low power consumption and its computing power could mean that it is better to use a Raspberry Pi 2 for specific small tasks that do not demand an entire server.
-For this reason research will be done on the performance of the Raspberry Pi 2 as a small data center.
+For this reason research is done on the performance of the Raspberry Pi 2 in a small data center.
 \newline
@@
 
-In this paper there will be an investigation in how useful the Raspberry Pi 2 is in a data center with video streaming.
-To come to an answer there will be taken a look into the performance of the Raspberry Pi 2.
-For this the main research question will be:
+In this paper there is an investigation in how useful the Raspberry Pi 2 is in a data center with video streaming.
+To come to an answer the performance of the Raspberry Pi 2 is evaluated.
+For this the main research question is:
 \begin{center}
@@
 
-In order to come to a good answer we need to  research several things.
-Therefore some sub-questions will be researched.
-These sub-questions will altogether provide a answer to the main research question.
+In order to come to a answer for the main question several sub-questions are researched. These sub-questions will altogether provide a answer to the main research question.
 
@@
 The first two research questions describe the state of the art.
-The last three sub-questions go into the technical research that will investigate the performance and possibility of Raspberry Pi's for cloud video streaming.
+The last three sub-questions go into the technical research that investigates the performance and possibility of Raspberry Pi's for cloud video streaming.
 The five sub-questions are being looked at in the next sections.
@@
 This is why multimedia applications have high performance requirements.
+To make the video streaming possible the client will connect with video streaming service its load balancer.
+The load balancer will then point were which videos are stored.
+Here below is in a UML sequence diagram the flow displayed between the client and the video service.
 \begin{figure}[H]
@@
 	\includegraphics[width=0.4\textwidth]{VideoStreaming.jpg}
-	\caption{Raspberry Pi 2 model B}
+	\caption{Video stream}
 	\label{fig:stream} %always place your label after your caption!
 \end{figure}
-HTTP streaming is used for streaming a video.
-In HTTP streaming the HTTP GET request specifies the specific range of bytes the client wants to retrieve from the desired video~\cite{computer-networking}.
-In this way the client can correctly receive the video, if it receives too much data then its buffer for video playing can get full.
+
+As visible in the diagram you can see that there is a loop for the streaming.
+In this loop the client will keep requesting for more parts of the videos.
+Depending on the algorithm being used the amount of data requested by the client can fluctuate.
+For streaming a video HTTP streaming is often used.
+By using HTTP the client can correctly receive the video, if it receives too much data then its buffer for video playing can get full.
 To prevent throwing data away the server will then stop sending.
@@
 \end{table}
-The Raspberry Pi 2 (RPi 2)only consumes 3 watts, because of this it doesn't need active cooling.
+The Raspberry Pi 2 (RPi 2) only consumes 3 watts, because of this it does not need active cooling.
 The RPi 2 does have a limited ethernet cable of only 100 Mbps.
@@
 
-In the end it would be ideal if the RPi 2 will fit inside a data center.
+A lot of small computers that can be turned of, instead of a few big ones that have to be on all the time can be a big step in saving energy consumed by big data centers.
+In this part we will look into the possibilities of doing this with the Raspberry Pi.
+\newline
 It is possible to fit a lot of Raspberry Pi's inside a data center.
@@
 With a special board you can for example reboot them from a distance.
-\newline In this research we only have 8 Pi's and these fit easily inside the rack.
+By having a microserver like a Raspberry Pi in a data center the hardware can be owned by only the customer, and because its in a data center there are the advantages of the high speed internet.
+By owning the hardware the customer will have more control over the data in the privacy and reliability aspect.\newline In this research we only have 8 Pi's and these fit easily inside the rack.
 The cooling of the data rack is more than sufficient to cool all these Raspberry's.
@@
 
-The setup for this project looked like this:
+In this project a own cluster of Raspberry Pi's has been build to test its possibilities. The setup for this project looked like this:
 \begin{figure}[H]
@@
 	\begin{tabular}{|c|c|c|} \hline
-		Core & Ampère (A) & Volt\\ \hline
-		1 & 0.339 & 4.84 \\ \hline
-		2 & 0.365 & 4 \\ \hline
-		3 & 0.392 & 4 \\ \hline
-		4 & 0.443 & 4 \\ \hline
+		Core & Ampère (A) & Volt (V)\\ \hline
+		1 & 0.340 & 4.84 \\ \hline
+		2 & 0.365 & 4.79 \\ \hline
+		3 & 0.392 & 4.77 \\ \hline
+		4 & 0.415 & 4.78 \\ \hline
 	\end{tabular}
@@
 
-The idle usage of the Raspberry Pi 2 is 0.312 Ampère and 4.86 Volt.
-In the table there is showed that with a benchmark test of only one core the Ampère going through the system is only 0.339, this means that it is barely increasing when using one core fully or idle.
+The idle usage of the Raspberry Pi 2 is 0.315 Ampère and 4.78 Volt.
+In the table there is showed that with a benchmark test of only one core the Ampère going through the system is  0.339A.
+There is also a read  and a memory test done which gave a voltage of 4.79 and a Ampère of 0.440-0.442.
 A normal server needs about 500 watt.
-Each Raspberry Pi has a consumption of about 3.5 watt, so about 500/3.5=140 Pi's will be possible instead of a single server.
+Each Raspberry Pi has a consumption in this test of about 2.1 watt, so about 500/2.1=238 Pi's will be possible instead of a single server.
 By using these small modular systems the power consumption inside a data center can be improved.
+The space usage however still isn't optimal, because the Raspberry Pi 2 has a micro USB cable  in one corner and an ethernet cable in the other as can be seen in figure \ref{fig:raspberry}.
+This can be solved by letting the power go over the ethernet by using a Power over Ethernet cable and a switch that is suitable for this technology.
+Another solution can be by making a motherboard on which you can plug in Raspberry Pi modules instead of a whole device.
+This is something that can be done in future work.
 
@@
 \textbf{NGINX}~\cite{nginx}: For the load balancing and streaming over HTTP NGINX will be used.
+NGINX has a efficient algorithm to do HTTP load balancing.
 A RTMP module from Arut for NGINX will be used to make a media streaming server over HTTP \cite{arut}.
+This is a efficient algorithm to transfer the HTTP with RTMP encapsulated data to the users.
 NGINX is optimized for ARM.
@@
 The Player uses server modules to stream the video to the client using the formats HTTP FLV or H264.\newline
-Cassandra is a database that helps replicating data across multiple data centers \cite{cassandra}.
+\textbf{Cassandra} is a database that helps replicating data across multiple data centers \cite{cassandra}.
 In the case of this project there are videos stored.
@@
 	\item CPU test
+	\item Iperf test
 	\item RTMP stream test
@@
 The Raspberry Pi's are stress tested to make sure that they are operating correctly.
-For this the program stress for Linux is used to monitor its health.
-All eight Raspberry Pi 2 have been tested using this program and they were working correctly.
+For this the program stress for Linux is used to monitor its health \cite{stress}.
+Stress is a workload generator to test if the CPU, memory and I/O are working correctly.
+All three Raspberry Pi 2 have been tested using this program and they were working correctly.
 
@@
 FFmpeg needs a lot of CPU power to create new videos in different formats.
-To test this the top command of Linux was used.
+To test this the top command of Linux was used \cite{top}.
 This measures the processor activity in real time.
-In this test a 230 MB 720p MPEG-4 (MP4 ) video has been made into three different lower qualities videos, it required 200 \% of the CPU power.
+In this test a 230 MB 720p MPEG-4 (MP4 ) video has been converted into three different lower qualities videos, it required 200 \% of the CPU power.
 The output is a 120p, 240p and 480p video file.
-At 200 \% CPU 2 cores has to be used out of the four to produce the video, this would result in the fact that the Raspberry Pi can only process two videos into different formats at the same time.
+At 200 \% CPU 2 cores have to be used out of the four to produce the video, this would result in the fact that the Raspberry Pi can only process two videos into different formats at the same time.
 When you have streamers that have only limited data available they will not have all the different formats.
-These streamers need to quickly produce these videos to different formats and this can lead till difficulties.
+These streamers need to quickly produce these videos to different formats and this can lead to difficulties.
 \newline
@@
 The CPU power that is needed for a single stream is about 2 \% and this barely increases when more clients are listening to it.
-This test is done by using web browsers and the Linux top command.
+This test is done by using web browsers and the Linux top command \cite{top}.
+
+\subsubsection{Iperf}
+
+The internet speed is an important aspect in video streaming.
+According to Netflix you need about 5.0 Megabits per second to stream one HD movie \cite{netflix}.
+During the ipref test the RPi 2 has with the a maximum connection of  94.4 Mbps~\cite{ipref}.
+This would result in the possibility for a RPi 2 to stream about 18 videos at the same time.
 
@@
 This test is done with a laptop and RPi 2.
-First a test case is created in Apache JMeter then a RTMP video stream is started and this is checked in a media player and a web page in a web browser.
-The result of this test is that it can handle 25 users for streaming MPEG-4 (MP4 ) files at a user at the same time.
-If there are more users used the video might freeze.
-This can result in a bad experience for the user watching the video.
-The RTMP stream will stream the video only in 720p format.
-Another test is by opening a media player like VLC were you can type in the RTMP stream address coming from the RPi 2.
+First a test case is created in Apache JMeter then a RTMP video stream is started and this is checked in a web page in a web browser.
+The reason to check it inside a web browser is because Apache JMeter can only measure HTTP files.
+The result of this test is that it can handle 25 users for streaming MPEG-4 (MP4 ) files over HTTP.
+If there are more users used the video might freeze, because there is to much latency.
+This becomes worse the more users there are this is a linear decrease.
+The RTMP stream used in this test streams the video only in 720p format.
+\newline Another test is by opening a media player like VLC were you can type in the RTMP stream address coming from the RPi 2.
 If the RTMP stream with the 230 MB video of 49 minutes is opened you can see that the video freezes some times do to buffering problems.
+This is because of the buffer length that is to long.
 \newline
@@
 This is with the Raspberry Pi 2 having a 100 Mbit connection.
-The RPi 2 has with the Iperf test a maximum connection of  94.4 Mbps~\cite{ipref}.
-With a USB 2.0 gigabit adapter this could increase in a 470 Mbit connection resulting in a increasing amount of users for each Raspberry Pi 2.
+As been seen in the test before it might already freeze at 25 users.
+This latency is introduced by the client which has not enough buffer time.
+Another problem is that FFmpeg is used as converter video to the RTMP stream, the use of a converter causes latency.
 \newline
 If then a different stream is created with for example a audio file of 9 minutes there is no freezing with the VLC player.
-To test it in the browser a JW player is embedded inside the web page.
+\newline To test it in the browser a JW player is embedded inside the web page.
 This browser stream can be maxed with the 118 users that are theoretically possible with the 800 kbit/s stream of the small movie.
+This is because the latency is not that high duo to the smaller screen used and the lower buffer length.
 
 \subsubsection{Video on demand test}
-For the video on demand test a RTMP stream with FFmpeg has been created and NGINX was started to share the video. 
-For Video on Demand most is done by NGINX and it was clearly visible that this kind of streaming is causing less freezing.
-This is because you can already start watching before the video is loaded.
-Video on demand (VOD)is better equipped to load the stream then only RTMP.
+For the video on demand (VOD) test a RTMP stream with FFmpeg has been created and NGINX was started to share the video.
+VLC was then opened on the laptop to see if there were any differences between VOD and a normal RTMP stream.
+The difference between VOD and RTMP is huge.
+With the use of video on demand the freezing was not visible.
+VOD is better equipped to load the stream then only RTMP.
 With only RTMP it's only possible to watch what is at that moment being played like normal television.
-It also doesn't adjust the bit stream depending on the quality you need.
-Something VOD does.
+RTMP does not adjust the bit stream depending on the quality you need, which is something VOD does.
 
 \subsubsection{SMIL test}
-Streaming with SMIL protocol has been done.
-This makes it possible to choose your own video streaming rate for the same file, for example 120p or 480p version of a movie.
+By using the SMIL protocol you make it possible to choose your own video streaming rate for the same file, for example 120p or 480p version of a movie.
 You now can choose the quality by yourself.
-This is something that Youtube does.
-There is also a possibility to switch the quality depending on the amount of data that can get over the network.
-During the test with 100 connections there was freezing when the users can set their own quality.
+This is something that for example Youtube does.
+With SMIL there is the possibility to switch the quality depending on the amount of data that can get over the network.
+During the test with Apache JMeter by which 100 connections were simulated watching the video with the SMIL protocol used there was freezing when the users can not set their own quality.
 When it is done automatically this was not the case.
-In apache JMeter it was also possible to see some latency when testing.
-For this testing videos of different qualities have been made.
+In apache JMeter it was also possible to see some latency when testing the streams.
+To make this test possible videos of different qualities have been created.
+These video versions were created by FFmpeg and were the 720p, 480p, 240p and 120p version of the 230 MB video.
 
 \subsubsection{Cassandra test}
-For the file location and database it would be nice to run the Cassandra data server.
+For the file location and database a Cassandra database has been made.
 This data server is also used by Netflix to keep track of it's files.
-It turned out that it was possible to run Cassandra.
-cqlsh command it is possible to so that the cluster is running.
+It turned out that it was possible to run Cassandra after a lot of configuration for the Raspberry Pi was done.
+To see if Cassandra was running the Cassandra query language shell was  opened on each RPi 2.
+This was done by using the cqlsh command which is the command to start the cluster and its terminal.
+The output of the cqlsh command showed that it was connected to the cluster and the IP address of the RPi 2.
 
@@
 The Raspberry Pi 2 has made load balancing possible with NGINX and JW Player.
-Besides that it is possible to stream video's over the HTTP with RTMP encapsulated to the user.
-NGINX has a efficient algorithm to transfer the HTTP with RTMP encapsulated data to the users.
-It has also a efficient algorithm to do normal load balancing.
+In order to stream video to the user a RTMP message is encapsulated in HTTP for the web browser.
+For the media player a RTMP stream is send to the user that is made by NGINX and FFmpeg.\newline
+The Raspberry Pi 2 can make videos of different qualities with FFmpeg and it is perfectly capable of distributing these videos of the other Pi's.
+The maximum RTMP stream output for my RPi 2 was for one around 800 kb/s.
+This data stream size can be different for the size and duration of the video that is being send.
 \newline
-The Raspberry Pi 2 can make videos of different qualities with FFmpeg and it is perfectly capable of distributing these videos of the other Pi's.
-FFmpeg has a huge demand of the processor power and this can be a problem when a lot of videos have to be encoded.
-The RPi 2 has a slow internet connection and this means that it streaming capacity is rather limited.
-The maximum RTMP stream output for my RPi 2 was for one around 800 kb/s.
-This can be different for the size and duration of your MP4 stream or FLV.
 The video streaming with Video on Demand or adaptive streaming has a good performance.
@@
 In the future the Raspberry Pi 2 can be better than a normal server, because its more dedicated ARM processor.
+\newline
+For the file location it is possible to set up a scalable Cassandra database.
+By using Cassandra it is possible to locate the files even if one node fails.
+This can be important when many Raspberry Pi's in a data center are being used.
 
-In the table \ref{tab:Specificaties} its stated that the Raspberry only has 100 Mbps.
-Video streaming Its limited ethernet connection is a problem when it comes to video streaming.
-However with a larger Ethernet cable and a fast connection to a harddisk it would be much better for video streaming then the traditional video streaming from bigger servers.
-
-\section{Discussion \& Conclusion}
+\section{Conclusion}
 Small scale data centers are important for the data transfer over the internet.
@@
 In an ideal case you want to have elasticity over the network.
-In this way you can increase and decrease the computation of a data center nearby the user, so that data doesn't have to travel so far.For video streaming you want the data as near to the user as possible in order to get him the best quality at the right speed, so that the video doesn't freeze.
+In this way you can increase and decrease the computation of a data center nearby the user, so that data does not have to travel so far.
+For video streaming you want the data as near to the user as possible in order to get him the best quality at the right speed, so that the video doesn't freeze.
 For video streaming the client needs to buffer a part of the movie.
 If the server is nearby then it's more easy to adjust the settings of these buffer.
-\newline
+
 The Raspberry Pi 2 can be useful for video streaming.
@@
 Improvements on those load balancing techniques were not possible in the scope of this research, but might be possible in future research.
-\todo{any last words	}
+\todo{R3 \& R5 + any last words	 to do}
+
+\section{Discussion}
+
+ FFmpeg has a huge demand of the processor power and this can be a problem when a lot of videos have to be encoded. \newline
+ The RPi 2 has a slow internet connection and this means that it streaming capacity is limited to only 18 videos at the same time.
+With a USB 2.0 gigabit adapter attached to a Raspberry Pi 2 this could increase in a 470 Megabit connection then it would be possible to stream about 94 videos at the same time.
+\newline
+ Apache JMeter is a tool to test HTTP streaming.
+This can be used for doing web browsers streaming videos, but it would be more ideal to test only the RTMP stream.
+This turned out to be impossible with Apache.
+The next time there should be better looked at testing only the RTMP stream.
 
@@
 Besides this it might be interesting to look into Peer-to-Peer distribution in general and for video streaming in specific, there can be taken a look into the technology and legal aspect of  Peer-to-Peer distribution.
+It might be that a Raspberry Pi 2 can fit more easily inside a data center by using PoE or by making a special motherboard and Raspberry Pi 2 modules instead of a whole device.
 
 \section{Acknowledgments}
-This paper would not have been possible without the help of Björn Postema and Nick Shot.
-\clearpage
-\bibliographystyle{abbrv}
+This paper would not have been possible without the help of  student Nick Shot and PhD candidate Björn Postema.
+A special thanks to Björn Postema from the Design and Analysis of Communication Systems group of the University Twente, for his insight, good ideas and providing the necessary materials
+for doing this research.
+
+\bibliographystyle{abbrvnat}
 \bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
@@
 
-\section{Software configuration}\label{sec:software}
+\section{Software configuration and testing}\label{sec:software}
 
@@
 \subsubsection{GitHub}
-For more information about the project its possible to see the GitHub repository. Comments or questions about the code can also be asked there. \newline
+For more information about the project its possible to see the GitHub repository. Comments or questions about the code can be asked in the repository. \newline
 The link is: \newline

### 2015-06-02 paper/paper.tex
new paper conclusion

@@
 \begin{abstract}
-This is a paper in the area of cloud computing.
 Cloud computing is a trend IT that customers move computing and data away from desktop and portable PCs into data centers.
@@
 This research is a design research in which a design is made for a video streaming cloud consisting of Raspberry Pi's.
+In this research it turned out that the Raspberry Pi 2 has its hardware limits.
+The results is that it is not so useful inside a data center, but it is good for education purposes.
+In this research it was possible to run different video streaming algorithms.
+The Raspberry Pi 2 turned out to be a great device for doing research into video streaming.
 \end{abstract}
@@
 	\item What are small scale data centers with video streaming and why are they used?
-	\item Is the Raspberry Pi's usable for video streaming?
+	\item Is the Raspberry Pi 2 usable for video streaming?
 	\item How to fit the Raspberry Pi's into a data center considering cooling, space allocation and power?
@@
 This research is part literature study and a part of it is building a small Raspberry Pi cloud to analyze balancing techniques on the Raspberry Pi 2.
-For this research cloud video streaming is one of the specific aspects that will be investigated.
+For this research cloud video streaming is one of the specific aspects that is investigated.
 The first two research questions describe the state of the art.
@@
 \section{Research Methods}
-This research will investigate a cloud computer consisting of Raspberry Pi's.
+This research investigates a cloud computer consisting of Raspberry Pi's.
 The research method for this would be the Design Science research method.
 this is a method to solve field problems.
-This research will make use of the Design Science method proposed by Hevner~\cite{hevner:2007}.
-This design method has three parts.
+This research uses the Design Science method proposed by Hevner~\cite{hevner:2007}.
+This design method consists of three parts.
 \begin{figure}[H]
@@
 The \textbf{relevance cycle} is important, because you first have to identify the problems and opportunities.
-To identify these problems we will gave some more background information in the next section.
-The \textbf{design cycle} is where you actually build the design.
-This will be highlighted in the Setup \& Experiment section.
-The \textbf{rigor cycle} matters because it can give you two types of additional knowledge.
+The identification of these problems we are done in the next section.
+\newline The \textbf{design cycle} is where you actually build the design.
+This is highlighted in section \ref{sec:setupex}.
+\newline The \textbf{rigor cycle} is a cycle were you can get two types of additional knowledge.
 It provides past knowledge to ensure its invention and it's there to guarantee that the new product is a research contribution.
-This will for example be taken into account in the Result section.
+Information about the past can be found in section \ref{sec:back}.
+The other part is in section \ref{sec:setupex}.
 
-\todo{UML sequence diagram}
-
-\section{Background}
+\section{Background}\label{sec:back}
 \subsection{Small scale computing}
@@
 The load balancer will then point were which videos are stored.
+To show how the processes operate with one a other a UML sequence diagram is used \cite{Bernardi:2002:USD:584369.584376}.
 Here below is in a UML sequence diagram the flow displayed between the client and the video service.
@@
 
-\section{Setup \& Experiment}
+\section{Setup \& Experiment}\label{sec:setupex}
 
 \subsection{Experiment approach}
-This setup can be build by following the section \ref{sec:software} in the appendix.
+This setup can be build by following the information in the GitHub link in section \ref{sec:software} that can be found in the appendix.
 More details about the setup can be found in section \ref{sec:setup}.
+\newline
 A RPi 2 is used for video streaming with load balancing.
@@
 By owning the hardware the customer will have more control over the data in the privacy and reliability aspect.\newline In this research we only have 8 Pi's and these fit easily inside the rack.
-The cooling of the data rack is more than sufficient to cool all these Raspberry's.
+The cooling of the data rack is more than sufficient for all these Raspberry's.
 The power consumption of the RPi 2 is low as you can see in table \ref{tab:cpu} below.
@@
 This setup can be placed inside of a data center.
-The switch and the router will then be removed and the rest will be fit nicely into the server rack.
+The switch and the router will then be removed and the rest will be fit into the server rack.
 The setup that has been made now could easily fit on the project table, so that it was easy to reach them and a lot of research on them could be done.
@@
 	\centering \caption{CPU test}
-	\begin{tabular}{|c|c|c|} \hline
-		Core & Ampère (A) & Volt (V)\\ \hline
-		1 & 0.340 & 4.84 \\ \hline
-		2 & 0.365 & 4.79 \\ \hline
-		3 & 0.392 & 4.77 \\ \hline
-		4 & 0.415 & 4.78 \\ \hline
+	\begin{tabular}{|c|c|c|c|} \hline
+		Test & Ampère (A) & Volt (V) & Watt (W)\\ \hline
+		CPU 1 core & 0.340 & 4.84  & 1,65\\ \hline
+		CPU 2 cores & 0.365 & 4.79 & 1,75\\ \hline
+		CPU 3 cores & 0.392 & 4.77 & 1,87 \\ \hline
+		CPU 4 cores & 0.415 & 4.78 & 1,99 \\ \hline
+		Memory test & 0.440 & 4.79 & 2,11 \\ \hline
+		Storage read & 0.442 & 4,77 & 2,11\\ \hline
+		Storage write & 0.395 & 4.77 & 1.89 \\ \hline
+		Idle & 0.315 & 4.78 & 1,51 \\ \hline
 	\end{tabular}
@@
 The idle usage of the Raspberry Pi 2 is 0.315 Ampère and 4.78 Volt.
-In the table there is showed that with a benchmark test of only one core the Ampère going through the system is  0.339A.
+In the table there is showed that with a benchmark test of only one core the Ampère going through the system is  0.340A.
 There is also a read  and a memory test done which gave a voltage of 4.79 and a Ampère of 0.440-0.442.
@@
 	\item SMIL test
-	\item Cassandra test for file location
+	\item File location test
 \end{enumerate}
@@
 
-\subsubsection{Iperf}
+\subsubsection{Iperf test}
 
@@
 According to Netflix you need about 5.0 Megabits per second to stream one HD movie \cite{netflix}.
-During the ipref test the RPi 2 has with the a maximum connection of  94.4 Mbps~\cite{ipref}.
-This would result in the possibility for a RPi 2 to stream about 18 videos at the same time.
+During the ipref test the RPi 2 has with the a maximum connection of  94.2 Mbps~\cite{ipref}.
+This would result in the possibility for a RPi 2 to stream about 18 HD videos at the same time.
+Using the USB port and a gigabit adaptor can increase this amount to 470 MBps which would result in 94 HD videos at the same time.
 
@@
 \newline
-The RTMP stream is streaming about 800 kbit/s for a small 300 MB movie.
+The RTMP stream is streaming about 800 kbit/s for a small 230 MB movie.
 Theoretically this would mean that according to the formula max users=bandwidth/bit rate stream it will result in 118 users.
@@
 With SMIL there is the possibility to switch the quality depending on the amount of data that can get over the network.
-During the test with Apache JMeter by which 100 connections were simulated watching the video with the SMIL protocol used there was freezing when the users can not set their own quality.
-When it is done automatically this was not the case.
+During the test with Apache JMeter 100 connections were simulated watching the video.
+There are two scenarios one were the user can choose the quality by himself and one were it is done automatically.
+For the first scenario the user could choose between the 120p, 240p or 480p version of the 230 MB movie earlier used.
+The test is done by simulating only 120p, only 240p, only 480p or only 720p of the movie.
+When the 480p version is used freezing could be seen.
+With the other two this was a lot less.
+This results in the fact that when users select their own quality it is possible that some freezing can occur.
+When the quality was selected depending on the amount of data that a user can receive then there occurred no freezing.
 In apache JMeter it was also possible to see some latency when testing the streams.
@@
 
-\subsubsection{Cassandra test}
+\subsubsection{File location test}
 For the file location and database a Cassandra database has been made.
@@
 The output of the cqlsh command showed that it was connected to the cluster and the IP address of the RPi 2.
+\newline
+With NGINX and it's load balancing algorithm over HTTP it is possible to redirect the user to the right video.
 
-\section{Result}
+\section{Conclusion}
+The Raspberry Pi 2 turned out to be a device that can be perfectly used in research.
+It has it's limitations and capabilities.
+In this paper the research focused on the performance of the Raspberry Pi 2 in small scale data center with video streaming.
+To answer this several research questions are answered.
 
-For this project a good setup for video streaming has been built.
-This result has be made possible with NGINX and several other programs.
+The first research question aimed to find out what small data centers with video streaming are, and why they are used.
+Small scale data centers are important for the data transfer over the internet.
+They are used to avoid internet bottlenecks.
+Besides that smaller cloud computers can make use of microservers like the Raspberry Pi 2.
+For a good video stream a server is nearby, because then it's easier to adjust the settings for the buffer to watch a streamed video at the best quality.
+So a small data centers with video streaming is used to get an elastic network, that can scale data bandwidth needed for the movie.
+
+The goal of the second research question is to find out if the Raspberry Pi 2 is usable for video streaming.
+The Raspberry Pi 2 is capable of running a operating system that can host a streaming server.
+The Raspberry Pi 2 is capable of running an RTMP stream and serving videos on demand.
+The Raspberry has a low power usage, but has a limited network connection.
+This limited network connection makes the Raspberry Pi 2 not good for video streaming.
+The CPU is rather limited and FFmpeg could only convert two HD videos at the same time.
+Despite all these disadvantages the Raspberry Pi is still a good device to test streaming software for the ARM processor.
+It gives you the possibility to analyze on small scale what happens on the cloud with the video stream.
+
+The goal of the third research question was to see if it is possible to fit the Raspberry Pi inside a data center.The first advantage of the Raspberry Pi 2 is that it is a lot smaller and there can be placed several of them inside a data center instead of a server.
+It is possible to fit 500 Raspberry Pi's inside a single server rack inside a data center.
+This can save energy, because they can be turned on and off separately and they do not consume so much energy as a normal server.
+However this also has some drawbacks.
+The Raspberry Pi 2 still does not have enough processing power and its internet connection is slow.
+To solve these kinds of problems power over ethernet can be used.
+
+The aim of the fourth research question is to find a suitable setup for a Raspberry Pi cloud with video streaming.
+For this project a setup for video streaming has been built.
+For the operating system a diet version of the Raspbian is used this is called Dietpi.
+For the streaming NGINX, JW Player and FFmpeg are needed.
 The Raspberry Pi 2 has made load balancing possible with NGINX and JW Player.
-In order to stream video to the user a RTMP message is encapsulated in HTTP for the web browser.
-For the media player a RTMP stream is send to the user that is made by NGINX and FFmpeg.\newline
-The Raspberry Pi 2 can make videos of different qualities with FFmpeg and it is perfectly capable of distributing these videos of the other Pi's.
-The maximum RTMP stream output for my RPi 2 was for one around 800 kb/s.
-This data stream size can be different for the size and duration of the video that is being send.
-\newline
+In order to stream a video to the user a RTMP message is encapsulated in HTTP for the web browser.
+For the media player a RTMP stream is send to the user that is made by NGINX and FFmpeg.
+The Raspberry Pi 2 can make videos of different qualities with FFmpeg.
+For the file location it is possible to set up a scalable Cassandra database.
+By using Cassandra it is possible to locate the files even if one node fails.
 The video streaming with Video on Demand or adaptive streaming has a good performance.
-It is only limited to around 100 users.
 The RPi 2 has a rather limited connection, this makes video streaming with the RPi 2 still not to useful.
 However this experiment shows that the RPi 2 is capable of video streaming.
-In the future the Raspberry Pi 2 can be better than a normal server, because its more dedicated ARM processor.
-\newline
-For the file location it is possible to set up a scalable Cassandra database.
-By using Cassandra it is possible to locate the files even if one node fails.
-This can be important when many Raspberry Pi's in a data center are being used.
+In the future it will be good possible that devices with a ARM processor are used in a data center.
 
-\section{Conclusion}
-Small scale data centers are important for the data transfer over the internet.
-It can avoid internet bottlenecks.
-Besides that are the smaller cloud computers often better in executing small tasks instead of the bigger ones.
-In an ideal case you want to have elasticity over the network.
-In this way you can increase and decrease the computation of a data center nearby the user, so that data does not have to travel so far.
-For video streaming you want the data as near to the user as possible in order to get him the best quality at the right speed, so that the video doesn't freeze.
-For video streaming the client needs to buffer a part of the movie.
-If the server is nearby then it's more easy to adjust the settings of these buffer.
+The last research question looks into how the availability in a Raspberry pi cluster with video streaming affected by various load balancing techniques.
+In the research several load balancing techniques were used.
+NGINX offers load balancing over adaptive streaming, this is used for video on demand (VOD).
+To redirect the user to the video HTTP load balancing by NGINX has been done.
+In this research it turned out that RTMP streaming or VOD have differences in the availability.
+By using VOD the streaming goes better and the user experiences less freezing.
+SMIL can cause freezing when the user chooses the quality by himself, because its bitrate might not be sufficient for the quality causing freezing.
+When you let the computer decide to change the quality there will be less freezing.
+So by using these different load balancing techniques the performance and the user experience changes.
+Improvements on those load balancing techniques were not possible due to time constraints, but these improvements can be possible in future research.
 
-The Raspberry Pi 2 can be useful for video streaming.
-It can definitely be used for further research into video streaming algorithms.
-This can be algorithms such as video distribution algorithms.
-The Raspberry Pi 2 is a microserver and has a processor for small tasks which is video streaming.
-The Raspberry Pi 2 does have some drawbacks for video streaming, but is perfect for education purposes.
-\newline
-It is possible to fit 500 Raspberry Pi's inside a single server rack. \newline
-For the setup a diet version of the Raspbian operating system is used called Dietpi. Besides this it makes use of NGINX for the server with a streaming module for video. \newline
-In the research several load balancing techniques were used.
-Cassandra is used in this research to distribute and locate the videos over different Raspberry Pi's.
-Adaptive streaming is used for Video on demand and normal RTMP streaming is used to setup streams.
-Improvements on those load balancing techniques were not possible in the scope of this research, but might be possible in future research.
-\todo{R3 \& R5 + any last words	 to do}
+The main question is about the performance of the Raspberry Pi 2 inside a small scale data center with video streaming. A setup that is needed to do this is build in this research. 
+The Raspberry Pi 2 does have some drawbacks for video streaming, but is perfect for education purposes in the field of video streaming.
 
@@
 
- FFmpeg has a huge demand of the processor power and this can be a problem when a lot of videos have to be encoded. \newline
- The RPi 2 has a slow internet connection and this means that it streaming capacity is limited to only 18 videos at the same time.
-With a USB 2.0 gigabit adapter attached to a Raspberry Pi 2 this could increase in a 470 Megabit connection then it would be possible to stream about 94 videos at the same time.
+There are several points of discussion in this research.
+The RPi 2 has a slow internet connection and this means that it streaming capacity is limited.
+With a USB 2.0 gigabit adapter attached to a Raspberry Pi 2 this could increase in a 470 Megabit connection then it would be possible to stream about 5 times more videos at the same time.
 \newline
 Apache JMeter is a tool to test HTTP streaming.
-This can be used for doing web browsers streaming videos, but it would be more ideal to test only the RTMP stream.
-This turned out to be impossible with Apache.
+This can be used for doing web browsers streaming videos, but it would be more ideal to test only the RTMP stream for the RTMP test.
+This turned out to be impossible with this testing tool.
 The next time there should be better looked at testing only the RTMP stream.
@@
 This paper would not have been possible without the help of  student Nick Shot and PhD candidate Björn Postema.
-A special thanks to Björn Postema from the Design and Analysis of Communication Systems group of the University Twente, for his insight, good ideas and providing the necessary materials
-for doing this research.
+A special thanks to Björn Postema from the Design and Analysis of Communication Systems group of the University Twente, for his insight, good ideas and providing the necessary materials for doing this research.
 
@@
 \begin{figure}[H]
-	\includegraphics[scale=0.65]{Kostenoverzicht_cluster.pdf}
+	\includegraphics[scale=0.65]{cost_cluster.pdf}
 	\label{fig:cost}

### 2015-06-05 paper/paper.tex
changes

@@
 \usepackage{tabularx}
+
 \usepackage[numbers]{natbib}
@@
 \begin{document}
-
+\setcounter{page}{1}
+\pagenumbering{arabic}
 %
 % --- Author Metadata here --- DO NOT REMOVE OR CHANGE 
-%\conferenceinfo{13$^{th}$ Twente Student Conference on IT}{June 23$^{st}$, 2010, Enschede, The Netherlands.}
+\conferenceinfo{23$^{th}$ Twente Student Conference on IT}{June 22$^{st}$, 2015, Enschede, The Netherlands.}
 \CopyrightYear{2015} % Allows default copyright year (200X) to be over-ridden - IF NEED BE.
@@
 \begin{abstract}
-Cloud computing is a trend IT that customers move computing and data away from desktop and portable PCs into data centers.
+Cloud computing is a IT trend  in which customers move computing and data away from computer and laptop into data centers.
 These data centers require a lot of power and cooling.
-Nowadays approximately 30\% of the data coming from these data centers is video streaming.
+Nowadays, approximately 30\% of the data coming from these centers is video streaming.
 The Raspberry Pi 2 is a low cost device that can be used in a cloud for video streaming.
@@
 \section{Introduction}
-Today most of us have some data in the cloud. But despite the attention from the community, research and development of Cloud Computing services are still in its early days~\citep{tso:2013}. \newline
-Cloud computing is a trend in IT that moves customers computing and data away from desktop and portable PCs into large data centers \citep{dikaiakos:2009}.
-In the future most internet users are expected to access internet services over lightweight portable devices requiring a lot of data bandwidth \cite{dikaiakos:2009}.
+Today, most of us have some data in the cloud. Despite the attention from the community, research and development of Cloud Computing services are still in its early days~\citep{tso:2013}. \newline
+Cloud computing is a trend in IT that moves customers computing and data away from computer and laptop into large data centers \citep{dikaiakos:2009}.
+In the future, most internet users are expected to access internet services over lightweight portable devices requiring a lot of data bandwidth \cite{dikaiakos:2009}.
 This bandwidth usage causes bottlenecks.
-To prevent these bottlenecks people build data centers around the globe.
-On these data servers a lot of improvements can be made \cite{abrahamsson:2013,beloglazov:2010}.
-These data servers for example require a lot of space and cooling.
+To prevent these bottlenecks, data centers are build around the globe.
+These data centers can be greatly improved \cite{abrahamsson:2013,beloglazov:2010}.
+For example, these data centers require a lot of space and cooling.
 There are now new technologies such as for example the powerful ARM processor.
-Many companies want to explore the possibilities of the Raspberry Pi 2 , because of its ARM processor and the price \cite{Pcextreme}.
-Some data centers already offer some cloud computing using the Raspberry Pi 2.
+Many companies want to explore the possibilities of the Raspberry Pi 2 , because of its ARM processor and the low price \cite{Pcextreme}.
+At the time of writing the Raspberry Pi 2 costs around 40 euro.
+Some data centers already offer some cloud computing using the Raspberry Pi 2 \cite{Pcextreme}.
 \newline
-A Raspberry Pi 2 has a power usage between the 3-5 Watt and is a small computer.
-A normal server has a power usage between the 75 and 250 watt~\cite{Pcextreme,beloglazov2012energy}.
-The low power consumption and its computing power could mean that it is better to use a Raspberry Pi 2 for specific small tasks that do not demand an entire server.
+A Raspberry Pi 2 is a small computer and has a power usage between the 2 and 4 Watt.
+In contrast, a normal server has a power usage between the 75 and 250 watt~\cite{Pcextreme,beloglazov2012energy}.
+The low power consumption of the Raspberry Pi 2 and its computing power could mean that it is better to use a Raspberry Pi 2 for specific small tasks that do not demand an entire server.
 For this reason research is done on the performance of the Raspberry Pi 2 in a small data center.
@@
 A Raspberry Pi cloud can be the small data center for the future \cite{tso:2013}.
-The Raspberry is sold for 40 euro, this price makes it cheaper to do research in compared to a normal server.
-Building a cloud like this can be a cost effective scale model\cite{tso:2013}.
-It's a ideal testbed for testing distributed software.
+The Raspberry Pi 2 is cheaper in price compared to a more expensive normal server.
+The Raspberry Pi 2 can be an ideal testbed for testing distributed software.
 
-The Netherlands have one million subscribers for Netflix \cite{volkskrant}.
-Netflix is a popular video streaming service that makes HD movies watching possible.
-For this Netflix makes use of a content distribution network (CDN).
-On the internet this is known as an on demand service \cite{Adhikari:2012}.
-Netflix makes use of MPEG-DASH a protocol that makes streaming over HTTP possible \cite{martin:2013}.
-The problem is that Netflix is responsible for  29,7\% of the peak downstream traffic in US \cite{Adhikari:2012}.
-Because of this downstream the two main providers Comcast and  AT\&T were limiting the downstream of Netflix.
-This caused a lot of criticism and a new law for net neutrality has been made as a solution for this criticism \cite{net-neutrality}.
+In The Netherlands, one million people use Netflix \cite{volkskrant}.
+Netflix is a popular video streaming service that provides HD movies.
+For this Netflix makes use of a Content Distribution Network (CDN).
+Netflix makes use of MPEG-DASH a protocol for streaming over HTTP \cite{martin:2013}.
+The problem is that Netflix is responsible for  29,7\% of the peak downstream traffic in the US \cite{Adhikari:2012}, because of the traffic the two main providers Comcast and  AT\&T were limiting the downstream of Netflix.
+This caused a lot of criticism, to solve this a new law for net neutrality has been made \cite{net-neutrality}.
 \newline
-In the Netherlands video streaming services such as Youtube and Netflix have an increasing amount of users.
-The data streaming problems coming from these increasing amount of users make it interesting to do more research in data centers with video streaming.
-Most of the research in computer science nowadays happen on expensive large servers \cite{tso:2013}.
-For this it can be very useful to see if it is possible to do research on a small computer like a Raspberry Pi 2.
-The problem is that we do not know if video streaming in a cloud consisting of Raspberry Pi's is possible.
+In the Netherlands, video streaming services such as Youtube and Netflix have an increasing number of users.
+Nowadays, the data streaming problems are increasing, this makes it interesting to do more research in data centers with video streaming.
+Most of the existing research in computer science is performed on expensive large servers \cite{tso:2013}.
+It can be very useful to see if it is possible to do research on a small computer like a Raspberry Pi 2.
 
-In this paper there is an investigation in how useful the Raspberry Pi 2 is in a data center with video streaming.
-To come to an answer the performance of the Raspberry Pi 2 is evaluated.
+This paper investigates how useful the Raspberry Pi 2 is in a data center with video streaming.
+To come to a conclusion the performance of the Raspberry Pi 2 is evaluated by doing several benchmark tests.
 For this the main research question is:
@@
 
-In order to come to a answer for the main question several sub-questions are researched. These sub-questions will altogether provide a answer to the main research question.
+To answer for the main question, several sub-questions are researched, which are:
 
@@
 
-This research is part literature study and a part of it is building a small Raspberry Pi cloud to analyze balancing techniques on the Raspberry Pi 2.
-For this research cloud video streaming is one of the specific aspects that is investigated.
-The first two research questions describe the state of the art.
-The last three sub-questions go into the technical research that investigates the performance and possibility of Raspberry Pi's for cloud video streaming.
-The five sub-questions are being looked at in the next sections.
-Followed by a final section for conclusions and identified areas for future work.
+The five sub-questions are looked at in the next sections. Followed by a final section for conclusions and identified areas for future work.
+The first two research question are a literature study into video streaming and cloud computing.
+and a part of it is  The last three sub-questions go into the technical research that investigates the performance and possibility of Raspberry Pi's for cloud video streaming.
+This is done by building a small Raspberry Pi cloud.
 
 \section{Research Methods}
-This research investigates a cloud computer consisting of Raspberry Pi's.
-The research method for this would be the Design Science research method.
-this is a method to solve field problems.
+In the research the  aim is to build a Raspberry Pi cloud to measure the performance.
+This is achieved by building a Raspberry Pi cloud and doing benchmark test on this cloud.
 This research uses the Design Science method proposed by Hevner~\cite{hevner:2007}.
-This design method consists of three parts.
+The method is used to make an architecture for a Raspberry Pi cloud.
+This design science method consists of three cycles:
 \begin{figure}[H]
@@
 	\includegraphics[width=0.4\textwidth]{Design_science.png}
-	\caption{Design Science}
+	\caption{Design Science cycles \cite{hevner:2007}}
 	\label{fig:design} %always place your label after your caption!
 \end{figure}
-The \textbf{relevance cycle} is important, because you first have to identify the problems and opportunities.
-The identification of these problems we are done in the next section.
-\newline The \textbf{design cycle} is where you actually build the design.
-This is highlighted in section \ref{sec:setupex}.
-\newline The \textbf{rigor cycle} is a cycle were you can get two types of additional knowledge.
-It provides past knowledge to ensure its invention and it's there to guarantee that the new product is a research contribution.
-Information about the past can be found in section \ref{sec:back}.
-The other part is in section \ref{sec:setupex}.
+\textbf{relevance cycle} Represents the interaction with the domain. Here the problems and opportunities are identified. The identification of these problems are done in the next section. \newline 
+\textbf{design cycle} The most important cycle where the design is build. This is highlighted in section \ref{sec:setupex}. \newline
+\textbf{rigor cycle} Represents the interaction with the scientific community. This information can be found in section \ref{sec:back} and \ref{sec:setupex}.
 
@@
 Small scale cloud computing is cloud computing with smaller computation amounts than normal \cite{cox:2014}.
-Most users that operate in the cloud buy the services instead of buying the hardware and having to set up the servers themselves.
-This service is called Infrastructure as a Service.
-To this specific cloud service belongs the online storage of data.
-The Amazon Elastic Compute Cloud (Amazon EC2) is one of the most widely used infrastructure platforms that these clients use \cite{hofer:2011}.
-This elasticity of computing resources is very important \cite{Miettinen:2010:EEM:1863103.1863107}.
-A lot of companies have their own virtual machines running in large data centers \cite{beloglazov:2010}.
-The advantage is that these instances can be scaled dynamically to the customer it's need.
-Using these instances makes easier management of the computers and varying workloads possible.
+Most customers for cloud solutions buy the services instead of buying the hardware and having to set up the servers themselves.
+This service is called Infrastructure as a Service (IaaS).
+The elasticity of computing resources in the cloud is important to provide IaaS \cite{Miettinen:2010:EEM:1863103.1863107}.
+Many companies have their software running on virtual machines in data centers \cite{beloglazov:2010}.
+The advantage is that these virtual machines are scaled dynamically to the customer its need.
+Using the cloud makes  management easier.
 
-Several cloud services have a huge demand on the network. This high demand can sometimes make it possible that data centers are unreachable.
-That is a reason why many companies have their own data centers.
-These data centers are small and not energy efficient.
-Another reason why companies have their own data center is because they don't want their data to be in somebody else his hands.
+Several cloud services have a huge network demand, this may cause data centers to be unreachable.
+Because of the privacy and reachability of a data center many companies have their own servers.
+These servers are not energy efficient.
+\newline
 Netflix a cloud service is responsible for approximately 30\% of the peak downstream traffic in US \cite{Adhikari:2012, computer-networking}.
-To improve this there are several data patterns possible, it can for example make a huge different in sending data in small bursts or in one large burst.
+The data flowing through the network has different patterns.
+To improve this there are several data patterns possible, it can for example make a huge different in sending data in small bursts or in one large burst \cite{computer-networking}.
 
-A CDN makes use of small data centers.
-This is because in a CDN you can get your data that is from America from a more nearby storage place.
-For example a website may be hosted in America.
-This website is connected to a CDN and in this way its possible to get your data from a more nearby server that has a copy of that website.
-For example if you live in Amsterdam you can perhaps get your data from London where the CDN is located instead of America.
-In this way the latency is decreased and there is a shorter connection distance and you have faster load times.
-
-Power Usage Efficiency (PUE) is nowadays becoming a more important aspect in cloud computing.
-Keeping the power usage low is one of the main challenges of cloud computing.
-The data centers now are only 12 till 20\% of the time operating, while all the servers inside are still using energy.
-Keeping these data centers up requires a lot of electrical power.
-Therefore we perhaps need to more Green Cloud Computing solutions that reduce the electrical power consumption and reduce the environmental impact of data centers~\cite{beloglazov2012energy}.
-For example with data centers that are using microservers.
-More information about this is in the next section.
-\newline
-With the increase of lightweight portable devices the energy efficiency becomes more important.
-For example can the data center do the graphic calculations needed to create a good video, however then more data needs to be send of the network.
-This will save energy, but will increase the data over the network.
-This means that a trade-off has to be made between local processing and computation offloading \cite{Miettinen:2010:EEM:1863103.1863107}.
-Computation offloading makes the data centers do the calculations, therefore making cloud computing more important.
+Power Usage Efficiency (PUE) is a important aspect in cloud computing \cite{beloglazov2012energy}.
+There are more lightweight portable devices coming \cite{Miettinen:2010:EEM:1863103.1863107}, these devices are energy efficient, but will demand more processes being done by data centers \cite{Miettinen:2010:EEM:1863103.1863107}.
+Nowadays, the data centers operate 12 to 20\% of the time, the other 80 \% of the time the servers inside are still using energy \cite{beloglazov2012energy}.
+Therefore there is a need Green Cloud Computing solutions that reduce the electrical power consumption and the environmental impact of data centers~\cite{beloglazov2012energy}.
+Microservers can be used to reduce the consumption.
 
 \subsection{Microserver}
-Microservers come to good use in small data centers \cite{microserver}.
-They are smaller in size, computer power and consume less electricity.
-This makes them perfect for high traffic usage tasks.
-Its cheaper to a small device than a big server inside a data center, so smaller microservers make a data center more dynamic.
-The ability to add and remove more easily microservers can save a lot of energy.
-It's also better for optimization.
-A micro server often has a different processor compared to a normal server.
-ARM is a processor a micro server might use.
-This processor does not have so much overhead compared to a Intel one.
-The Intel processor is better at complex tasks, while the Arm processor is better at small tasks \cite{microserver}.
-The difference in these processes is because of their design.
-The ARM has the possibility to optimize it for a special task.
-In the data center of the future more of these dedicated processors will be used.
+Microservers are used in data centers \cite{microserver}.
+Microservers consume less electricity and have enough computer power for small tasks, therefore they can be used for high traffic usage tasks.
+Besides this they are small and are easier replaced compared to a normal server, by using them data centers can be more dynamic \cite{microserver}.
+The ability to add and remove microservers more easily can save a lot of energy.
+\newline
+A microserver often has a different processor compared to a normal server.
+The processors are often microprocessors like a ARM processor \cite{microserver}.
+There are two big processor companies in the world called ARM, Intel and AMD.
+The Intel and AMD processors are better at complex tasks, while the ARM processor is better at small tasks \cite{microserver}.
+In the data center of the future more dedicated microservers will be used, they are better at specialized tasks and are more energy efficient \cite{microserver}.
 
-\subsection{Streaming}\label{sec:stream}
-Video streaming happens with TCP or HTTP.
-TCP sends frames to the client and in these frames is the video stored.
-Of course if the available TCP send rate is large enough then the video will play without any delays.
-But if the TCP send rate is less then needed then the video play will alternate between periods of continuous playout and periods of freezing~\cite{computer-networking}.
-Its very important that video freezing or audio playing faster then the video does not happen.
-This is why multimedia applications have high performance requirements.
-To make the video streaming possible the client will connect with video streaming service its load balancer.
-The load balancer will then point were which videos are stored.
-To show how the processes operate with one a other a UML sequence diagram is used \cite{Bernardi:2002:USD:584369.584376}.
-Here below is in a UML sequence diagram the flow displayed between the client and the video service.
+\subsection{Video streaming}\label{sec:stream}
+Video streaming happens with HTTP, HTTP sends frames to the client and in the frames is the video stored \cite{computer-networking}.
+If the send rate is large enough the video will play without any delays, but if the send rate is too less then the video play will alternate between periods of continuous playout and periods of freezing~\cite{computer-networking}.
+\newline
+To make video streaming possible the client will connect with video streaming service its load balancer.
+The load balancer will then locate the videos.
+To show how the processes and operators operate with each other a UML sequence diagram is used \cite{Bernardi:2002:USD:584369.584376}.
 \begin{figure}[H]
@@
 
-As visible in the diagram you can see that there is a loop for the streaming.
-In this loop the client will keep requesting for more parts of the videos.
+In the diagram there is a loop for the video streaming, here the client will keep requesting for more parts of the videos.
 Depending on the algorithm being used the amount of data requested by the client can fluctuate.
 For streaming a video HTTP streaming is often used.
-By using HTTP the client can correctly receive the video, if it receives too much data then its buffer for video playing can get full.
-To prevent throwing data away the server will then stop sending.
-To prevent throwing data away the client will have a not to large buffer.
-\newline
+By using HTTP the client can correctly receive the video, if it receives too much data its buffer for video playing gets full.
+To prevent throwing data away the server then stops sending.
+
 There is a important streaming technique called adaptive streaming.
@@
 It improves the experience for the end-user by adapting the video quality dynamically to the viewers network condition \cite{ffmpeg}.
-This techniques looks to the clients CPU possibility and it's network possibilities.
+This techniques looks to the clients CPU possibility and its network possibilities.
 It delivers small sized chunks at multiple bitrates.
@@
 \subsection{Video streaming and load balancing}
-For video streaming several load balancing techniques can be used.
-There are several choices that have to be made by choosing a load balancer for a service.
-These choices can for example be performance, reliability and features.
+For video streaming several load balancing techniques are used.
+To choose a technique there is looked at performance, reliability and features.
 There can be a non-uniform demand for different movies.
-One solution to overcome this problem would be to replicate the most popular movies.
-One obvious problem is then that it is expensive in terms of storage space required.
-To solve this you can use dynamic replication to solve the load demand~\cite{dan1996load}.
-By using this you move portions of a movie to less used storage devices.
+One solution to overcome this problem would be to replicate the most popular movies, but this is expensive in terms of storage space required for this.
+A dynamic replication can be used to solve the load demand~\cite{dan1996load}.
+By using this  portions of a movie are moved to less used storage devices, so that these can stream the movie.
 The allocation of these movies only happen when there is a to high increase on one specific storage device.
@@
 
-Nowadays a lot of people watch their movies online using video streaming and this amount of people is increasing.
-The Netherlands have for example one million subscribers for Netflix \cite{volkskrant}.
-One thing that these users want is the on demand video streaming.
-They do not want to store the data itself and they want to have a wide choice of different videos.
-Netflix is a video streaming service that makes HD movies watching possible.
-This is known as a on demand service.
+One thing that users want is on demand video streaming.
+They do not want to store the data itself, and they want to have a wide choice of different videos when they want to watch it.
+Netflix is a on demand video streaming service that makes HD movies watching possible.
 For this Netflix makes use of a content distribution network (CDN).
@@
 \subsubsection{Video stream CDN}
-Video streamer Netflix has  it's own CDN.
+A CDN makes use of small data centers.
+This is because users want their data as nearby as possible  In this way the latency is decreased and there is a shorter connection distance, this gives the user faster load times.
+Video streamer Netflix has  its own CDN.
 This CDN is fully operational in 2015 and now they still use some other CDN's like Akamai.
@@
 A Beowulf cluster is simply a collection of identical, commodity computer hardware based systems~\cite{beowolf-setup}.
-The big advantage of the Raspberry Pi in this project was that it is cheap and it does not need a cluster administrator to watch over everything you do.
+The big advantage of the Raspberry Pi in this project was that it was cheap and it does not need a cluster administrator to check everything that was being done.
 
@@
 A small network cable offers still room for analyzing the video stream.
-The USB 2.0 has not a huge capabilities to share the data from a external harddisk to a user, but it will be enough for this small simulation.
-A normal Seagate harddisks demands 10 Watt when it is actively streaming videos and when it's standby it has a consumption of 0.1  Watt.
+The USB 2.0 has not a huge capabilities to share the data from a external harddisk to a user.
+A external Seagate harddisk demands 10 Watt when it is actively streaming videos and when it is standby it has a consumption of 0.1  Watt.
 
@@
 A lot of small computers that can be turned of, instead of a few big ones that have to be on all the time can be a big step in saving energy consumed by big data centers.
-In this part we will look into the possibilities of doing this with the Raspberry Pi.
+In this part we will look into the possibilities of doing this with the Raspberry Pi 2 .
 \newline
@@
 For this special designed boards are needed.
-With a special board you can for example reboot them from a distance.
+With a special board RPi 2 can be rebooted from a distance.
 By having a microserver like a Raspberry Pi in a data center the hardware can be owned by only the customer, and because its in a data center there are the advantages of the high speed internet.
-By owning the hardware the customer will have more control over the data in the privacy and reliability aspect.\newline In this research we only have 8 Pi's and these fit easily inside the rack.
+By owning the hardware the customer will have more control over the data in the privacy and reliability aspect.\newline In this research there are 3 Pi's and these fit easily inside the rack.
 The cooling of the data rack is more than sufficient for all these Raspberry's.
-The power consumption of the RPi 2 is low as you can see in table \ref{tab:cpu} below.
-The RPi 2 is also easy to replace inside a data center and it can easily be turned on and of, this makes it suitable inside a server rack.
+The power consumption of the RPi 2 is low as seen in table \ref{tab:cpu}.
+The RPi 2 is easy to replace inside a data center and it can easily be turned on and off, this makes it suitable inside a server rack.
 A problem that will exist with the Raspberry Pi 2 inside the data center is that every time a Pi's have troubles a help team inside the data center has to fix this for its customer.
@@
 	\centering 
-	\includegraphics[width=0.50\textwidth]{setup.jpg}
+	\includegraphics[width=0.45\textwidth]{setup.jpg}
 	\caption{Project Setup}
@@
 
+\begin{figure}[H]
+	\includegraphics[scale=0.37]{Temperature_Test.png}
+	\label{fig:temp}
+	\caption{Temperature Test}
+\end{figure}
+
 The idle usage of the Raspberry Pi 2 is 0.315 Ampère and 4.78 Volt.
@@
 This can be solved by letting the power go over the ethernet by using a Power over Ethernet cable and a switch that is suitable for this technology.
-Another solution can be by making a motherboard on which you can plug in Raspberry Pi modules instead of a whole device.
-This is something that can be done in future work.
+Another solution can be by making a motherboard on which  Raspberry Pi modules can be plugged instead of a whole device, This is future work.
 
@@
 This low memory usage is important, because the creation of different video formats requires a lot of process power.
-For most systems you want as less unnecessary overhead as possible.
 \newline
-\textbf{NGINX}~\cite{nginx}: For the load balancing and streaming over HTTP NGINX will be used.
+\textbf{NGINX}~\cite{nginx}: For the load balancing and streaming over HTTP NGINX is used.
 NGINX has a efficient algorithm to do HTTP load balancing.
-A RTMP module from Arut for NGINX will be used to make a media streaming server over HTTP \cite{arut}.
+A RTMP module from Arut for NGINX is used to make a media streaming server over HTTP \cite{arut}.
 This is a efficient algorithm to transfer the HTTP with RTMP encapsulated data to the users.
-NGINX is optimized for ARM.
+NGINX is optimized for ARM \cite{nginx}.
 This is a processor the Raspberry Pi 2 is using.
-One other reason to choose for NGINX and not for a apache webserver is that it uses less memory.
-NGINX has a more efficient model than apache, and because of this it can handle more HTTP requests.
-Besides this is for NGINX and Apache the most documentation available on how to do video streaming.
+Another reason to choose for NGINX and not for a apache webserver is that it uses less memory.
+NGINX has a more efficient model than apache, therefore it can handle more HTTP requests \cite{nginxvsapache}.
+Besides this is for NGINX and Apache the most documentation available on how to do video streaming \cite{nginxvsapache}.
 \newline
@@
 
-In this testing section several test will be done these are: 
+In this testing section several test are done, these are: 
 \begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex] 
@@
 At 200 \% CPU 2 cores have to be used out of the four to produce the video, this would result in the fact that the Raspberry Pi can only process two videos into different formats at the same time.
-When you have streamers that have only limited data available they will not have all the different formats.
+Streamers have limited data available, so they will not have all the different video formats.
 These streamers need to quickly produce these videos to different formats and this can lead to difficulties.
@@
 The internet speed is an important aspect in video streaming.
-According to Netflix you need about 5.0 Megabits per second to stream one HD movie \cite{netflix}.
+According to Netflix there is 5.0 Megabits per second needed to stream one HD movie \cite{netflix}.
 During the ipref test the RPi 2 has with the a maximum connection of  94.2 Mbps~\cite{ipref}.
 This would result in the possibility for a RPi 2 to stream about 18 HD videos at the same time.
-Using the USB port and a gigabit adaptor can increase this amount to 470 MBps which would result in 94 HD videos at the same time.
+A simultaneous request of data by multiple streams reduces the bandwidth.
+So if many people do at the same time a request this can influence the connection of the Raspberry Pi.
+%Using the USB port and a Gigabit adapter can increase this amount to 220 Mbit/sec which would double the amount of HD videos being streamed.
 
@@
 The RTMP stream used in this test streams the video only in 720p format.
-\newline Another test is by opening a media player like VLC were you can type in the RTMP stream address coming from the RPi 2.
-If the RTMP stream with the 230 MB video of 49 minutes is opened you can see that the video freezes some times do to buffering problems.
-This is because of the buffer length that is to long.
+\newline Another test is by opening a media player like VLC were the RTMP stream address from the RPi 2 is opened.
+If the RTMP stream with the 230 MB video of 49 minutes is opened  there can be seen that the video freezes, this is due to buffering problems.
+The cause of this is that the buffer length is too long.
 \newline
@@
 VOD is better equipped to load the stream then only RTMP.
-With only RTMP it's only possible to watch what is at that moment being played like normal television.
-RTMP does not adjust the bit stream depending on the quality you need, which is something VOD does.
+With only RTMP it is only possible to watch what is at that moment being played like normal television.
+RTMP does not adjust the bit stream depending on the quality needed, which is something VOD does.
 
 \subsubsection{SMIL test}
-By using the SMIL protocol you make it possible to choose your own video streaming rate for the same file, for example 120p or 480p version of a movie.
+By using the SMIL protocol it is possible to choose a different video streaming rate for the same file, for example 120p or 480p version of a movie.
 You now can choose the quality by yourself.
@@
 For the file location and database a Cassandra database has been made.
-This data server is also used by Netflix to keep track of it's files.
+This data server is also used by Netflix to locate the movies.
 It turned out that it was possible to run Cassandra after a lot of configuration for the Raspberry Pi was done.
@@
 \newline
-With NGINX and it's load balancing algorithm over HTTP it is possible to redirect the user to the right video.
+NGINX has a load balancing algorithm over HTTP. In this test it was possible to redirect the user to the right video by using this algorithm.
+
+\section{Discussion}
+
+There are several points of discussion in this research.
+The RPi 2 has a slow internet connection and this means that it streaming capacity is limited.
+With a USB 2.0 gigabit adapter attached to a Raspberry Pi 2 this could  double the connection speed, so twice the amount of videos are being streamed.
+\newline
+Apache JMeter is a tool to test HTTP streaming.
+This can be used for doing web browsers streaming videos, but it would be more ideal to test only the RTMP stream for the RTMP test.
+This turned out to be impossible with this testing tool.
+The next time there should be better looked at testing only the RTMP stream.
 
 \section{Conclusion}
-The Raspberry Pi 2 turned out to be a device that can be perfectly used in research.
-It has it's limitations and capabilities.
+The Raspberry Pi 2 turned out to be a device that can be used in research.
+It has limitations and capabilities.
 In this paper the research focused on the performance of the Raspberry Pi 2 in small scale data center with video streaming.
@@
 
-The first research question aimed to find out what small data centers with video streaming are, and why they are used.
-Small scale data centers are important for the data transfer over the internet.
+To answer the first research question, small scale data centers are important for the data transfer over the internet.
 They are used to avoid internet bottlenecks.
 Besides that smaller cloud computers can make use of microservers like the Raspberry Pi 2.
-For a good video stream a server is nearby, because then it's easier to adjust the settings for the buffer to watch a streamed video at the best quality.
-So a small data centers with video streaming is used to get an elastic network, that can scale data bandwidth needed for the movie.
+For a good video stream a server is needed nearby, because its easier to adjust the settings for the buffer to watch a streamed video at the best quality.
+A small data centers with video streaming is used to get an elastic network, that can scale data bandwidth needed for video streaming.
 
@@
 Despite all these disadvantages the Raspberry Pi is still a good device to test streaming software for the ARM processor.
-It gives you the possibility to analyze on small scale what happens on the cloud with the video stream.
+The Raspberry Pi 2 has possibility to analyze on small scale what happens on the cloud with the video stream.
 
@@
 However this experiment shows that the RPi 2 is capable of video streaming.
-In the future it will be good possible that devices with a ARM processor are used in a data center.
+In the future it is likely that devices with a ARM processor are used in a data center.
 
@@
 SMIL can cause freezing when the user chooses the quality by himself, because its bitrate might not be sufficient for the quality causing freezing.
-When you let the computer decide to change the quality there will be less freezing.
+When the computer decides to change the quality there is less freezing.
 So by using these different load balancing techniques the performance and the user experience changes.
@@
 
-The main question is about the performance of the Raspberry Pi 2 inside a small scale data center with video streaming. A setup that is needed to do this is build in this research. 
-The Raspberry Pi 2 does have some drawbacks for video streaming, but is perfect for education purposes in the field of video streaming.
-
-\section{Discussion}
-
-There are several points of discussion in this research.
-The RPi 2 has a slow internet connection and this means that it streaming capacity is limited.
-With a USB 2.0 gigabit adapter attached to a Raspberry Pi 2 this could increase in a 470 Megabit connection then it would be possible to stream about 5 times more videos at the same time.
-\newline
-Apache JMeter is a tool to test HTTP streaming.
-This can be used for doing web browsers streaming videos, but it would be more ideal to test only the RTMP stream for the RTMP test.
-This turned out to be impossible with this testing tool.
-The next time there should be better looked at testing only the RTMP stream.
+The main question is about the performance of the Raspberry Pi 2 inside a small scale data center with video streaming.
+A setup that is needed to do this is build in this research.
+The Raspberry Pi 2 does have some drawbacks for video streaming, but is usable for education purposes in the field of video streaming.
 
@@
 %
-\vspace{50 mm}
+%\vspace{50 mm}
 
@@
 
-\clearpage
 \appendix
@@
 \begin{figure}[H]
-	\includegraphics[scale=0.65]{cost_cluster.pdf}
+	\includegraphics[scale=1]{cost_cluster.png}
 	\label{fig:cost}

### 2015-06-08 paper/paper.tex
paper changes

@@
 \setlength{\bibsep}{0.0pt}
-\newcommand\todo[1]{
-	\textcolor{green}{#1}
-}
 \restylefloat{figure}
@@
 
-\keywords{Cloud computing, Raspberry Pi 2,  micro data center, video streaming, load balancing}
+\keywords{Cloud computing, Raspberry Pi 2, RPi2,  micro data center, video streaming, load balancing}
 
 \section{Introduction}
-Today, most of us have some data in the cloud. Despite the attention from the community, research and development of Cloud Computing services are still in its early days~\citep{tso:2013}. \newline
-Cloud computing is a trend in IT that moves customers computing and data away from computer and laptop into large data centers \citep{dikaiakos:2009}.
-In the future, most internet users are expected to access internet services over lightweight portable devices requiring a lot of data bandwidth \cite{dikaiakos:2009}.
+Today, most of us have data in the cloud. Despite the attention from the community, research and development of Cloud Computing services are still in its early days~\citep{tso:2013}. \newline
+Cloud computing is a trend in IT that moves customers computing and data away from computer, and laptop into large data centers \citep{dikaiakos:2009}.
+In the future, most Internet users are expected to access Internet services over lightweight portable devices requiring a lot of network bandwidth \cite{dikaiakos:2009}.
 This bandwidth usage causes bottlenecks.
-To prevent these bottlenecks, data centers are build around the globe.
+To prevent these bottlenecks, data centers are built around the globe.
 These data centers can be greatly improved \cite{abrahamsson:2013,beloglazov:2010}.
 For example, these data centers require a lot of space and cooling.
-There are now new technologies such as for example the powerful ARM processor.
-Many companies want to explore the possibilities of the Raspberry Pi 2 , because of its ARM processor and the low price \cite{Pcextreme}.
-At the time of writing the Raspberry Pi 2 costs around 40 euro.
-Some data centers already offer some cloud computing using the Raspberry Pi 2 \cite{Pcextreme}.
+There are now new technologies such as the powerful ARM processor.
+Companies want to explore the possibilities of the Raspberry Pi 2 (RPi2), because of its ARM processor and the low price \cite{Pcextreme}.
+At the time of writing the RPi2 costs around 40 euro.
+The RPi2 is cheaper in price compared to a more expensive normal server.
+Some data centers offer some cloud computing using the Raspberry Pi 2 \cite{Pcextreme}.
 \newline
-A Raspberry Pi 2 is a small computer and has a power usage between the 2 and 4 Watt.
-In contrast, a normal server has a power usage between the 75 and 250 watt~\cite{Pcextreme,beloglazov2012energy}.
-The low power consumption of the Raspberry Pi 2 and its computing power could mean that it is better to use a Raspberry Pi 2 for specific small tasks that do not demand an entire server.
-For this reason research is done on the performance of the Raspberry Pi 2 in a small data center.
+A RPi2 is a small computer and has a power usage between two and four Watt.
+In contrast, a normal server has a power usage between 75 and 250 Watt~\cite{Pcextreme,beloglazov2012energy}.
+The low power consumption of the RPi2 and its computing power could mean that it is better to use a RPi2 for specific small tasks that do not demand an entire server.
+For this reason, research is done on the performance of the RPi2 in a small data center.
 \newline
-A Raspberry Pi cloud can be the small data center for the future \cite{tso:2013}.
-The Raspberry Pi 2 is cheaper in price compared to a more expensive normal server.
-The Raspberry Pi 2 can be an ideal testbed for testing distributed software.
+A Raspberry Pi cloud can be the small data center for the future \cite{tso:2013}. The RPi2 can be an ideal testbed for testing distributed software.
 
-In The Netherlands, one million people use Netflix \cite{volkskrant}.
+In The Netherlands one million people use Netflix \cite{volkskrant}.
 Netflix is a popular video streaming service that provides HD movies.
-For this Netflix makes use of a Content Distribution Network (CDN).
-Netflix makes use of MPEG-DASH a protocol for streaming over HTTP \cite{martin:2013}.
-The problem is that Netflix is responsible for  29,7\% of the peak downstream traffic in the US \cite{Adhikari:2012}, because of the traffic the two main providers Comcast and  AT\&T were limiting the downstream of Netflix.
+To achieve this Netflix makes use of a Content Distribution Network (CDN).
+Netflix makes use of MPEG-DASH, a protocol for streaming over HTTP \cite{martin:2013}.
+The problem is that Netflix is responsible for approximately 30 \% of the peak downstream traffic in the US \cite{Adhikari:2012}.
+The result was that the two main providers Comcast and  AT\&T were limiting the downstream traffic of Netflix.
 This caused a lot of criticism, to solve this a new law for net neutrality has been made \cite{net-neutrality}.
@@
 Most of the existing research in computer science is performed on expensive large servers \cite{tso:2013}.
-It can be very useful to see if it is possible to do research on a small computer like a Raspberry Pi 2.
+It can be very useful to see if it is possible to do research on a small computer like a RPi2.
 
-This paper investigates how useful the Raspberry Pi 2 is in a data center with video streaming.
-To come to a conclusion the performance of the Raspberry Pi 2 is evaluated by doing several benchmark tests.
+This paper investigates how useful the RPi2 is in a data center with video streaming.
+To come to a conclusion the performance of the RPi2 is evaluated by doing several benchmark tests.
 For this the main research question is:
 \begin{center}
-How well does the Raspberry Pi 2 perform in small scale data centers with video streaming? 
+How well does the RPi2 perform in small scale data centers with video streaming? 
 \end{center}
@@
 	\item What are small scale data centers with video streaming and why are they used?
-	\item Is the Raspberry Pi 2 usable for video streaming?
-	\item How to fit the Raspberry Pi's into a data center considering cooling, space allocation and power?
-	\item What setup does a Raspberry Pi cloud with video streaming require?
-	\item How is availability in a Raspberry pi cluster with video streaming affected by various load balancing techniques? 
+	\item Is the RPi2 usable for video streaming?
+	\item How to fit the RPi2s into a data center considering cooling, space allocation and power?
+	\item What setup does a RPi2 cloud with video streaming require?
+	\item How is availability in a RPi2 cluster with video streaming affected by various load balancing techniques? 
 \end{enumerate}
 
-The five sub-questions are looked at in the next sections. Followed by a final section for conclusions and identified areas for future work.
+The five sub-questions are investigated in the next sections. Followed by a final section for conclusions and identified areas for future work.
 The first two research question are a literature study into video streaming and cloud computing.
-and a part of it is  The last three sub-questions go into the technical research that investigates the performance and possibility of Raspberry Pi's for cloud video streaming.
-This is done by building a small Raspberry Pi cloud.
+The last three sub-questions go into the technical research that investigates the performance and possibility of RPi2s for cloud video streaming.
+This is done by building a small RPi2 cloud.
 
 \section{Research Methods}
-In the research the  aim is to build a Raspberry Pi cloud to measure the performance.
-This is achieved by building a Raspberry Pi cloud and doing benchmark test on this cloud.
+In the research the  aim is to build a RPi2 cloud to measure the performance.
+This is achieved by building a RPi2 cloud and doing benchmark test on this cloud.
 This research uses the Design Science method proposed by Hevner~\cite{hevner:2007}.
@@
 \textbf{relevance cycle} Represents the interaction with the domain. Here the problems and opportunities are identified. The identification of these problems are done in the next section. \newline 
-\textbf{design cycle} The most important cycle where the design is build. This is highlighted in section \ref{sec:setupex}. \newline
+\textbf{design cycle} The most important cycle where the design is built. This is highlighted in section \ref{sec:setupex}. \newline
 \textbf{rigor cycle} Represents the interaction with the scientific community. This information can be found in section \ref{sec:back} and \ref{sec:setupex}.
@@
 Many companies have their software running on virtual machines in data centers \cite{beloglazov:2010}.
-The advantage is that these virtual machines are scaled dynamically to the customer its need.
+The advantage is that these virtual machines are scaled dynamically to the customers need.
 Using the cloud makes  management easier.
@@
 \newline
-Netflix a cloud service is responsible for approximately 30\% of the peak downstream traffic in US \cite{Adhikari:2012, computer-networking}.
+Netflix, a cloud service, is responsible for approximately 30\% of the peak downstream traffic in the US \cite{Adhikari:2012, computer-networking}.
 The data flowing through the network has different patterns.
@@
 Power Usage Efficiency (PUE) is a important aspect in cloud computing \cite{beloglazov2012energy}.
-There are more lightweight portable devices coming \cite{Miettinen:2010:EEM:1863103.1863107}, these devices are energy efficient, but will demand more processes being done by data centers \cite{Miettinen:2010:EEM:1863103.1863107}.
-Nowadays, the data centers operate 12 to 20\% of the time, the other 80 \% of the time the servers inside are still using energy \cite{beloglazov2012energy}.
-Therefore there is a need Green Cloud Computing solutions that reduce the electrical power consumption and the environmental impact of data centers~\cite{beloglazov2012energy}.
-Microservers can be used to reduce the consumption.
+There are more lightweight portable devices coming \cite{Miettinen:2010:EEM:1863103.1863107}, these devices are energy efficient, but will demand more processes by data centers \cite{Miettinen:2010:EEM:1863103.1863107}.
+Nowadays, the data centers operate 12 to 20\% of the time, the other 80 \% of the time the servers inside are still using energy \cite{beloglazov2012energy, meisner2009powernap}.
+Therefore there is a need for Green Cloud Computing solutions that reduce the electrical power consumption and the environmental impact of data centers~\cite{beloglazov2012energy}.
+Microservers can be used to reduce the electricity consumption.
 
@@
 A microserver often has a different processor compared to a normal server.
-The processors are often microprocessors like a ARM processor \cite{microserver}.
-There are two big processor companies in the world called ARM, Intel and AMD.
+The processors are often microprocessors like ARM processors \cite{microserver}.
+There are three big processor companies in the world: ARM, Intel and AMD.
 The Intel and AMD processors are better at complex tasks, while the ARM processor is better at small tasks \cite{microserver}.
@@
 \subsection{Video streaming}\label{sec:stream}
-Video streaming happens with HTTP, HTTP sends frames to the client and in the frames is the video stored \cite{computer-networking}.
-If the send rate is large enough the video will play without any delays, but if the send rate is too less then the video play will alternate between periods of continuous playout and periods of freezing~\cite{computer-networking}.
+HTTP is used for video streaming, HTTP sends frames to the client and in the frames is the video stored \cite{computer-networking}.
+If the send rate is large enough the video will play without any delays, but if the send rate is too low then the video playback will alternate between periods of continuous playback and periods of freezing~\cite{computer-networking}.
 \newline
-To make video streaming possible the client will connect with video streaming service its load balancer.
+To make video streaming possible the client will connect with video streaming service by its load balancer.
 The load balancer will then locate the videos.
-To show how the processes and operators operate with each other a UML sequence diagram is used \cite{Bernardi:2002:USD:584369.584376}.
+To show how the processes and operators operate with each other, the UML sequence diagram in figure \ref{fig:stream} is used \cite{Bernardi:2002:USD:584369.584376}.
 \begin{figure}[H]
@@
 
-In the diagram there is a loop for the video streaming, here the client will keep requesting for more parts of the videos.
+In the diagram there is a loop for the video streaming, here the client will keep requesting more parts of the videos.
 Depending on the algorithm being used the amount of data requested by the client can fluctuate.
 For streaming a video HTTP streaming is often used.
-By using HTTP the client can correctly receive the video, if it receives too much data its buffer for video playing gets full.
+If the client receives too much data its buffer gets full.
 To prevent throwing data away the server then stops sending.
 
-There is a important streaming technique called adaptive streaming.
-This streaming algorithm is often used for video on demand (VOD).
+There is a important streaming technique called adaptive streaming \cite{computer-networking}.
+This streaming algorithm is often used for video on demand (VOD) \cite{computer-networking}.
 It improves the experience for the end-user by adapting the video quality dynamically to the viewers network condition \cite{ffmpeg}.
-This techniques looks to the clients CPU possibility and its network possibilities.
+This techniques takes into account the clients CPU possibility and its network possibilities.
 It delivers small sized chunks at multiple bitrates.
-This techniques is used for HTTP Live Streaming (HLS).
-This makes use of RTMP streaming and HTTP.
-This way of streaming is released in 2014.
-It codifies video in the H.264 format.\newline
+This techniques is used for HTTP Live Streaming (HLS) \cite{jwplayer}.
+HLS makes use of RTMP streaming and HTTP.
+HLS codifies video in the H.264 format.\newline
 There is another special kind of HTTP streaming called DASH (Dynamic Adaptive Streaming over HTTP)~\cite{computer-networking}.
 In DASH the video is encoded into several different versions.
-If the bandwidth is high, then the client selects chunks from a high-rate version and the way around~\cite{computer-networking}.
-The possibility to switch between bit rate versions is in video streaming very important.
-To make a smooth transition between these versions possible there are intermediate versions so that the client will see less suddenly the change in video quality.
-In HTTP streaming the server stores the video with a different URL.
+If the bandwidth is high, then the client selects chunks from a high-rate version and the other way around~\cite{computer-networking}.
+The possibility to switch between versions of different bitrates is in video streaming important for user experience.
+To make a smooth transition between these versions possible there are intermediate versions so that the client will see the change in video quality less suddenly.
 
@@
 For video streaming several load balancing techniques are used.
-To choose a technique there is looked at performance, reliability and features.
+To choose a technique the following aspects are taken into account performance, reliability and features.
 There can be a non-uniform demand for different movies.
@@
 A dynamic replication can be used to solve the load demand~\cite{dan1996load}.
-By using this  portions of a movie are moved to less used storage devices, so that these can stream the movie.
-The allocation of these movies only happen when there is a to high increase on one specific storage device.
+Parts of a movie are moved to less used storage devices, so that these can stream the movie.
+The allocation of these movies only happens when there is a too high increase on one specific storage device.
 In this way load imbalances can be prevented \cite{dan1996load}.
@@
 Load balancers are generally grouped in two layers.
-Layer 4 (FTP,IP, UDP, TCP )and layer 7 the application layer.
-Layer 7 load balancers distribute request based upon data in the application layer.
-Here below are some protocols and languages used for this:
+Layer 4, the transport layer and layer 7 the application layer \cite{computer-networking}.
+Layer 7 load balancers distribute requests based upon data in the application layer.
+Here below are two protocols and a language that is used:
 \begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-	\item HTTP, is the hypertext transfer protocol. In section \ref{sec:stream} are mentioned some usages of this protocol. A lot of video streaming services use HTTP streaming \cite{Adhikari:2012}.  
+	\item HTTP, is the hypertext transfer protocol. In section \ref{sec:stream} usages of this protocol are mentioned. A lot of video streaming services use HTTP streaming \cite{Adhikari:2012}.  
 	\item RTMP is a real time messaging protocol ~\cite{rtmp}.
@@
 It is encapsulated in HTTP to traverse firewalls.
-It gives more video player options compared to normal HTTP thus giving the user a better experience.
+It gives more video player options compared to normal HTTP, thus giving the user a better experience.
 A disadvantage compared to normal HTTP is that it is sensitive for data spikes.
@@
 
-One thing that users want is on demand video streaming.
-They do not want to store the data itself, and they want to have a wide choice of different videos when they want to watch it.
+Users want on demand video streaming, because they do not want to store the data themselves, and want a wide choice of different videos on demand.
 Netflix is a on demand video streaming service that makes HD movies watching possible.
-For this Netflix makes use of a content distribution network (CDN).
-They make use of amazon its AWS, simpleDB , S3 and Cassandra for file storage \cite{Adhikari:2012}.
-Netflix makes use of MPEG-DASH a protocol that makes streaming over HTTP possible.
+For this Netflix uses a content distribution network (CDN).
+Netflix uses amazon its AWS, simpleDB, S3 and Cassandra for file storage \cite{Adhikari:2012}.
+Netflix makes use of MPEG-DASH, a protocol that makes streaming over HTTP possible.
 To make this possible Netflix does several things in the cloud.
@@
 \subsubsection{Video stream CDN}
-A CDN makes use of small data centers.
-This is because users want their data as nearby as possible  In this way the latency is decreased and there is a shorter connection distance, this gives the user faster load times.
-Video streamer Netflix has  its own CDN.
-This CDN is fully operational in 2015 and now they still use some other CDN's like Akamai.
-Reasons for having an own CDN is that the load balancing can be better improved.
+A CDN uses small data centers, because users want their data as nearby as possible  In this way the latency is decreased and there is a shorter connection distance, this gives the user faster load times.
+Video streamer Netflix has  its own CDN \cite{netflix}.
+Reasons for having an own CDN is that the load balancing can be improved.
 The CDN that Netflix has created is called Open Connect.
-To make their CDN possible they work together with the ISP providers.
-They use high performance HTTP delivery to get the content to the users.
-By having their own CDN they can get the video's faster to their users, because they can optimize their video stream algorithms for their own CDN.
-Besides this its possible that in this way the data going over the network can be decreased.
+Netflix uses high performance HTTP delivery to get the content to the users.
+Data going over the network can be decreased and videos get faster to users with an own CDN, because video stream algorithms are better analyzed.
 
@@
 There have been several cloud projects with the Raspberry Pi. \newline
-One of these has been the supercomputer build by Southampton~\cite{cox:2014}.
-Here they build it with 64 raspberry Pi's .
-They used a Message Passing interface to communicate between the Raspberry Pi's.
-The research was done in order to see what the performance of a low-power high performance cluster is.
+One was the supercomputer built by Southampton~\cite{cox:2014}.
+Here a cluster was built with 64 raspberry Pi's.
+A Message Passing interface was used to communicate between the Raspberry Pi's.
+The research was done in order to see what the performance of a low-power high performance cluster was.
 \newline
@@
 This data center has 56 Raspberry Pi's.
-It is build for research and education purposes for a cloud data center.
-They have a Hadoop running on their servers.
+It was built for research and education purposes for a cloud data center.
+Hadoop was tested on their servers.
 \newline
-There was another project called the Beowulf cluster~\cite{beowolf-setup}.
+Another project called the Beowulf cluster~\cite{beowolf-setup}.
 This project was created for a PhD assignment.
-This cluster is build for collaboratively processing sensor data.
+This cluster was built for collaboratively processing sensor data.
 A Beowulf cluster is simply a collection of identical, commodity computer hardware based systems~\cite{beowolf-setup}.
@@
 
-For Video streaming there are several projects. These projects are often done by service providers such as Google with their video streamer Youtube. \newline
-NGINX is busy with their Video streaming project.
-NGINX works together with Netflix to give users the best video watching experience.
-NGINX is a scalable service with high performance load balancing.
-Netflix is together with NGINX busy with their project Open Connect.
+For Video streaming there are several projects. These projects are often done by service providers. \newline
+Netflix works together with NGINX on Netflix his project Open Connect.
+With this cooperation they want to give  users the best video watching experience.
 This project wants to improve the load balancing for video streaming over the whole network.
@@
 WOWZA provides video streaming for a lot of companies and universities.
-WOWZA has done several projects for video streaming and has build with the University of Maine a content management system for their online videos.
+WOWZA has done several projects for video streaming and has built with the University of Maine a content management system for their online videos.
+\newline
 One mayor video stream service is of course Youtube \cite{youtube}.
@@
 Nowadays Youtube is still working hard on optimizing their video streaming service.
-Youtube has a online API so developers can join in and start their own projects.
-Youtube has its own projects for example helping mobile gamers stream their video, helping with live streaming and many more.
+Youtube has a online API, so developers can join in and start their own projects.
+Youtube has its own projects for example helping mobile gamers stream their video and helping with live streaming.
 
@@
 	\includegraphics[width=0.4\textwidth]{Pi2ModB1GB_-comp.jpeg}
-	\caption{Raspberry Pi 2 model B}
+	\caption{Raspberry Pi 2 model B \cite{raspberry-pi}}
 	\label{fig:raspberry} %always place your label after your caption!
@@
 \begin{table}[H]
-	\centering \caption{Specifications}
+	\centering \caption{Specifications \cite{raspberry-pi}}
 	\begin{tabular}{|c|c|} \hline
@@
 \end{table}
-The Raspberry Pi 2 (RPi 2) only consumes 3 watts, because of this it does not need active cooling.
-The RPi 2 does have a limited ethernet cable of only 100 Mbps.
-This can be a huge drawback when large amounts of data need to be distributed over the Network.
-It is however very useful for a investigation in load balancing for video streaming.
-A small network cable offers still room for analyzing the video stream.
-The USB 2.0 has not a huge capabilities to share the data from a external harddisk to a user.
+The RPi2 only consumes 3 Watt, because of this it does not need active cooling.
+The RPi2 has a limited ethernet interface of only 100 Mbps.
+The network cable offers room for analyzing the video stream.
+The USB 2.0 is used to share the data from a external harddisk to a user.
 A external Seagate harddisk demands 10 Watt when it is actively streaming videos and when it is standby it has a consumption of 0.1  Watt.
@@
 All these Pi's need power, therefore there is a power supply and 3 micro USB cables.
-There are three sd cards needed for the Operating System, and other software, to make the RPi 2 work.
+There are three sd cards needed for the Operating System, and other software, to make the RPi2 work.
 A cost structure for this can be found in the appendix section~\nameref{sec:cost}.
 
-For some benchmark test a laptop is plugged in, so that several tests can be done from the laptop.
+For some benchmark tests a laptop is plugged in, so that several tests can be done from the laptop.
 
@@
 \subsection{Experiment approach}
-This setup can be build by following the information in the GitHub link in section \ref{sec:software} that can be found in the appendix.
+This setup is built by following the information in the GitHub link in section \ref{sec:software}, that can be found in the appendix.
 More details about the setup can be found in section \ref{sec:setup}.
 \newline
-A RPi 2 is used for video streaming with load balancing.
-For the experiment Raspberry Pi's with a static ip address are needed.
-This so we can connect easily to them with SSH.
-For the experiment we need a Raspberry Pi 2 that can make use of the Ethernet.
-This is because a RPi 2 is used as a webserver to make video streaming possible.
-This webserver will make video streaming possible.
-It will have a VPN to make it possible to put video's on the RPi 2.
-After this a cluster with one RPi 2 as a load balancer and the other two as a video stream Pi will be build.
+A RPi2 is used for video streaming with load balancing.
+For the experiment we need a Raspberry Pi 2 that can make use of the Internet.
+This is because a RPi2 is used as a webserver to make video streaming possible.
+It has a VPN to make it possible to put video's on the RPi2.
+A cluster with one RPi2 as a load balancer and the other two as a video stream Pi is built.
 If such a cluster is made tests can be done and improvements can be made.
-For example some test in streaming in different quality with load balancing.
-The setup of the Raspberry Pi 2:
-
-\begin{figure}[H]
-	\centering 
-	\includegraphics[width=0.5\textwidth]{raspsetup.jpg}
-	\caption{Raspberry Setup}
-	\label{fig:setup} %always place your label after your caption!
-\end{figure}
+For example streaming tests with different quality videos and load balancing.
+The test are found in section \ref{sec:test}.
+Below the setup design and legend for the RPi2 are given:
 \begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex] 
@@
 \end{enumerate}
-In the section \ref{sec:setup} the software is defined to create a cluster like this.
+For the research number three to five are Raspberry Pi's.
+\begin{figure}[H]
+	\centering 
+	\includegraphics[width=0.5\textwidth]{raspsetup.jpg}
+	\caption{Raspberry Setup}
+	\label{fig:setup} %always place your label after your caption!
+\end{figure}
 
-\subsection{Raspberry Pi 2 inside a data center}
+\subsection{RPi2 inside a data center}
 
-A lot of small computers that can be turned of, instead of a few big ones that have to be on all the time can be a big step in saving energy consumed by big data centers.
-In this part we will look into the possibilities of doing this with the Raspberry Pi 2 .
-\newline
-It is possible to fit a lot of Raspberry Pi's inside a data center.
-PCextreme has made it possible to fit 500 Pi's inside a single data rack \cite{Pcextreme}.
+In this part the research focuses on the possibilities of the RPi2 in a data center. \newline
+It is possible to fit a lot of RPi2s inside a data center.
+PCextreme has placed 500 Pi's inside a single data rack \cite{Pcextreme}.
 For this special designed boards are needed.
-With a special board RPi 2 can be rebooted from a distance.
-By having a microserver like a Raspberry Pi in a data center the hardware can be owned by only the customer, and because its in a data center there are the advantages of the high speed internet.
+With a special board RPi2 can be rebooted and turned off from a distance \cite{Pcextreme}.
+By having a microserver like a RPi2 in a data center the hardware can be owned by only the customer, because its better payable than a normal server.
+In a data center there are the advantages of the high speed Internet.
 By owning the hardware the customer will have more control over the data in the privacy and reliability aspect.\newline In this research there are 3 Pi's and these fit easily inside the rack.
-The cooling of the data rack is more than sufficient for all these Raspberry's.
-The power consumption of the RPi 2 is low as seen in table \ref{tab:cpu}.
-The RPi 2 is easy to replace inside a data center and it can easily be turned on and off, this makes it suitable inside a server rack.
-A problem that will exist with the Raspberry Pi 2 inside the data center is that every time a Pi's have troubles a help team inside the data center has to fix this for its customer.
-It is harder to get  a fully automated re-installation as for example a vServer more easily does.
+The cooling of the data rack is sufficient for all these RPi2s.
+The power consumption of the RPi2 is low as seen in table \ref{tab:cpu}.
+The RPi2 is easy to replace and it can easily be turned on and off, this makes it suitable inside a server rack.
+A problem that will exist with the RPi2 inside the data center is that every time a Pi's have troubles a help team inside the data center has to fix this for the customer.
 
-In this project a own cluster of Raspberry Pi's has been build to test its possibilities. The setup for this project looked like this:
+In this project a cluster of RPi2s is built to test its possibilities. The setup for this project is displayed below:
 \begin{figure}[H]
@@
 \end{figure}
-The figure \ref{fig:projectsetup} is photo of the project setup.
-This project setup is comparable with figure \ref{fig:setup}.
-The numbers in the front pint to the Raspberry Pi's that are also showed in figure \ref{fig:setup}.
+The numbers in front in figure \ref{fig:projectsetup} point to the RPi2s, these numbers correspond with the numbers in figure \ref{fig:setup}.
 The number in the back shows the little router that is behind the power supply.
 In this picture there is a extra switch to connect all the Raspberry Pi's.
-To redo this experiment there are only three Raspberry Pi's necessary.
 \newline
-This setup can be placed inside of a data center.
-The switch and the router will then be removed and the rest will be fit into the server rack.
-The setup that has been made now could easily fit on the project table, so that it was easy to reach them and a lot of research on them could be done.
+This setup can be placed inside of a data center. The switch and the router will then be removed and the rest will be fit into the server rack.
 
-To verify that a Pi can operate inside a data center some tests have been done.
+To verify that a Pi2 can operate inside a data center some tests have been done.
 For these tests a multimeter has been used.
 The Elro M990 multimeter has been used.
-The program sysbench has been used to run several CPU tests for the Raspberry Pi 2 its four cores.
+The program sysbench has been used to run several CPU tests for the RPi2 its four cores.
 This is a benchmark test to get a quick impression about the performance of the system.
@@
 		Test & Ampère (A) & Volt (V) & Watt (W)\\ \hline
-		CPU 1 core & 0.340 & 4.84  & 1,65\\ \hline
-		CPU 2 cores & 0.365 & 4.79 & 1,75\\ \hline
-		CPU 3 cores & 0.392 & 4.77 & 1,87 \\ \hline
-		CPU 4 cores & 0.415 & 4.78 & 1,99 \\ \hline
-		Memory test & 0.440 & 4.79 & 2,11 \\ \hline
-		Storage read & 0.442 & 4,77 & 2,11\\ \hline
+		CPU 1 core & 0.340 & 4.84  & 1.65\\ \hline
+		CPU 2 cores & 0.365 & 4.79 & 1.75\\ \hline
+		CPU 3 cores & 0.392 & 4.77 & 1.87 \\ \hline
+		CPU 4 cores & 0.415 & 4.78 & 1.99 \\ \hline
+		Memory test & 0.440 & 4.79 & 2.11 \\ \hline
+		Storage read & 0.442 & 4.77 & 2.11\\ \hline
 		Storage write & 0.395 & 4.77 & 1.89 \\ \hline
-		Idle & 0.315 & 4.78 & 1,51 \\ \hline
+		Idle & 0.315 & 4.78 & 1.51 \\ \hline
 	\end{tabular}
@@
 \end{table}
+A normal server needs about 500 W \cite{meisner2009powernap}.
+The RPi2 has a consumption in this test of about 2.1 W see table \ref{tab:cpu}.
+With a simple calculation is seen that 500/2.1=238 Pi's are possible instead of one server.
+The idle temperature is only 1.5 W, while normal severs still need 60 \% of the power \cite{meisner2009powernap}.
+By using these small modular systems the power consumption inside a data center can be improved.
+The space usage is not optimal, because the RPi2 has a micro USB cable  in one corner and an ethernet cable in the other as can be seen in figure \ref{fig:raspberry}.
+Improvements can be made by letting the power go over the ethernet by using a Power over Ethernet equipment.
+Another solution can be by making a motherboard on which  Raspberry Pi modules can be plugged instead of a whole device, This is future work.
+\newline
+There is a Temperature test done by running the same tests and measuring the temperature by using a self written script.
+The temperature is measured on the CPU.
+The room temperature during this test was around 23 degrees Celsius.
 
@@
 	\includegraphics[scale=0.37]{Temperature_Test.png}
+	\caption{Temperature Test}
 	\label{fig:temp}
-	\caption{Temperature Test}
+
 \end{figure}
+When running a four thread CPU test the maximum temperature is 60 degrees Celsius and at idle the temperature is 42 degrees Celsius, see figure \ref{fig:temp}.
+Data centers require a temperature of around 26 degree Celsius \cite{temperature}.
+So if a lot of Raspberry Pi's are together some cooling is needed.
+This will require less cooling then a server.
+A server is still consuming 60 \% of its power and thereby producing a lot of heat.
+While Raspberry Pi's can be turned off and are better scalable.
 
-The idle usage of the Raspberry Pi 2 is 0.315 Ampère and 4.78 Volt.
-In the table there is showed that with a benchmark test of only one core the Ampère going through the system is  0.340A.
-There is also a read  and a memory test done which gave a voltage of 4.79 and a Ampère of 0.440-0.442.
-A normal server needs about 500 watt.
-Each Raspberry Pi has a consumption in this test of about 2.1 watt, so about 500/2.1=238 Pi's will be possible instead of a single server.
-By using these small modular systems the power consumption inside a data center can be improved.
-The space usage however still isn't optimal, because the Raspberry Pi 2 has a micro USB cable  in one corner and an ethernet cable in the other as can be seen in figure \ref{fig:raspberry}.
-This can be solved by letting the power go over the ethernet by using a Power over Ethernet cable and a switch that is suitable for this technology.
-Another solution can be by making a motherboard on which  Raspberry Pi modules can be plugged instead of a whole device, This is future work.
-
-\subsection{Raspberry Pi 2 setup}\label{sec:setup}
+\subsection{RPi2 setup}\label{sec:setup}
 In this setup we are going to make a Netflix kind of video stream service. \newline
-\textbf{Dietpi} is the software we use as operating system \cite{dietpi}.
-This is a diet version of Raspbian the normal Raspberry Pi operating service.
-The Raspbian again is a diet version of Linux.
-This makes that Dietpi only has the most necessary software to operate.
-In this way the memory usage for the operating system stays low.
-This low memory usage is important, because the creation of different video formats requires a lot of process power.
+\textbf{Dietpi} is the software used as operating system \cite{dietpi}.
+This is a diet version of Raspbian, the normal Raspberry Pi operating service.
+Raspbian is a diet version of Linux \cite{raspberry-pi}.
+This means that Dietpi only has the most necessary software to operate.
+By using Dietpi the memory usage for the operating system stays low.
+This low memory usage is important, because the creation of different video formats requires a lot of process and memory power.
 \newline
@@
 NGINX is optimized for ARM \cite{nginx}.
-This is a processor the Raspberry Pi 2 is using.
-Another reason to choose for NGINX and not for a apache webserver is that it uses less memory.
-NGINX has a more efficient model than apache, therefore it can handle more HTTP requests \cite{nginxvsapache}.
-Besides this is for NGINX and Apache the most documentation available on how to do video streaming \cite{nginxvsapache}.
+This is the processor the RPi2 is using.
+Another reason to choose for NGINX and not for the Apache webserver is that it uses less memory.
+NGINX has a more efficient model than Apache, therefore it can handle more HTTP requests \cite{nginxvsapache}.
+Besides, for NGINX and Apache the most documentation available on how to do video streaming \cite{nginxvsapache}.
 \newline
@@
 It is a open source media player.
-Besides this also JW player can make it possible to do some load balancing dependable on the bit rate that is coming from the video.
-It supports dynamic streaming, dynamic streaming consists of multiple single streams with the same content, all in a different quality \cite{jwplayer}.
-from different streams.
+JW player makes it possible to do some load balancing dependable on the bit rate that is coming from the video.
+It supports dynamic streaming, that consists of multiple single streams with the same content, all in a different quality from different streams \cite{jwplayer}.
 The Player uses server modules to stream the video to the client using the formats HTTP FLV or H264.\newline
 \textbf{Cassandra} is a database that helps replicating data across multiple data centers \cite{cassandra}.
-In the case of this project there are videos stored.
-This data can automatically be replicated across the nodes for fault-tolerance.
-In this way its possible to have the data still available when a node crashes.
+In the case of this project there are videos stored by using Cassandra.
+The data can automatically be replicated across the nodes for fault-tolerance.
+Therefore, the data is still available when a node crashes.
 
-\subsection{Raspberry Pi 2  testing}
+\subsection{Raspberry Pi 2  testing}\label{sec:test}
 
-In this testing section several test are done, these are: 
+In this testing section several test are done. In appendix \ref{sec:software} are the results and software configuration. The following test were executed: 
 \begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex] 
@@
 
-The Raspberry Pi's are stress tested to make sure that they are operating correctly.
+The RPi2s are stress tested to make sure that they are operating correctly.
 For this the program stress for Linux is used to monitor its health \cite{stress}.
 Stress is a workload generator to test if the CPU, memory and I/O are working correctly.
-All three Raspberry Pi 2 have been tested using this program and they were working correctly.
-
+All three RPi2s are tested using this program and are working correctly.
+\newline
 Another test is done with FFmpeg.
 FFmpeg needs a lot of CPU power to create new videos in different formats.
-To test this the top command of Linux was used \cite{top}.
-This measures the processor activity in real time.
-In this test a 230 MB 720p MPEG-4 (MP4 ) video has been converted into three different lower qualities videos, it required 200 \% of the CPU power.
+To measure the CPU usage the top command of Linux was used, this measures the processor activity in real time \cite{top}.
+In this test a 230 MB 720p MPEG-4 (MP4 ) video has been converted into three different lower quality videos, this required 200 \% of the CPU power.
 The output is a 120p, 240p and 480p video file.
-At 200 \% CPU 2 cores have to be used out of the four to produce the video, this would result in the fact that the Raspberry Pi can only process two videos into different formats at the same time.
-Streamers have limited data available, so they will not have all the different video formats.
-These streamers need to quickly produce these videos to different formats and this can lead to difficulties.
+At 200 \% CPU 2 cores are used out of the four to produce the video, this results in the fact that the RPi2 can only process two videos into different formats at the same time.
+The RPi2 has limited storage available, so they cannot store all the different video formats.
+This results in that the RPi2 needs to produce  these videos quickly to different formats, this can lead to difficulties.
 \newline
@@
 The CPU power that is needed for a single stream is about 2 \% and this barely increases when more clients are listening to it.
-This test is done by using web browsers and the Linux top command \cite{top}.
+To test the stream it is watched in a web browser and the CPU is measured using the Linux top command \cite{top}.
 
@@
 
-The internet speed is an important aspect in video streaming.
+The Internet speed is an important aspect in video streaming.
 According to Netflix there is 5.0 Megabits per second needed to stream one HD movie \cite{netflix}.
-During the ipref test the RPi 2 has with the a maximum connection of  94.2 Mbps~\cite{ipref}.
-This would result in the possibility for a RPi 2 to stream about 18 HD videos at the same time.
+During the ipref test the RPi2 has with a maximum connection of  94.2 Mbps~\cite{ipref}.
+This would result in the possibility for a RPi2 to stream about 18 HD videos at the same time.
 A simultaneous request of data by multiple streams reduces the bandwidth.
-So if many people do at the same time a request this can influence the connection of the Raspberry Pi.
-%Using the USB port and a Gigabit adapter can increase this amount to 220 Mbit/sec which would double the amount of HD videos being streamed.
+So if many people do at the same time a request this can influence the connection of the RPi2.
 
@@
 
-To stress test and see if the server is streaming correctly we use Apache JMeter~\cite{jmeter}.
-This test with Apache JMeter is used to see how many streams a Raspberry Pi 2 can handle.
-This test is done with a laptop and RPi 2.
-First a test case is created in Apache JMeter then a RTMP video stream is started and this is checked in a web page in a web browser.
-The reason to check it inside a web browser is because Apache JMeter can only measure HTTP files.
+In this test a RTMP steam is tested.
+This test is done with Apache JMeter to see how many streams a RPi2 can handle~\cite{jmeter}.
+This test is done with a laptop and RPi2.
+First a test case is created in Apache JMeter then a RTMP video stream is started and a stream is checked in a web page in a web browser.
+The reason to check it inside a web browser is because Apache JMeter can only measure HTTP captures.
 The result of this test is that it can handle 25 users for streaming MPEG-4 (MP4 ) files over HTTP.
-If there are more users used the video might freeze, because there is to much latency.
+If there are more users used the video might freeze, because there is too much latency.
 This becomes worse the more users there are this is a linear decrease.
 The RTMP stream used in this test streams the video only in 720p format.
-\newline Another test is by opening a media player like VLC were the RTMP stream address from the RPi 2 is opened.
+\newline Another test is by opening a media player like VLC were the RTMP stream address from the RPi2 is opened.
 If the RTMP stream with the 230 MB video of 49 minutes is opened  there can be seen that the video freezes, this is due to buffering problems.
@@
 This latency is introduced by the client which has not enough buffer time.
-Another problem is that FFmpeg is used as converter video to the RTMP stream, the use of a converter causes latency.
+Another problem is a converter is used to convert a video to the RTMP stream, the use of a converter causes latency.
 \newline
@@
 \subsubsection{File location test}
-For the file location and database a Cassandra database has been made.
+For file location and database a Cassandra database has been made.
 This data server is also used by Netflix to locate the movies.
 It turned out that it was possible to run Cassandra after a lot of configuration for the Raspberry Pi was done.
-To see if Cassandra was running the Cassandra query language shell was  opened on each RPi 2.
+To see if Cassandra was running the Cassandra query language shell was  opened on each RPi2.
 This was done by using the cqlsh command which is the command to start the cluster and its terminal.
-The output of the cqlsh command showed that it was connected to the cluster and the IP address of the RPi 2.
+The output of the cqlsh command showed that it was connected to the cluster and the IP address of the RPi2.
 \newline
@@
 
-There are several points of discussion in this research.
-The RPi 2 has a slow internet connection and this means that it streaming capacity is limited.
-With a USB 2.0 gigabit adapter attached to a Raspberry Pi 2 this could  double the connection speed, so twice the amount of videos are being streamed.
-\newline
-Apache JMeter is a tool to test HTTP streaming.
-This can be used for doing web browsers streaming videos, but it would be more ideal to test only the RTMP stream for the RTMP test.
-This turned out to be impossible with this testing tool.
-The next time there should be better looked at testing only the RTMP stream.
+A small data center is built by using Raspberry Pi's.
+Small data centers are being used to avoid bottlenecks.
+Using microservers in data centers improves the scalability of the data center.
+Microservers such as the RPi2 can be used in these data centers.
+Small data centers with video streaming are used to get an elastic network, that can scale data bandwidth needed for video streaming.
+It is used to make faster adaptation of the video quality possible.
+By using it the user gets the best video quality without freezing.
+
+It turned out that it is possible to make a video streaming cluster with RPi2s.
+The RPi2 cloud has a low power consumption, but is not good for video streaming due to its limited bandwidth and CPU performance.
+In the research it was possible to analyze what happens with the video streams inside the cluster and to a test device like a laptop.
+This makes it possible to see what happens at the begin part of the network, so video stream algorithms can be improved.
+
+The RPi2 is placed inside a data center.
+The RPi2 is a lot smaller and there can be placed several of them inside a data center instead of a server.
+The RPi2 can save energy, because they can be turned on and off more scalable and they do not consume so much energy as a normal server.
+
+The setup of the RPi2 cloud consists of a operating system, a fault-tolerant database, a webserver, a video converter and a video player.
+The RPi2 has made load balancing possible with a webserver and media player in a browser.
+In order to stream a video to the user a RTMP message is encapsulated in HTTP for the web browser.
+The RPi2 can make videos of different qualities with a video converter.
+In tests it turned out that this video converter could only convert two videos at the same time.
+A stream is made by using a video converter and webserver.
+For the file location it is possible to set up a scalable fault tolerant database, so it is possible to locate the files even if one node fails.
+The video streaming with Video on Demand or adaptive streaming has a good performance using this setup.
+In the future it is likely that devices with a ARM processor are used in a data center.
+The ARM processor has the possibilities to make it dedicated for a special task.
+
+Video streaming affected by various load balancing techniques.
+In the research several load balancing techniques were used.
+The webserver offers load balancing over adaptive streaming, this is used for video on demand (VOD).
+To redirect the user to the video HTTP load balancing is done with a webserver.
+In this research it turned out that RTMP streaming or VOD have differences in the availability.
+By using VOD the streaming goes better and the user experiences less freezing.
+SMIL can cause freezing when the user chooses the quality by himself, because its bitrate might not be sufficient for the quality demanded, causing freezing.
+When the computer does the change in quality there is less freezing.
+By using these different load balancing techniques the performance and the user experience changes.
+Improvements on those load balancing techniques were not possible due to time constraints, but these improvements can be possible in future research.
 
 \section{Conclusion}
-The Raspberry Pi 2 turned out to be a device that can be used in research.
-It has limitations and capabilities.
-In this paper the research focused on the performance of the Raspberry Pi 2 in small scale data center with video streaming.
-To answer this several research questions are answered.
-
-To answer the first research question, small scale data centers are important for the data transfer over the internet.
-They are used to avoid internet bottlenecks.
-Besides that smaller cloud computers can make use of microservers like the Raspberry Pi 2.
-For a good video stream a server is needed nearby, because its easier to adjust the settings for the buffer to watch a streamed video at the best quality.
-A small data centers with video streaming is used to get an elastic network, that can scale data bandwidth needed for video streaming.
-
-The goal of the second research question is to find out if the Raspberry Pi 2 is usable for video streaming.
-The Raspberry Pi 2 is capable of running a operating system that can host a streaming server.
-The Raspberry Pi 2 is capable of running an RTMP stream and serving videos on demand.
-The Raspberry has a low power usage, but has a limited network connection.
-This limited network connection makes the Raspberry Pi 2 not good for video streaming.
-The CPU is rather limited and FFmpeg could only convert two HD videos at the same time.
-Despite all these disadvantages the Raspberry Pi is still a good device to test streaming software for the ARM processor.
-The Raspberry Pi 2 has possibility to analyze on small scale what happens on the cloud with the video stream.
-
-The goal of the third research question was to see if it is possible to fit the Raspberry Pi inside a data center.The first advantage of the Raspberry Pi 2 is that it is a lot smaller and there can be placed several of them inside a data center instead of a server.
-It is possible to fit 500 Raspberry Pi's inside a single server rack inside a data center.
-This can save energy, because they can be turned on and off separately and they do not consume so much energy as a normal server.
-However this also has some drawbacks.
-The Raspberry Pi 2 still does not have enough processing power and its internet connection is slow.
-To solve these kinds of problems power over ethernet can be used.
-
-The aim of the fourth research question is to find a suitable setup for a Raspberry Pi cloud with video streaming.
-For this project a setup for video streaming has been built.
-For the operating system a diet version of the Raspbian is used this is called Dietpi.
-For the streaming NGINX, JW Player and FFmpeg are needed.
-The Raspberry Pi 2 has made load balancing possible with NGINX and JW Player.
-In order to stream a video to the user a RTMP message is encapsulated in HTTP for the web browser.
-For the media player a RTMP stream is send to the user that is made by NGINX and FFmpeg.
-The Raspberry Pi 2 can make videos of different qualities with FFmpeg.
-For the file location it is possible to set up a scalable Cassandra database.
-By using Cassandra it is possible to locate the files even if one node fails.
-The video streaming with Video on Demand or adaptive streaming has a good performance.
-The RPi 2 has a rather limited connection, this makes video streaming with the RPi 2 still not to useful.
-However this experiment shows that the RPi 2 is capable of video streaming.
-In the future it is likely that devices with a ARM processor are used in a data center.
-
-The last research question looks into how the availability in a Raspberry pi cluster with video streaming affected by various load balancing techniques.
-In the research several load balancing techniques were used.
-NGINX offers load balancing over adaptive streaming, this is used for video on demand (VOD).
-To redirect the user to the video HTTP load balancing by NGINX has been done.
-In this research it turned out that RTMP streaming or VOD have differences in the availability.
-By using VOD the streaming goes better and the user experiences less freezing.
-SMIL can cause freezing when the user chooses the quality by himself, because its bitrate might not be sufficient for the quality causing freezing.
-When the computer decides to change the quality there is less freezing.
-So by using these different load balancing techniques the performance and the user experience changes.
-Improvements on those load balancing techniques were not possible due to time constraints, but these improvements can be possible in future research.
-
-The main question is about the performance of the Raspberry Pi 2 inside a small scale data center with video streaming.
-A setup that is needed to do this is build in this research.
-The Raspberry Pi 2 does have some drawbacks for video streaming, but is usable for education purposes in the field of video streaming.
+Video streaming services have an increasing number of users, which causes an increase in the amount of network traffic and thus also in the amount of steaming problems.
+Small data centers decrease streaming problems, because of their elastic nature, which allows them to handle fluctuating video steaming bandwidth.
+We used RPi2s in small data centers to efficiently analyze video steaming.
+The analysis can be used to improve availability, user experience, and efficiency.
+Steaming servers operate only up to 20 \% of their total uptime, while still using 60 \% of their electricity needs.
+Compared to current steaming servers, RPi2s have a lower temperature because their electricity consumption is significantly lower.
+Nevertheless, RPi2s have a limited data bandwidth, which influences the capability of steaming and therefore affects user experiences.
+The CPUs of RPi2s have limited processing capabilities.
+Specialized microprocessors like ARM can very likely be used in the future to improve those capabilities.
+To conclude, performance can be more efficiently analyzed by using RPi2 clusters.
 
 \section{Future work}
-New possibilities with faster USB and Ethernet cable.
-It is possible to create a gigabit connection over USB 2.0.
-This will make better video streaming possible and more users can be reached over the HTTP.
+New possibilities with faster USB and Ethernet interface.
+It is possible to create a gigabit connection over USB 2.0, this could double the connection speed, so twice the amount of videos can be streamed.
+This will make better video streaming possible and more users can be reached over HTTP.
 Work together with streaming services such as NGINX to further develop video streaming services hosted by ARM processors.
-In the future it would also be possible to run a Cassandra service for the Raspberry Pi 2 this will make the file location of video's possible in a cluster.
+In the future it would also be possible to run a Cassandra service for the RPi2 this will make the file location of video's possible in a cluster.
 Netflix is currently looking for a specialist in  Peer-to-Peer distribution for their videos \cite{netflix}.
 Peer-to-Peer distribution can be interesting with Raspberry Pi.
-Besides this it might be interesting to look into Peer-to-Peer distribution in general and for video streaming in specific, there can be taken a look into the technology and legal aspect of  Peer-to-Peer distribution.
-It might be that a Raspberry Pi 2 can fit more easily inside a data center by using PoE or by making a special motherboard and Raspberry Pi 2 modules instead of a whole device.
+Besides this it might be interesting to investigate Peer-to-Peer distribution in general and for video streaming in specific, there can be done research into the technology and legal aspect of  Peer-to-Peer distribution.
+Apache JMeter is the tool to test HTTP streaming, but it would be more ideal to test only the RTMP stream for the RTMP test.
+This turned out to be impossible with this testing tool.
+It is useful to test only the RTMP stream next time.
+It might be that a Raspberry Pi 2 can fit more easily inside a data center by using Power over Ethernet or by making a special motherboard and Raspberry Pi 2 modules instead of a whole device.
 
 \section{Acknowledgments}
-This paper would not have been possible without the help of  student Nick Shot and PhD candidate Björn Postema.
-A special thanks to Björn Postema from the Design and Analysis of Communication Systems group of the University Twente, for his insight, good ideas and providing the necessary materials for doing this research.
+This paper would not have been possible without the help of Nick Shot and MSc Björn Postema.
+A special thanks to Björn Postema from the Design and Analysis of Communication Systems group of the University of Twente, for his insight, good ideas and providing the necessary materials for doing this research.
 
@@
 
+\clearpage
 \appendix
@@
 \begin{figure}[H]
-	\includegraphics[scale=1]{cost_cluster.png}
+	\includegraphics[scale=0.8]{cost_cluster.png}
 	\label{fig:cost}
